---
title: "Rosie's GAM results"
author: "Rosie"
date: "12/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)
library(vegan)
library(sf)
if (!require("rspatial")) devtools::install_github('rspatial/rspatial')
library(rspatial)
library( spgwr )
library(nlme)
library(boot)
library(itsadug)
library(mgcv)
library(raster)
library(stars)
```

## Spatial and Annual variation in temperature

Early exploration found no real trend in temperature across years (no signs of climate change). Some years were definitely warmer than others, but we don't have a long enough data set to say anything conclusive. Therefore, it seems more useful to use our data to look at changes across space and changes within years. THe approach I am using:

* Calculate average temperature, minimum temperature, and maximum temperature for each day of the year for the past ten years (where we have the most data)
* Run a tensor product smooth on temperature, latitude, longitude, and day
* Plot the results for some representative days of the year
* See how the results change given a 2-degree increase in average temperature or maximum temperature.


### The GAMs

For each GAM, I first ran the model without any accounting for temporal autocorrelation. I used the `bam` function in the package `mgcv` because I have a large data set.

`g1 = bam(Temperature ~ te(Latitude, Longitude, julian, bs = c("cr","cr", "cc")), 
             data =tempmean2, method = "REML"))`
             
I then calculated the value of `rho` based on the autocorrelation of the residuals of the origional model. I used this value to run a new GAM with an AR1 correlation parameter.


`r1 = acf(resid(g1), plot=FALSE)$acf[2]`

`g2 =  bam(Temperature ~ te(Latitude, Longitude, julian, bs = c("cr","cr", "cc")),
             data =tempmean2, method = "REML",  rho=r1, AR.start=tempmean2$start.event)`

These models were repeated for the minimum, maximum, average, and range of temperatures.

## Plots

To plot the results, I created a grid based on a rasterization of the Delta waterways, and used the "predict" function to fill in values for areas between data points based on the GAM model. I then raised the prediction for maximum and average temperatures by two degrees to see how different things might be under climate change scenarios. 

```{r, echo=FALSE}
load("GAMresults.RData")

#############################################################################
#plotting functions

raster_plot<-function(data, labels="All", type){
  if (type == "range") lims = c(0,6) else lims = c(5,30)
  data = st_crop(data, deltabuff)
  ggplot()+
    geom_stars(data=data)+
    facet_wrap(~Date)+
    scale_fill_viridis_c(name="Temperature", na.value="white",
                         limits=lims,
                         labels= function(x) ifelse((x/2)==as.integer(x/2), as.character(x), ""),
                         guide = guide_colorbar(direction="horizontal", title.position = "top", barwidth = 10, ticks.linewidth = 2,
                                                barheight=1, title.hjust=0.5, label.position="bottom", label.theme=element_text(size=12), 
                                                title.theme=element_text(size=13)))+
    coord_sf()+
    ylab("Latitude")+
    xlab("Longitude")+
    theme_bw() + theme(legend.position = "top")
}

raster_plot2<-function(data, date, labels="All", lims = NULL){
  data = data[,,,date]
  data = st_crop(data, deltabuff)
  ggplot()+
    geom_stars(data=data)+
   # facet_wrap(~Date)+
    scale_fill_viridis_c(name="Temperature", na.value="white", limits = lims,
                         labels= function(x) ifelse((x/2)==as.integer(x/2), as.character(x), ""),
                         guide = guide_colorbar(direction="horizontal", title.position = "top", barwidth = 10, ticks.linewidth = 2,
                                                barheight=1, title.hjust=0.5, label.position="bottom", label.theme=element_text(size=12), 
                                                title.theme=element_text(size=13)))+
    coord_sf()+
    ylab("Latitude")+
    xlab("Longitude")+
    theme_bw() + theme(legend.position = "top")
}



```

For example, here is a plot of the maximum temperatures currently, and with a 2-degree increase.

```{r}

raster_plot(rastered_preds, type = "Max") + ggtitle("Max Temperature")
raster_plot(rastered_preds2, type = "Max") + ggtitle("Max Temperature with 2 degree increase")


```

It's a little easier to look at just one day at a time. This is March 15th.

```{r}

raster_plot2(rastered_preds, 3, lims = c(10,25)) + ggtitle("Max Temperature - March")
raster_plot2(rastered_preds2, 3, lims = c(10,25)) + ggtitle("Max Temperature +2 - March")

```

Here is the mean temperature.

```{r}

raster_plot(rastered_predsave, type = "mean") + ggtitle("Mean Temperature")

raster_plot(rastered_preds2ave, type = "mean") + ggtitle("Mean Temperature with 2 degree increase")

raster_plot2(rastered_predsave, 3, lims = c(12,18)) + ggtitle("Mean Temperature - March")
raster_plot2(rastered_preds2ave, 3, lims = c(12,18)) + ggtitle("Mean Temperature +2 - March")

```

Many models show only small increases in average temperatures, but increases in temperature range might be more significant. Let's see what a 10% increase in temperature range looks like.

```{r}
raster_plot(rastered_predsrange, type = "range") + ggtitle("Temp range")
raster_plot(rastered_preds2range, type = "range") + ggtitle("Temp range with 10% increase")

raster_plot2(rastered_preds2range, 3, lims = c(0,7)) + ggtitle("Temp range - March")

raster_plot2(rastered_preds2range, 3, lims = c(0,7)) + ggtitle("Temp range +10%- March")


```

