---
title: "Local Regression analysis"
author: "Rosie"
date: "7/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)
library(vegan)
library(sf)
if (!require("rspatial")) devtools::install_github('rspatial/rspatial')
library(rspatial)
library( spgwr )

#load the data
temps = readRDS("Temp_filtered (1).rds")


#first calculate the daily means
tempmean = temps %>%
  filter(Date > as.Date("2014-1-1"), Station != "RYF") %>%
  mutate(julian = yday(Date)) %>%
  group_by(Station, julian) %>%
  summarize(Temp = mean(Temp, na.rm = T))

```

## Local regression

One of the cool ways you can address differences across space is run a regression that calculates different coefficients over space. I ran the model over the continuous stations, then extrapolated the results to the rest of the Detla.

First we have to do some data manipulation to get everything into a spatial format. 

```{r}
#read in shapefile of the delta
delta = read_sf("deltashap/hydro_delta_marsh.shp")

#add lat/longs for the stations
stas = read.csv("StationLatLongs.csv")


#attached lat/longs to mean temperature
tempmean2 = merge(tempmean, stas)

#Specify a coordinate reference system and turn it into a spatial object
alb <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")

#Filter the Delta shapefile so it doesn't include areas where we dont have a lot of data
delta2 = sf::as_Spatial(dplyr::filter(delta, HNAME != "SAN FRANCISCO BAY", HNAME != "SAN PABLO BAY"))

#I'm not positive we have to do this transformation, but it was in teh example so I'm doing it.
ctst <- spTransform(delta2, alb)
```

Now I'll filter out just the data from January-June and find the optimal badwidth for the interpolation. I think this basically tells you how much "smoothing" to put between your sampling points.
```{r}
tempmean2.1 = dplyr::filter(tempmean2, julian <190)
tempmeansub = tempmean2.1
sp = tempmeansub
coordinates(sp) = ~ Longitude + Latitude
crs(sp) <- "+proj=longlat +datum=NAD83"
spt <- spTransform(sp, alb)

#find optimal bandwith
#THIS TAKES FOREVER!
bw <- gwr.sel( Temp~ julian, data= spt)


```

To make the pretty map, I need to create a blank raster from the Delta shapefile. Once I calculate the predicted values for the regression, I'll fill it in.


```{r}
r <- raster(ctst,  res=100)
rdelta2 <- rasterize(ctst, r)
newpts <- rasterToPoints(rdelta2)
```

Now I run the GWR function to calculate local regressions

```{r warning=F}
#

g <- gwr(Temp ~ julian, data= spt,
         bandwidth=bw, fit.points=newpts[, 1:2])
g
```

Put the fitted points back on my raster and plot it!

```{r fig.width=15}
slope <- rdelta2
intercept <- rdelta2
slope[!is.na(slope)] <- g$SDF$julian
intercept[!is.na(intercept)] <- g$SDF$'(Intercept)'
s <- stack(intercept, slope)
names(s) <- c('intercept', 'slope')
plot(s, xlim = c(-200000, -100000), ylim = c(-50000,50000))


```

##Now the cool part - how things have changed over the historical record

```{r}


#first calculate the daily means
temps$Year = year(temps$Date)
tempmax = temps %>%
  mutate(julian = yday(Date)) %>%
  group_by(Station, julian, Year) %>%
  summarize(Temp = mean(Temp, na.rm = T),
            maxTemp = max(Temp, na.rm = T),
            minTemp = min(Temp, na.rm = T))

tempmax2 = merge(tempmax, stas)

tempmax2.1 = dplyr::filter(tempmax2, julian <250)
#spx = sample_n(tempmax2.1, 10000)
spx = tempmax2.1

#turn it into a spatial object
coordinates(spx) = ~ Longitude + Latitude
crs(spx) <- "+proj=longlat +datum=NAD83"
sptx <- spTransform(spx, alb)

#find badwidth
bwx <- gwr.sel( maxTemp~ julian + Year, data= sptx)


gx <- gwr(maxTemp~ julian + Year, data= sptx,
         bandwidth=bwx, fit.points=newpts[, 1:2])
gx

```
```

Put the fitted points back on my raster and plot it!

```{r fig.width=15}
slopeDay <- rdelta2
slopeYear <- rdelta2
intercept <- rdelta2
slopeDay[!is.na(slopeDay)] <- gx$SDF$julian
slopeYear[!is.na(slopeYear)] <- gx$SDF$Year
intercept[!is.na(intercept)] <- gx$SDF$'(Intercept)'
s <- stack(intercept, slopeDay, slopeYear)
names(s) <- c('intercept', 'Seasonal Change', "Inter-annual Change")
plot(s, xlim = c(-200000, -100000), ylim = c(-50000,50000))


```
