---
title: "ClusterHeatmap"
author: "Catarina Pien"
date: "10/21/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)
library(vegan)
library(sf)
library(RColorBrewer)
library(gridExtra)
library(scales)
library(ggmap)
# tempFilt <- readRDS("Data/tempFilt.rds") 
# tempToUse <- readRDS("Data/temp10years_20200922.rds")
tempAn0 <- readRDS("Data/tempAnnual.rds")
tempMon <- readRDS("Data/tempMonthly.rds")
# tempDaily <- readRDS("Data/tempDaily.rds")
# tempHeat <- readRDS("Data/heatstressDaily.rds")

```

# Shrink annual dataset to full dataset
```{r include = FALSE}
tempAn0 <- filter(tempAn0, WY > 2008 & WY < 2020) 

nYear <- tempAn0 %>%
  group_by(Station, WY) %>%
  summarize(n()) %>%
  ungroup() %>%
  group_by(Station) %>%
  summarize(nYear = n())

tempAn <- left_join(tempAn0, nYear) %>%
  filter(nYear == 11)
```

# Make wide datasets and cluster

```{r warning=FALSE, include = FALSE, message=FALSE, fig.width=12}

#put it into wide format for the cluster analysis
tempAnwide = pivot_wider(tempAn, id_cols = c(Station), 
                       names_from = WY, values_from = meanTemp)
tempAnwide2 = pivot_wider(tempAn, id_cols = c(Station), 
                         names_from = WY, values_from = minTemp)
tempAnwide3 = pivot_wider(tempAn, id_cols = c(Station), 
                         names_from = WY, values_from = maxTemp)
tempAnwide4 = pivot_wider(tempAn, id_cols = c(Station), 
                         names_from = WY, values_from = rangeTemp)

tempAnwide5 = cbind(tempAnwide[-1], tempAnwide2[,-1], tempAnwide3[,-1], tempAnwide4[,-1])

row.names(tempAnwide) = tempAnwide$Station

#calculate distance and cluster
tempdist = dist(tempAnwide[-1], "euclidean")
tempfit = hclust(tempdist, method = "ward.D")
plot(tempfit, main = "Clusters based on annual mean, min, max, range", cex = 0.6)

```

pheatmap-dendrogram and heat map

```{r include = FALSE}
library(pheatmap)
library(viridis)
tempAnwide1 <- tempAnwide[-1]
tempAnwide_s <- scale(tempAnwide1)
row.names(tempAnwide_s) <- tempAnwide$Station
pheatmap(tempAnwide_s, cluster_cols = F, main = "Station Clusters")

tempAnwide1 <- as.data.frame(tempAnwide1)
row.names(tempAnwide1) <- tempAnwide$Station
# Row annotation: Region (as assigned by Rosie previously)
row_annot <- tempAn %>%
  select(1:2) %>%
  unique()%>%
  as.data.frame()
rownames(row_annot) <- row_annot$Station 
row_annot <- row_annot[1]

# Column annotation: WY Type
col_annot <- tempAn %>%
  select(c(WY, WYType2_Sac)) %>%
  unique() %>%
  as.data.frame() 
rownames(col_annot) <- col_annot$WY
col_annot <- col_annot[2]

# Colors for annotations
newCols <- colorRampPalette(grDevices::rainbow(length(unique(row_annot$Region))))
mycolors <- newCols(length(unique(row_annot$Region)))
names(mycolors) <- unique(row_annot$Region)
mycolors <- list(category = mycolors)

# Heat map
# Order years
tempAnwide_yearorder <- tempAnwide1 %>%
  select(c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018"))

pheatmap(tempAnwide_yearorder, scale = "column", annotation_row = row_annot, cluster_cols = F, main = "Compare Stations")

pheatmap(tempAnwide_yearorder, scale = "row", annotation_row = row_annot,  annotation_col = col_annot,
         cluster_cols = F, main = "Compare Years")


# Clustered years
pheatmap(tempAnwide1, scale = "row", annotation_col = col_annot, 
         main = "Compare years")

```


# Make a winter and summer annual dataset

Code to make sure every month has data - currently is not being used (need to join with above)
```{r nMon}
# Filter to only data that has temps from every month so as not to skew the data that only has part of the year represented.
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

nMon$WY <- as.numeric(nMon$WY)
```

Add Season; Filter and alter variables
```{r}
tempMon <- tempMon %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempMon$Season <- factor(tempMon$Season, levels = c("Spring", "Summer", "Fall", "Winter"))
tempMon$WY <- as.numeric(tempMon$WY)
tempMon$fWY <- ordered(tempMon$WY)
tempMon$fMonth <- ordered(tempMon$Month, levels = c("11", "12", "1", "2"))
tempMon$fYear <- ordered(tempMon$Year)
tempMon <- filter(tempMon, WY > 2008 & WY < 2020)
tempMonM <- left_join(tempMon, nMon) %>%
  filter(nMon == 12)

```

# Make new annual datasets
```{r}
tempSum0 <- tempMonM %>% filter(Month %in% c(5,6,7,8,9,10)) %>%
  group_by(Region, Station, WY, WYType2_Sac) %>%
  summarize(maxT = mean(maxTemp),
            meanT = mean(meanTemp),
            minT = mean(minTemp),
            rangeT = mean(rangeTemp)) %>%
  ungroup() 
  
tempWet0 <- tempMonM %>% filter(Month %in% c(11,12,1,2,3,4)) %>%
    group_by(Region, Station, WY, WYType2_Sac) %>%
  summarize(maxT = mean(maxTemp),
            meanT = mean(meanTemp),
            minT = mean(minTemp),
            rangeT = mean(rangeTemp)) %>%
  ungroup()

tempSum <- left_join(tempAn0, nYear) %>%
  filter(nYear == 11)
```

# Shrink annual dataset to full dataset
```{r include = FALSE}

nYearSum <- tempSum %>%
  group_by(Station, WY) %>%
  summarize(n()) %>%
  ungroup() %>%
  group_by(Station) %>%
  summarize(nYear = n())

tempSum <- left_join(tempSum0, nYearSum) %>%
  filter(nYear == 11)

nYearWet <- tempWet %>%
  group_by(Station, WY) %>%
  summarize(n()) %>%
  ungroup() %>%
  group_by(Station) %>%
  summarize(nYear = n())

tempWet <- left_join(tempWet0, nYearWet) %>%
  filter(nYear == 11)

```


# Summer/Fall Heatmaps
```{r warning=FALSE, message=FALSE, fig.width=12}

#put it into wide format for the cluster analysis
tempSumWideMean = pivot_wider(tempSum, id_cols = c(Station), 
                       names_from = WY, values_from = meanT)
tempSumWideMax = pivot_wider(tempSum, id_cols = c(Station), 
                         names_from = WY, values_from = maxT)
tempSumWideRange = pivot_wider(tempSum, id_cols = c(Station), 
                         names_from = WY, values_from = rangeT)

tempSumWideMean <- as.data.frame(tempSumWideMean)
rownames(tempSumWideMean) <- tempSumWideMean$Station

#calculate distance and cluster
tempdistSum = dist(tempSumWideMean[-1], "euclidean")
tempfitSum = hclust(tempdistSum, method = "ward.D")
plot(tempfitSum, main = "Clusters based on annual mean, min, max, range", cex = 0.6)

```

```{r}
library(pheatmap)
library(viridis)
tempSumWide1 <- tempSumWideMean[-1]

# Row annotation: Region (as assigned by Rosie previously)
row_annotSum <- tempSum %>%
  select(1:2) %>%
  unique()%>%
  as.data.frame()
rownames(row_annotSum) <- row_annotSum$Station 
row_annotSum <- row_annotSum[1]

# Column annotation: WY Type
col_annotSum <- tempSum %>%
  select(c(WY, WYType2_Sac)) %>%
  unique() %>%
  as.data.frame() 
rownames(col_annotSum) <- col_annotSum$WY
col_annotSum <- col_annotSum[2]

# Colors for annotations
newCols <- colorRampPalette(grDevices::rainbow(length(unique(row_annot$Region))))
mycolors <- newCols(length(unique(row_annot$Region)))
names(mycolors) <- unique(row_annot$Region)
mycolors <- list(category = mycolors)

# Heat map
# Order years
tempSum_yearorder <- tempSumWide1 %>%
  select(c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019"))

```

Unscaled, year order
```{r, fig.dim = c(7,8)}
pheatmap(tempSum_yearorder, annotation_row = row_annotSum, cluster_cols = F, main = "Summer Means")
```


Cluster of stations, organized by WY order
```{r, fig.dim = c(7,8)}
pheatmap(tempSum_yearorder, scale = "column", annotation_row = row_annotSum,
         annotation_col = col_annotSum,cluster_cols = F, main = "Summer Means scaled by WY")
```


```{r fig.dim = c(7,8)}
pheatmap(tempSum_yearorder, scale = "row", annotation_row = row_annotSum,  annotation_col = col_annotSum,
         cluster_cols = F, main = "Summer Means scaled by Station")
```


Include year cluster (years organized by cluster)

```{r fig.dim = c(7,8)}
pheatmap(tempSumWide1, scale = "row", annotation_col = col_annotSum, annotation_row = row_annotSum,
         main = "Summer means - scaled by Station")
```

```{r fig.dim = c(7,8)}
pheatmap(tempSumWide1, scale = "column", annotation_col = col_annotSum, annotation_row = row_annotSum,
         main = "Summer means - scaled by WY")
```


# Winter/Spring Heat maps
```{r}
tempWetWideMean = pivot_wider(tempWet, id_cols = c(Station), 
                         names_from = WY, values_from = meanT)
tempWetWideMax = pivot_wider(tempWet, id_cols = c(Station), 
                         names_from = WY, values_from = maxT)

tempWetWideMean <- as.data.frame(tempWetWideMean)
rownames(tempWetWideMean) <- tempWetWideMean$Station

#calculate distance and cluster
tempdistWet = dist(tempWetWideMean[-1], "euclidean")
tempfitWet = hclust(tempdistWet, method = "ward.D")
plot(tempfitWet, main = "Clusters based on annual mean, min, max, range", cex = 0.6)

```

```{r}
library(pheatmap)
library(viridis)
tempWetWide1 <- tempWetWideMean[-1]

# Row annotation: Region (as assigned by Rosie previously)
row_annotWet <- tempWet %>%
  select(1:2) %>%
  unique()%>%
  as.data.frame()
rownames(row_annotWet) <- row_annotWet$Station 
row_annotWet <- row_annotWet[1]

# Column annotation: WY Type
col_annotWet <- tempWet %>%
  select(c(WY, WYType2_Sac)) %>%
  unique() %>%
  as.data.frame() 
rownames(col_annotWet) <- col_annotWet$WY
col_annotWet <- col_annotWet[2]

# Colors for annotations
newCols <- colorRampPalette(grDevices::rainbow(length(unique(row_annot$Region))))
mycolors <- newCols(length(unique(row_annot$Region)))
names(mycolors) <- unique(row_annot$Region)
mycolors <- list(category = mycolors)

# Heat map
# Order years
tempWet_yearorder <- tempWetWide1 %>%
  select(c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019"))

```

Absolute temps
```{r fig.dim = c(7,8)}
pheatmap(tempWet_yearorder,  annotation_row = row_annotWet,
         annot_col = col_annotWet, 
         cluster_cols = F, main = "Winter/Spring Means")
```

Organized by year order

```{r fig.dim = c(7,8)}
pheatmap(tempWet_yearorder, scale = "column", annotation_row = row_annotWet,
         annotation_col = col_annotWet,
         cluster_cols = F, main = "Winter/Spring Means scaled by WY")
```


```{r fig.dim = c(7,8)}
pheatmap(tempWet_yearorder, scale = "row", annotation_row = row_annotWet,  annotation_col = col_annotWet,
         cluster_cols = F, main = "Winter/Spring Means scaled by station")

```

Include year cluster (years organized by cluster)

```{r fig.dim = c(7,8)}
pheatmap(tempWetWide1, scale = "row", annotation_col = col_annotWet, annotation_row = row_annotWet,
         main = "Winter/Spring Means scaled by Station")
```


```{r fig.dim = c(7,8)}
pheatmap(tempWetWide1, scale = "column", annotation_col = col_annotWet, annotation_row = row_annotWet,
         main = "Winter/Spring Means scaled by WY")
```

