---
title: "DepthAnalysisExploration"
author: "Catarina Pien"
date: "8/5/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(readr)
```

### Read in data
* Add date and time variables (lubridate:: month(), day(), year())
* Order factors to be low-medium-high
```{r import}
dir <- getwd()
# Run this then check your dir (type dir in console).
setwd(paste0(dir, "/DepthAnalysis/")) # If your "dir" does not include the DepthAnalysis folder run this line. If it does ignore this line.
depth <- readRDS("/DepthAnalysis/Data/depthdata_heatstress_20201005.rds") # Run this
#depth$Datetime <- attr(depth$Datetime, "tzone") <- "PDT"
```

### Check timezone
```{r timezone}
depth2 <- depth %>%
  filter(WaterCol == "Bottom",
         Station == "ANH") %>%
  mutate(Date = date(Datetime)) 
## what does this show us?? if I am reading it correctly this shows anh bottom max temperature june-August? -MN

# Look at when max temp hour occurs
depth2a <- depth2 %>%
  group_by(Date) %>%
   summarize(max.Temp = max(Temp),
            n = n()) %>%
  filter(n>20) %>%
  left_join(depth2) %>%
  filter(Temp == max.Temp) %>%
  mutate(Month = month(Date),
         Hour = hour(Datetime))
view(depth2a)

# Make surface dataset 
# Compared with CDEC - now the same (PST)
ANH_surf <- depth%>%
  filter(WaterCol == "Surface",
         Station == "ANH")

# Matches Excel File - same when reading as character vs. not.
ANH1 <- read_csv("DepthAnalysis/Data/ANH_07122020_12312019_BottomTemp.csv")
ANH1a <- read_csv("DepthAnalysis/Data/ANH_07122020_12312019_BottomTemp.csv",
                 col_types = cols( DATE = col_character()))

# Changing names, inputs
ANH2 <- ANH1a %>%
  mutate(Datetime = parse_datetime(DATE, format = "%m/%d/%Y %H:%M"),
         Temp2 = round(VALUE,1),
         Minute = minute(Datetime),
         Hour = hour(Datetime),
         Date = date(Datetime)) %>%
  filter(Minute == 0,
         Temp2 >5 & Temp2 < 40) %>%
 select(-c(1:8))
#round (value,1) is the rounding to the tenth
#each of the temp2,datetime and minute, hour is adding new columns select line 1-8 is when she deleted the knew columns she used but doesn't need to show anymore

# Looking at when max temps occur
ANH2a <- ANH2 %>%
  group_by(Date) %>%
  summarize(max.Temp = max(Temp2),
            n = n()) %>%
  filter(n>20) %>%
  left_join(ANH2) %>%
  filter(Temp2 == max.Temp) %>%
  mutate(Month = month(Date))
## temp2 appears to be the new rounded values-MN

# Plot max temp by hour
library(plotly)
# Using Excel file
ANHp3 <- ggplot(ANH2a, aes(x = ordered(Hour), y = max.Temp, color = factor(Month)), alpha = 0.6) + geom_jitter()
ggplotly(ANHp3)

# Using depth dataset
ANHp4 <- ggplot(depth2a, aes(x = ordered(Hour), y = max.Temp, color = factor(Month)), alpha = 0.6) + geom_jitter()
ggplotly(ANHp4)

## did you find a difference using the different datasets?-MN

```


# need to get all data in dataframe to be from 2012-07-12 to 2019-12-27 and
Need to first take out the middle data from RRI
```{r}
depth_filter <- depth %>% 
  filter(Datetime >= as.Date("2012-07-12")& Datetime <= as.Date("2019-12-27")) %>% 
  filter(WaterCol!="Middle")
depth_filter

View(depth_filter)


# now in depth_filter the middle temp is taken out and is in the right timeframe for the data, may need to come back and adjust to be the exact subset of data as Brian M
#control plus enter equals running
```

ANH Data
```{r}
Anhdata<- depth_filter %>% 
  filter(Station == "ANH") %>% 
  filter(Stress == "Med")

Anhdata
```
No data in ANH has any high stress events.

Use the filter above and check on the MED for ANH, MAL, MRZ
```{r}
dates_filter <- depth_filter %>%
  group_by(Station, WaterCol) %>%
  summarize(start = first(Date),
            end = last(Date))
dates_filter
```


Subset so all stations cover the same time period? (use filter)
```{r}
# Table of start and end dates
dates <- depth %>%
  group_by(Station, WaterCol) %>%
  summarize(start = first(Date),
            end = last(Date))
dates 
```

### Stress Events
* Subset to June 1 - November 1 
* Subset to max daily temperature
```{r}
# need to filter out for the summer stress event
#need to get the maximum temp per day per station and per water column as well surface or bottom

temp_max <- depth_filter %>% 
  group_by(Station, WaterCol, Date, Stress) %>% 
  summarise(max(Temp))
  
temp_max
```
above now for each day I now have the max temp!!


1. Calculate the number of days max daily temperature meets "high stress" criteria 
  + By station
  + By depth
2. Calculate proportion of days in each of the stress categories 
```{r}
## answer 1. calculate the number of days max meets high stress

table_highstress <- temp_max %>% 
 filter(Stress== "High") %>% 
  group_by(Station, WaterCol) %>%
  count(Stress)

 
table_highstress 
 ## so far high stress has only been at RRI none at any of the other stations


## plot top and bottom max of each day
 ## make some figures of the events 
```
```{r}
table_Medstress <- temp_max %>% 
 filter(Stress== "Med") %>% 
  group_by(Station, WaterCol) %>%
  count(Stress)

table_Medstress
ggplot(table_Medstress, aes(x = Stress, y = n)) + geom_col() +
  facet_grid(WaterCol~Station)


```
should I turn this into a graph?

Visualization options: bar plot, proportional bar plot

```{r}
# Summarize data
# I'm leaving this code (below) in to help you make plots, but it is not correctly representing proportion because the dates are only reflecting dates at each stress level. You will want to standardize dates (above), and then you probably don't need to do the proportions at all. I can help you with this if you'd like. 

table <- depth_filter %>%
  group_by(Station, WaterCol, Stress) %>%
  summarize(n = n(),
            days = n/24,
            start = first(Date), # first date in the dataset
            end = last(Date),
            span = as.numeric(end-start)+1,
            prop = days/span)
#took this filter out because filtered at the top for na and for taking out the middle
#The filter function below is showing how to get rid of something.
# filter(!is.na(Stress), 
  #       WaterCol!="Middle")
table
# Make a bar plot!
# ndays in each stress category, faceted into station 
library(ggplot2)
ggplot(table_highstress, aes(x = Stress, y = n)) + geom_col() + ## this is ust for RRI since it is the only station with any high stress
  facet_grid(WaterCol~Station)

# Add stacked bar plot
ggplot(table, aes(x = Stress, y = days, fill = WaterCol)) + geom_col(position = "fill") +
  facet_wrap(~Station)

```

### Cat - Find the mean time of the max temp 

```{r meanmaxtemphour}
Max.time <- depth_filter %>%
  group_by(Station, WaterCol, Date) %>%
  mutate(Max.temp = max(Temp),
         Month = month(Datetime),
         Hour = hour(Datetime)) %>%
  filter(Temp == Max.temp) %>%
  ungroup()

Max.time.n <- depth_filter %>%
  group_by(Station, WaterCol, Date) %>%
  mutate(Max.temp = max(Temp),
         Month = month(Datetime),
         Hour = hour(Datetime)) %>%
  filter(Temp == Max.temp) %>%
    summarize(n = n()) %>%
  ungroup()

Max.time.summary = Max.time %>%
  group_by(Station, WaterCol, Month) %>%
  summarize(Median.max.hour = median(Hour))

# By month
ggplot(Max.time.summary, aes(x= ordered(Month), y = Median.max.hour)) + facet_grid(Station~WaterCol) + geom_col() + 
  theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15))

Max.time.summary2 = Max.time %>%
  group_by(Station, WaterCol) %>%
  summarize(Median.max.hour = round(median(Hour),1),
            n = n())
###most of the median max hours for both surface and bottom were at 1600, with the exception of MRZbottom and RRI surface at 1500

# By station/watercol
ggplot(Max.time.summary2, aes(x= Station, y = Median.max.hour)) + facet_grid(~WaterCol) + geom_col() + 
  theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15))

ggplot(Max.time.summary, aes(x= Station, y = Median.max.hour)) + facet_grid(~WaterCol) + geom_boxplot() + 
  theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15))

Max.time.summary3 <- Max.time %>%
  summarize(median.max = median(Hour))


```


### Surface-bottom temperature difference
* Convert data to wide format so that surface temps and bottom temps are in separate columns (google pivot_wider)
* Calculate temperature difference (use mutate)
* May have to do some averaging for variables below (use summarize)
* Define season
* Add water year type (use ifelse())
1. Is there a temperature difference
  + By station?
  + By season/month? 
  + By time of day?
  + By water year type?
  + By julian day?
  + By year? 
  + By combinations of these variables?
  
Visualization options: heatmap (esp month), bar plots 

Plot: 
Have a line at 0, plot a bar plot above and below zero

```{r}
#max temp difference at bottom/surface
depthDiff <- depth_filter %>%
  mutate(Year = year(Date)) %>%
  group_by(Station, WaterCol, Year, Date) %>%
  summarize(maxtemp = max(Temp))%>%
  ungroup()

library(tidyr)
############# Not accurately lined up Bottom-Surface
depthDiff_w <- pivot_wider(depthDiff,  names_from = WaterCol,   values_from = maxtemp)

depthDiff_w2 <- depthDiff_w %>%
  mutate(TempDiff = Bottom - Surface)


ggplot(depthDiff_w2, aes(x = Date, y = TempDiff)) + geom_point(size=.2) + labs(y="max tempdiff(c)") +
  facet_wrap(~Station) +geom_hline(yintercept = 0, color = "red")

#create new columns for month number and year
depthDiff_w2$Month=month(depthDiff_w2$Date)
depthDiff_w2$Year=year(depthDiff_w2$Date)
#plot my month
ggplot(depthDiff_w2, aes(x = factor(Month), y = TempDiff)) + geom_point(size=.2) + labs(y="Max TempDiff (c)") +geom_smooth(aes(group = factor(Station),  method = "loess", se = T))+
  facet_wrap(~Station) +geom_hline(yintercept = 0, color = "red") +
  theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15))

#Sites by year and months
ggplot(depthDiff_w2, aes(x = factor(Month), y = TempDiff)) + geom_point(size=.2) + labs(y="Max TempDiff (c)") +geom_smooth(aes(group = factor(Station),  method = "loess", se = T))+
  facet_grid(Station~Year) +geom_hline(yintercept = 0, color = "red")
###################################################################
depth_filter$WaterCol <- as.factor(depth_filter$WaterCol)

depthDiff_rel <- pivot_wider(depth_filter, names_from = WaterCol, values_from = Temp) %>%
  arrange(Station, Datetime)

# Missing data - RRI 
RRI_rel <- depthDiff_rel %>%
  filter(Station == "RRI") %>%
  mutate(Bottom = Bottom - 5)

ggplot(RRI_rel) +
  geom_point(aes(x = Datetime, y = Surface), color = "red", alpha = 0.5) +
  geom_point(aes(x = Datetime, y = Bottom), color = "green", alpha = 0.5)

depthDiff_rel2 <- depthDiff_rel %>%
  mutate(RelTempDiff = Bottom - Surface)

# Overall rel temp diff by station and date
ggplot(depthDiff_rel2, aes(x = Date, y = RelTempDiff)) + geom_point(size=.8) + labs(y="Relative TempDiff(C)") +
  facet_wrap(~Station) +geom_hline(yintercept = 0, color = "red") +
    theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15))

#create new columns for month number and year
depthDiff_rel2$Month=month(depthDiff_rel2$Date)
depthDiff_rel2$Year=year(depthDiff_rel2$Date)
depthDiff_rel2$Hour=hour(depthDiff_rel2$Datetime)

#add daytime categories for time of day
depthDiff_rel3 <- depthDiff_rel2 %>%
  mutate(TOD= ifelse(Hour>0 & Hour <=6, 'Early:1-6', ifelse(Hour>6 & Hour <=12, 'Morning:6-12', ifelse(Hour>12 & Hour <=18, 'Afternoon:12-18', ifelse(Hour>18 & Hour <=23, 'Evening:18-24' ,ifelse(Hour<1 & Hour >=0, 'Evening:18-24' , NA))))))



#set levels for time of day
depthDiff_rel3$TOD<-factor(depthDiff_rel3$TOD, levels=c("Early:1-6","Morning:6-12","Afternoon:12-18", "Evening:18-24"))

############################################################
#Convert hour to a trig funciton so that 0 and 24 are equal
#also julian day.
depthDiff_rel3 = mutate(depthDiff_rel3, sHour = cos(2*pi*(Hour)/24), sjulian = cos(2*pi*(julian)/365))


#plot by month
ggplot(depthDiff_rel3, aes(x = factor(Month), y = RelTempDiff,colour=factor(TOD))) + 
  geom_point(size=.4, position=position_dodge(width=0.2)) + 
  labs(y="Relative TempDiff (c)") +
  geom_smooth(aes(group = factor(TOD), colour=factor(TOD), method = "gam", se = TRUE))+
  facet_wrap(~Station) +
  geom_hline(yintercept = 0, color = "black",linetype='dashed') +
  theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.position = "bottom")


#plot by month - with hour as a sin function
ggplot(depthDiff_rel3, aes(x = sHour, y = RelTempDiff)) + 
  geom_point(size=.4) + 
  labs(y="Relative TempDiff (c)") +
  facet_wrap(~Station) +
  geom_hline(yintercept = 0, color = "black",linetype='dashed') +
  theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.position = "bottom")


check <- depthDiff_rel3 %>%
  filter(Station == "MRZ")%>%
  filter(is.na(RelTempDiff)) 

check2 <- depth_filter %>%
  filter(Station == "MRZ")

#Sites by year and months
ggplot(depthDiff_rel3, aes(x = factor(Month), y = RelTempDiff)) + 
  geom_point(size=.2) + 
  labs(y="Relative TempDiff (C)") +
  geom_smooth(aes(group = factor(Station),method = "loess", se = TRUE))+
  facet_grid(Station~Year) +geom_hline(yintercept = 0, color = "red") 

#plot by year
ggplot(depthDiff_rel3, aes(x = Date, y = RelTempDiff,colour=factor(TOD))) + geom_point(size=.5, position=position_dodge(width=0.2)) + labs(y="Relative TempDiff (C)") +
  facet_wrap(~Station) +geom_hline(yintercept = 0, color = "black", linetype='dashed') +
    theme_bw() +
      theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.position = "bottom",
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12))
  

#only regressions
ggplot(depthDiff_rel3, aes(x = Date, y = RelTempDiff,colour=factor(TOD)))+ labs(y="Relative TempDiff (c)") +geom_smooth(aes(group = factor(TOD), colour=factor(TOD), method = "loess", se = T))+
  facet_wrap(~Station) +geom_hline(yintercept = 0, color = "black",linetype='dashed') +
  theme_bw() +
      theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.position = "bottom",
        legend.text = element_text(size = 13))

#only regressions plot by month
ggplot(depthDiff_rel3, aes(x = factor(Month), y = RelTempDiff,colour=factor(TOD)))+ labs(y="Relative TempDiff (C)") +geom_smooth(aes(group = factor(TOD), colour=factor(TOD), method = "loess", span = 2, se = TRUE))+
  facet_grid(Year~Station) +geom_hline(yintercept = 0, color = "black",linetype='dashed') +
        theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.position = "bottom",
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12))

```

##### Cat started here ######
Run model for temp difference
* Change time of day groupings? 
* List variables to put in model 
* Figure out what a lower estimate means (greater difference or smaller difference?)
* Figure by station and TOD (panel)
```{r}

# Cut off first 3 days
# Include temperature lag 
depthDiff_rel3 <- depthDiff_rel3 %>%
  filter(Date > "2012-07-15") %>%
  group_by(Station) %>%
  mutate(TempDiffLag = lag(RelTempDiff, 1),
         TempDiffLag2 = lag(RelTempDiff,2))

# Add julian day
depthDiff_rel3$julian <- yday(depthDiff_rel3$Date)

# Add WY 
depthDiff_rel3 <- depthDiff_rel3 %>%
  mutate(WY = ifelse(Month > 10, Year + 1, Year))

# Run model 

# Filter to Station
RelTempDiff_MRZ <- depthDiff_rel3 %>% filter(Station == "MRZ")
RelTempDiff_RRI <- depthDiff_rel3 %>% filter(Station == "RRI")
RelTempDiff_MAL <- depthDiff_rel3 %>% filter(Station == "MAL")
RelTempDiff_ANH <- depthDiff_rel3 %>% filter(Station == "ANH")

# Plot max temp difference
ggplot(RelTempDiff_MRZ, aes(x = Hour, y = RelTempDiff)) + geom_point()
ggplot(RelTempDiff_RRI, aes(x = Hour, y = RelTempDiff)) + geom_point()
ggplot(RelTempDiff_MAL, aes(x = Hour, y = RelTempDiff)) + geom_point()
ggplot(RelTempDiff_ANH, aes(x = Hour, y = RelTempDiff)) + geom_point()

ggplot(depthDiff_rel3, aes(x = Hour, y = RelTempDiff)) + geom_point() + facet_wrap(~Station)

# Variables: 
# Julian day (sin or julian + julian^2)
# Hour vs TOD
# Mixed effects model vs Autoregression 
  # gls/lmer - Linear mixed effect model. Hour within station as a repeated measure

summary(m.MRZ1 <- glm(RelTempDiff ~ julian + I(julian^2)* TOD, data = RelTempDiff_MRZ))

m.TempDiff1 <- glm(RelTempDiff ~ julian * TOD, data = depthDiff_rel3)
summary(m.TempDiff1)

#now let's use hour in the model
m.TempDiff2 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + TempDiffLag2, data = RelTempDiff_ANH)
summary(m.TempDiff2)
library(visreg)
visreg(m.TempDiff2)

#NOt all that much autocorrelation at teh T-2 lag. 

library(itsadug)
library(mgcv)



#try using a GAM
RelTempDiff_ANH = start_event(as.data.frame(RelTempDiff_ANH), column="Datetime", event=c("Year"), label.event="Event")


g5 =  bam(RelTempDiff~  s(julian, bs = "cc") + s(Hour, bs = "cc") + te(julian, Hour, bs = c("cc","cc")), 
          data =RelTempDiff_ANH , method = "REML")

r5 = acf(resid(g5))$acf[2]


g5 =  bam(RelTempDiff~  s(julian, bs = "cc") + s(Hour, bs = "cc") + te(julian, Hour, bs = c("cc","cc")), 
          data =RelTempDiff_ANH , method = "REML", rho = r5,  AR.start=RelTempDiff_ANH$start.event)

plot(g5)


#try it again, without the interaction, cause that's kinda confusing

#look at antioch
g6 =  bam(RelTempDiff~  s(julian, bs = "cc") + s(Hour, bs = "cc"),
          data =RelTempDiff_ANH , method = "REML")
plot(g6)

r6 = acf(resid(g6))$acf[2]


g6.1 =  bam(RelTempDiff~  s(julian, bs = "cc") + s(Hour, bs = "cc"), 
          data =RelTempDiff_ANH , method = "REML", rho = r6,  AR.start=RelTempDiff_ANH$start.event)

plot(g6.1)



```

* Temp difference is greater when coefficient is more negative













If there is a difference (above) can include absolute temperatures to see what those numbers actually are.

```{r}
# Filter to just MRZ 
MRZ_depth <- depth_filter %>%
  filter(Station == "MRZ") %>%
  mutate(
    Hour = lubridate::hour(Datetime),
    TOD= ifelse(Hour>0 & Hour <=6, 'Early:1-6', 
                ifelse(Hour>6 & Hour <=12, 'Morning:6-12',
                       ifelse(Hour>12 & Hour <=18, 'Afternoon:12-18', 
                              ifelse(Hour>18 & Hour <=23, 'Evening:18-24' ,
                                     ifelse(Hour<1 & Hour >=0, 'Evening:18-24' , NA))))))
# Filter to just RRI
RRI_depth <- depth_filter %>%
  filter(Station == "RRI") %>%
  mutate(
    Hour = lubridate::hour(Datetime),
    TOD= ifelse(Hour>0 & Hour <=6, 'Early:1-6', 
                ifelse(Hour>6 & Hour <=12, 'Morning:6-12',
                       ifelse(Hour>12 & Hour <=18, 'Afternoon:12-18', 
                              ifelse(Hour>18 & Hour <=23, 'Evening:18-24' ,
                                     ifelse(Hour<1 & Hour >=0, 'Evening:18-24' , NA))))))


#look at absolute temp differences for MRZ
ggplot() + geom_point(data = MRZ_depth,aes(x = Date, y = Temp, color = WaterCol), alpha = 0.5, size = 1) + facet_wrap(~factor(TOD)) + labs(title = "MRZ Absolute Temps", y="Water Temp (C)") +
  geom_hline(yintercept = 25, color = "black", linetype='dashed') +
  geom_hline(yintercept = 22, color = "magenta", linetype='dashed') +
  scale_color_brewer(palette = "Dark2") +
    theme_bw() +
      theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.position = "bottom",
        legend.text = element_text(size = 13))

# look at absolute temp differences for RRI
ggplot() + geom_point(data = RRI_depth,aes(x = Date, y = Temp, color = WaterCol), alpha = 0.5, size = 1) + facet_wrap(~factor(TOD)) + labs(title = "RRI Absolute Temps", y="Water Temp (C)") +
  geom_hline(yintercept = 25, color = "black", linetype='dashed') +
    scale_color_brewer(palette = "Dark2") +
    theme_bw() +
      theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.position = "bottom",
        legend.text = element_text(size = 13))
```

### Temperature variability 
* Calculate daily temperature variation (either range, variance or standard deviation) max- min per day (could do per year, or like julian day and average over whole dataset)
1. Is there a difference in the daily deviation by depth
  + By station
  + By time of day? (usually wind in the afternoon)
  + By season?
  
```{r}
depth_range <- depth_filter %>%
  group_by(Station, WaterCol, Date) %>% 
  mutate(Year=year(Date)) %>%
  filter(Year == 2015) %>%
  summarize(maxtemp=max(Temp), 
            mintemp=min(Temp),
            range= maxtemp-mintemp)
  
ggplot(depth_range, aes(x = Date, y = range, color = WaterCol)) + geom_point(size=1) + 
  facet_wrap(~Station)

```



### temperature variability by Water Year type (answer all the questions above(-season) using WY)
### create WY column and assign the month 10-12 to the following year and add the type of water year from the excel file Sactype2


```{r}
depth_filter$Datetime <- as.character(depth_filter$Datetime)


depthfilterWY <- depth_filter %>%
  mutate(Datetime = parse_datetime(Datetime, format = "%Y-%m-%d %H:%M:%S"),
         Month = month(Datetime),
         Year = year(Datetime)) %>% 
  mutate(WY = ifelse(Month %in% c(10,11,12), Year + 1, Year))       

## mutate is adding or editing an existing or creating a new column, by editing you are technically overwriting a column. if you see a name and then an = you are making something new like line 511-512 above.  
 
depthfilterWY = left_join(depthfilterWY, WYType, by = 'WY')

### got all the WYType information from the excel file combined in depthfilterWY!
## New file =  left_join(main file, WYType file, by = “WY”) Cat's email suggestion for joining the WY file

### eliminate columns that are not needed descrribing wy in the depthfilterWY

depthfilterWY <- depthfilterWY %>% 
  select(Station, Datetime, Temp, WaterCol, Date, Stress, Month, Year, WY, WYType2_Sac)
## successfully removed unwanted WYT columns


## rearranging columns order
depthfilterWY <-depthfilterWY [,c("Station", "Datetime", "WY", "WYType2_Sac", "Temp", "WaterCol", "Date", "Stress", "Month", "Year")]
### [,c (column names and orders)]
```
### exploratory WYtype: what questions do we want to ask with regards to Water Year type?
```{r}
## julian day, need lubridate, need to check how the dates are loaded in? character? or date class?

view(depthfilterWY)
?yday
depthfilterWY$julian <- yday(depthfilterWY$Date)
head(depthfilterWY$julian)
view(depthfilterWY)
## rename the dataset and take out unneccessary columns
depthfilter_WY_julian <-depthfilterWY [,c("Station", "Datetime", "WY", "WYType2_Sac", "Temp", "WaterCol", "Date", "Stress", "Month", "Year", "julian")]
view(depthfilter_WY_julian)
### it worked, although I do not know how to check if the Julian date is the correct date or not..
```


```{r}
glm()
```


```{r}
## how many of these Med stress events were in dry years? wet? med? 
## I am confused on how to move forward with combing two different objects, how would I add WY to this question?
table_Medstress <- temp_max %>% 
 filter(Stress== "Med") %>% 
  group_by(Station, WaterCol) %>%
  count(Stress)

```


### Range 
2. take a single day and within a single day how much does that deviation change? so std? are temps at the bottom more stable? potentially at the surface you have higher deviation
```{r}
range_data <- depth_filter %>%
  group_by(Station, WaterCol, Date) %>%
  summarize(max.temp = max(Temp),
         min.temp = min(Temp),
         range = max.temp-min.temp)%>%
  mutate(Month = month(Date),
         Year = year(Date),
         yday = yday(Date)) %>%
  ungroup()

# range_data_yday <- range_data %>%
# pivot_wider(cols = c(Station, WaterCol), names_to = "StationDepth")
# group_by(Station, WaterCol, yday) %>%
# summarize(mean.range = mean(range)) 
```

Plot Range
```{r}
library(viridis)
ggplot(range_data, aes(x = as.factor(Month), y = range, color = WaterCol)) + 
  facet_grid(Station~., scales = "free") + geom_jitter(alpha = 0.5) +
  scale_color_brewer(palette="Dark2") + theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.text = element_text(size = 13),
        legend.position = "bottom")

ggplot(range_data, aes(x = as.factor(Month), y = range, color = WaterCol)) + 
  facet_grid(Station~., scales = "free") + geom_boxplot() +  
  scale_color_brewer(palette = "Dark2")+ theme_bw() + 
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.text = element_text(size = 13),
        legend.position = "bottom")

```



### Other questions
# How do results change if only 1+ day at different temperature thresholds?
  # Number of days extra in each category if 1+ day, 2+ day, vs. 3+ day
  
```{r}


```
  
  
 Cat's recommendation to color code to hour

Use lubridate::hour(Datetime) to get the hour of each point. 
Use mutate and ifelse to say mutate(TOD = ifelse(hour>0 & hour <=6, “early”, ifelse(hour>6 & hour <=12, “earlymid”, ifelse….. NA)
Then when you plot the data, color code by TOD (aka time of day) – feel free to name however you want. 
From Britt:
•	Can we figure out how to add colour by time of day? Wonder how the points will look and if trends? Not sure how to code this
o	0:00-6:00 (blue)
o	6:01-12:00 (yellow)
o	12:01-18:00 (red)
o	18:01-23:59 (green)
Can we convert these points to boxplots? Average by bars?

  
  
  
  
  
  
  