---
title: "heatcategories"
author: "Catarina Pien"
date: "7/28/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

Read in files
* Integrated dataset - filtered
* Extra EMP files 
```{r read}
library(tidyverse)
library(lubridate)
library(readr)

setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/DepthAnalysis/")

depthdata <- readRDS("Data/depthdata_QC_20200728.rds")
depthdata$Date <- date(depthdata$Datetime)
```

Classify Heat Category
1. Calculate maximum daily temperatures by station, depth
2. Flag temps > 25, >21
3. If there are 3+ days in a row where max temp >25, stress category = High
4. If not above, If there are more than 3 days in a row where max temp >21, stress category = Med
5. If neither, stress = Low
6. Join stress category with all temp values 
```{r Heat category}
# Calculate max temperatures

max <- depthdata %>%
  group_by(WaterCol, Station, Date) %>%
  summarize(maxT = max(Temp))

# Flagging starting on Day 3 of high/med temps   
heat <- max %>%
  group_by(WaterCol, Station) %>%
  mutate(Thr25 = ifelse(maxT > 25, 1L, 0L),
         Thr21 = ifelse(maxT > 21, 1L, 0L)) %>%
  mutate(Stress = ifelse(Thr25 == lag(Thr25, 1) & Thr25 == lag(Thr25, 2) & Thr25 == 1L, "High", 
                            ifelse(Thr21 == lag(Thr21, 1) & Thr21 == lag(Thr21, 2) & Thr21 == 1, "Med", 
                                   "Low"))) %>%
  select(-starts_with("Thr"))
  
# If the max temp of the day was flagged, the whole day's values are now flagged
depthdata_heat <- left_join(depthdata, heat, by = c("WaterCol", "Station", "Date")) %>%
  select(-maxT)

```


This would be for flagging all values in the group, not just starting on day 3
```{r alt flagging}

# heatAll <- max %>%
#   group_by(WaterCol, Station) %>%
#   mutate(Thr25 = ifelse(maxT > 25, 1L, 0L),
#          Thr21 = ifelse(maxT > 21, 1L, 0L)) %>%
#   mutate(issame25 = cumsum(Thr25 == 0L),
#          issame21 = cumsum(Thr21 == 0L)) %>%
#   group_by(WaterCol, Station, issame25) %>%
#   mutate(ndays25 = ifelse(Thr25 == 1L, sum(Thr25), 0L)) %>%
#   ungroup() %>%
#   mutate(Flag25 = ifelse(ndays25 >3, "Y", "N")) %>%
#   group_by(WaterCol, Station, issame21) %>%
#   mutate(ndays21 = ifelse(Thr21 == 1L, sum(Thr21), 0L)) %>%
#   ungroup() %>%
#   mutate(Flag21 = ifelse(ndays21 >= 3, "Y", "N")) 
#   select(-starts_with("issame")) %>%
#   select(-starts_with("Thr")) %>%
#   select(-starts_with("ndays")) %>%
#   mutate(Stresscat = ifelse(Flag25 == "Y", "High",
#                             ifelse(Flag21 == "Y", "Med", "Low"))) %>%
#   select(-starts_with("Flag"))
```

