---
title: "Relative Temperature Difference"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---
#Libraries needed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
### load all libraries, added all libraries from previous depthdatavisualiztion.rmd whether we necessarily needed them or not.
library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(tidyr)
library(visreg)
library(itsadug)
library(mgcv)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(viridis)
library(stargazer)
library(stargazer)
```

WD, Read in Data, Separate by Station
```{r}
## set wd, read in CSV relative tempdiff, bring over all data
relativetempdiff <- read.csv("DepthAnalysis/Data/RelativeTempDiff.csv")
## relativetempdiff has all of our parameters: julian day, WY, sinejulian, sinehour etc and is the correct timeframe

## filter the relativetempdiff for each station so I can bring in the models or try the models first
View(relativetempdiff)

RelTempDiff_MRZ <- relativetempdiff %>% filter(Station == "MRZ")
RelTempDiff_RRI <- relativetempdiff %>% filter(Station == "RRI")
RelTempDiff_MAL <- relativetempdiff %>% filter(Station == "MAL")
RelTempDiff_ANH <- relativetempdiff %>% filter(Station == "ANH")

```



##Plots
```{r}

## max differnce per station

ggplot(RelTempDiff_MRZ, aes(x = Hour, y = RelTempDiff)) + geom_point() 

ggplot(RelTempDiff_RRI, aes(x = Hour, y = RelTempDiff)) + geom_point()

ggplot(RelTempDiff_MAL, aes(x = Hour, y = RelTempDiff)) + geom_point()

ggplot(RelTempDiff_ANH, aes(x = Hour, y = RelTempDiff)) + geom_point()

### now plot all stations together with their relative temperature difference

ggplot(relativetempdiff, aes(x = Hour, y = RelTempDiff)) + geom_point() + facet_wrap(~Station)

```



## Models
```{r}
### run models for each station use as results interpretation


modelANH <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_ANH)
modelMAL <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_MAL)
modelMRZ <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_MRZ)
modelRRI <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_RRI)
### now let's look at the model outputs (will put into a table)
summary(modelANH)
summary(modelMAL)
summary(modelMRZ)
summary(modelRRI)


### deeper look into each station with ggplot and then ggplotly

##ANH##


##looking at the interaction between sjulian and shour
ggplot(RelTempDiff_ANH, aes(x= sjulian, y = sHour))+ geom_point() ## not a great plot
## with hour as a factor
ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(Hour)))+ geom_point(size = .4)
## better but still not great
###plotly to see the data clearer
#first with Hour
plotANHhour <- ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(Hour)))+ geom_point(size = .4) 
## need to add the station as the legend for quick view#

ggplotly(plotANHhour)
# now with TOD as a factor 
plotANHTOD <- ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotANHTOD)

## TOD seems like it will be easier for us to use for our figures for the viewers, but the models will be run hourly

## RRI##
##with TOD
plotRRITOD <- ggplot(RelTempDiff_RRI, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotRRI)

## MAL##
plotMALTOD <- ggplot(RelTempDiff_MAL, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotMALTOD)

##MRZ##
plotMRZTOD <- ggplot(RelTempDiff_MRZ, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotMRZTOD)


## Suggestions for making the data easier to view and see: color code by TOD (change groups) add a loess line with gmsmooth
## now going to try to plot all the TOD temp differences in a 4 panel
figure <- ggarrange(plotANHTOD, plotMALTOD, plotMRZTOD, plotRRITOD, labels = c("Antioch", "Mallard", "Martinez", "Rough and Ready Island"), ncol = 2, nrow = 2)
## didnt work I dont know where ggarrange function is I thought from the tutorial it looks like it was from ggplot
## now lets just try using the facet wrap

plotANHTOD + facet_wrap(plotMALTOD) + facet_wrap(plotMRZTOD) + facet_wrap(plotRRITOD) 

# Nope am missing the end part of the argument?


```

*Cat's notes here:*
To use facet_wrap you need all of the data to be in one dataset. So use your original dataset.
```{r}

## change the order of the TOD
relativetempdiff$TOD <- as.factor(relativetempdiff$TOD)
relativetempdiff$TOD<-  factor(relativetempdiff$TOD, levels(relativetempdiff$TOD)[c(2,4,1,3)])
levels(relativetempdiff$TOD)

### subset data to use when making the plots before finalized
relativetempdiff_sample <- relativetempdiff %>% sample_frac(.1)

### plot with faucet wrap

relativetempdiff$TOD <- factor(relativetempdiff$TOD, levels = c("Early:1-6", "Morning:6-12", "Afternoon:12-18", "Evening:18-24"))
levels(relativetempdiff$TOD) <- list("Early:1-6" = "Early:1-6", "Morning:7-12" = "Morning:6-12", "Afternoon:13-18" = "Afternoon:12-18", "Evening:19-24" = "Evening:18-24")


plotTOD <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_point(aes(color = TOD),size = .6) + facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +

  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) +
    guides(color = guide_legend(title = "Time of Day", override.aes=list(size = 4)))

plotTOD

## adding trend lines
plotTODlines <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_point(aes(color = TOD),size = 0.02, alpha = .1) +
geom_smooth(aes(color = TOD), method = "loess", se = F, fullrange = T) +
  facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(title = "Time of Day", override.aes = list(size=4)))

plotTODlines

## just the trend lines
plotlinesonly <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_smooth(aes(color = TOD), 
  method = "loess", se = T, fullrange = T) +
  facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(title = "Time of Day", override.aes = list(size=4)))

plotlinesonly
```

```{r}
plotTODLine <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_smooth(aes(color = TOD), method = "loess", se = TRUE) + facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  labs(y = "Relative Temperature Difference (C)", 
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) +
    guides(color = guide_legend(title = "Time of Day", override.aes=list(size = 4)))
plotTODLine
```


For your ggarrange, you had a typo in one of the plots and you need to call the plot. Here is your result, which doesn't look as good as the facet. 

```{r}
figure
```

I have not found the perfect solution for making multi-panel plots, but if you use facet, you can annotate each of your plots.

https://r-graphics.org/recipe-annotate-facet
```{r}
# Make a data frame for your labels
plot_labels <- data.frame(Station = c("ANH", "MAL", "MRZ", "RRI"), label = c("A", "B", "C", "D"))

# Add those labels to your plot
plotTOD + labs(x = "Julian Day", y = "Relative Temperature Diff (C)") + 
  geom_text(x = 350, y = -3.5, aes(label = label), size =6, data = plot_labels)
```
Nans and summary stats, model results table

```{r}
summary(relativetempdiff)

stargazer(modelANH, modelMAL, modelMRZ, modelRRI, type = "html", column.labels = c("ANH", "MAL", "MRZ", "RRI"), title = "Continuous Dataset Model Results", out ="allglmdpethmodeloutputs.html")

```
model results figures
```{r}
par(mfrow = c(2,2))
visreg(modelANH)
plot(modelANH)


```

