---
title: "Relative Temperature Difference"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---
#Libraries needed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
### load all libraries, added all libraries from previous depthdatavisualiztion.rmd whether we necessarily needed them or not.
library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(tidyr)
library(visreg)
library(itsadug)
library(mgcv)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(viridis)
library(stargazer)
```

WD, Read in Data, Separate by Station
```{r}
## set wd, read in CSV relative tempdiff, bring over all data
relativetempdiff <- readRDS("DepthAnalysis/Data/RelativeTempDiff2.rds")
## relativetempdiff has all of our parameters: julian day, WY, sinejulian, sinehour etc and is the correct timeframe

relativetempdiff <- relativetempdiff %>% select(-Stress)

# Add factor variables
relativetempdiff$fWY = factor(relativetempdiff$WY)
relativetempdiff$fYear = factor(relativetempdiff$Year)

# Filter to just water years 2013-2019 
relativetempdiff <- filter(relativetempdiff, WY < 2020 & WY > 2012)

# filter to only those on the hour
relativetempdiff$minute <- minute(relativetempdiff$Datetime)
relativetempdiff <- filter(relativetempdiff, minute == "0")

#no NAs
relativetempdiff <- filter(relativetempdiff, !is.na(RelTempDiff))

info <- relativetempdiff %>%
  group_by(Station, fWY) %>%
  summarize(n =  n())

## filter the relativetempdiff for each station so I can bring in the models or try the models first
RelTempDiff_MRZ <- relativetempdiff %>% filter(Station == "MRZ") %>% ungroup()
RelTempDiff_RRI <- relativetempdiff %>% filter(Station == "RRI") %>% ungroup()
RelTempDiff_MAL <- relativetempdiff %>% filter(Station == "MAL")
RelTempDiff_ANH <- relativetempdiff %>% filter(Station == "ANH")

```




##Plots
```{r}

## max differnce per station

ggplot(RelTempDiff_MRZ, aes(x = Hour, y = RelTempDiff)) + geom_point() 

ggplot(RelTempDiff_RRI, aes(x = Hour, y = RelTempDiff)) + geom_point()

ggplot(RelTempDiff_MAL, aes(x = Hour, y = RelTempDiff)) + geom_point()

ggplot(RelTempDiff_ANH, aes(x = Hour, y = RelTempDiff)) + geom_point()

### now plot all stations together with their relative temperature difference

ggplot(relativetempdiff, aes(x = Hour, y = RelTempDiff)) + geom_point() + facet_wrap(~Station)

```

Look at year differences
```{r}
# All stations
ggplot(relativetempdiff) + geom_jitter(aes(x = julian, y = RelTempDiff, color = fWY)) + facet_wrap(~Station)

# Julian-WY
# 2017 interesting
# Note 2020 and 2012 have some missing data?
ggplot(relativetempdiff) + geom_smooth(aes(x = julian, y = RelTempDiff, color = fWY), method = "loess") + facet_wrap(~Station)+ scale_color_viridis(discrete = TRUE) + 
  theme(strip.text = element_text(size = 15),
        axis.text = element_text(size = 15))

# Hour-WY
# Not much difference. 2012 and 2020 may be off because of aformementioned missing data. 
ggplot(relativetempdiff) + geom_smooth(aes(x = Hour, y = RelTempDiff, color = fWY), method = "loess") + facet_wrap(~Station) + scale_color_viridis(discrete = TRUE) + 
  theme(strip.text = element_text(size = 15),
        axis.text = element_text(size = 15))
```


## Models
```{r}
### run models for each station use as results interpretation








## original models below
modelMAL <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_MAL)
modelMRZ <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_MRZ)
modelRRI <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_RRI)
### now let's look at the model outputs (will put into a table)

summary(modelANH)
summary(modelMAL)
summary(modelMRZ)
summary(modelRRI)
```


MRZ
```{r}

##adjusting model
RelTempDiff_MRZ = filter(RelTempDiff_MRZ, !is.na(TempDiffLag), !is.na(RelTempDiff), !is.na(TempDiffLag2))


modelMRZ1 <- glm(RelTempDiff ~ sjulian + sHour + TempDiffLag + fYear , data = RelTempDiff_MRZ)

modelMRZ2 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear , data = RelTempDiff_MRZ)

modelMRZ3 <- glm(RelTempDiff ~ sjulian + sHour + + fYear:sjulian + TempDiffLag  , data = RelTempDiff_MRZ)

modelMRZ4 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear:sjulian , data = RelTempDiff_MRZ)

AIC(modelMRZ1, modelMRZ2, modelMRZ3, modelMRZ4)

summary(modelMRZ2)

# Validation
par(mfrow = c(2,2))
plot(modelMRZ2)

#R2
with(summary(modelMRZ2), 1 - deviance/null.deviance)
```



# RRI

What is the relative temperature difference at RRI? 
```{r}

##adjusting model
RelTempDiff_RRI = filter(RelTempDiff_RRI, !is.na(TempDiffLag), !is.na(RelTempDiff), !is.na(TempDiffLag2))


modelRRI1 <- glm(RelTempDiff ~ sjulian + sHour + TempDiffLag + fYear , data = RelTempDiff_RRI)

modelRRI2 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear , data = RelTempDiff_RRI)

modelRRI3 <- glm(RelTempDiff ~ sjulian + sHour + + fYear:sjulian + TempDiffLag  , data = RelTempDiff_RRI)

modelRRI4 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear:sjulian , data = RelTempDiff_RRI)

modelRRI5 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear:sjulian , data = RelTempDiff_RRI)

AIC(modelRRI1, modelRRI2, modelRRI3, modelRRI4)

summary(modelRRI4)




# Validation
par(mfrow = c(2,2))
plot(modelRRI4)
plot(hist(resid(modelRRI4)))

#R2
with(summary(modelRRI4), 1 - deviance/null.deviance)
```

GAMs - Model RRI and MRZ only 
```{r}


# https://noamross.github.io/gams-in-r-course/
  
# autoregressive
# gamm() - incorporating random effects and autocorrelation
  # look into nlme for description of autocorrelation function
  # arma, AR1
  # look up random effect notation in nlme
  # gamm model predictions - gratia
# RelTempDiff ~ interaction(julian, Hour) + re(fWY) + autocorrelation 

str(RelTempDiff_RRI)

# Use normal smooth and separate variables
gamRRI1 <- bam(RelTempDiff ~ s(julian, bs = "cc", k = 25) + s(Hour, bs = "cc", k = 15) + fWY, data = RelTempDiff_RRI, method = "REML")
par(mfrow = c(2,2))
gam.check(gamRRI1)

# Use tensor smooth for interactions of different scales
gamRRI2 <- bam(RelTempDiff ~ te(julian, Hour, k = c(15, 10), bs = c("cc")) + fWY, data = RelTempDiff_RRI, method = "REML")
par(mfrow = c(2,2))
gam.check(gamRRI2)
par(mfrow = c(1,1))
vis.gam(x = gamRRI2,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# Family = scat
gamRRI2b <- bam(RelTempDiff ~ te(julian, Hour, k = c(15,10), bs = "cc") + fWY, data = RelTempDiff_RRI, family = scat, method = "REML")
summary(gamRRI2b)
gam.check(gamRRI2b)
vis.gam(x = gamRRI2b,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# Include all 3
gamRRI3 <- bam(RelTempDiff ~ te(julian, Hour, fWY, d = c(2, 1), k = c(15,10), bs = c("cc", "tp")), data = RelTempDiff_RRI, family = scat, method = "REML")
gam.check(gamRRI3)


# Interaction with different levels
gamRRI4 <- bam(RelTempDiff ~ te(julian, Hour, by = fWY, k = c(12,12), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, AR.start=RelTempDiff_RRI$TempDiffLag, discrete = TRUE, family = scat, method = "REML")
par(mfrow = c(2,2))
gam.check(gamRRI4)
par(mfrow = c(1,1))
vis.gam(x = gamRRI4,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")
summary(gamRRI4)


# Random effect of year
gamRRI5 <- bam(RelTempDiff ~ te(julian, Hour, k = c(15,10), bs = "cc") + s(fWY, bs = "re"), data = RelTempDiff_RRI, family = scat, method = "REML")
summary(gamRRI5)
par(mfrow = c(2,2))
gam.check(gamRRI5)
par(mfrow = c(1,1))
vis.gam(x = gamRRI5,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# center and standardize TempDiffLag, easier for predictions
bam(Temperature_difference ~ te(Julian_day_s, Hour, by = fWaterYear) + fWaterYear, bs=c("cc","cc"))

# bam and gam random effects
+ s(fWaterYear,bs="re")
    # tp is default
    # cc = cyclic smooth
    # by = doesn't need a smooth
    # by = will make a smoother for each WY
    # factor smooth interaction: pooling effects by WY (see paper)

# Add WY 
# Check fit
# bam and gam have their own functions for model predictions
# gam.check() for model validation 

```

Create anomaly using model of surface data. Add anomaly to data. 
Use lowest k possible - don't want it to be too fitted.
```{r}
gamAnomaly <- bam(Surface~te(julian,Hour, k = c(5,5), bs = c("cc", "cc")), 
                         data = RelTempDiff_RRI,
                         family = scat, method = "fREML",
                         nthreads = 3,
                         discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gamAnomaly)
acf(resid(gamAnomaly))
par(mfrow = c(1,1))
plot(gamAnomaly, all.terms = TRUE, pages = 1)

# data-fitted values is type = response
# Use residuals from surface temperature as Anomaly 

RelTempDiff_RRI <- RelTempDiff_RRI%>%
  mutate(Anomaly = resid(gamAnomaly, type = "response"))

range(RelTempDiff_RRI$Anomaly)
```

Original anomaly
```{r}
RelTempDiff_RRI <- RelTempDiff_RRI %>%
  group_by(julian, Hour) %>%
  mutate(meanTemp = mean(Surface),
         Anomaly2 = Surface-meanTemp) %>%
  ungroup()

str(RelTempDiff_RRI)
hist(RelTempDiff_RRI$RelTempDiff)
```

Simple separated model - what do each of the parameters show?
```{r}
gamSimp <- bam(RelTempDiff~ s(julian, k = 15, bs = "cc") + s(Hour, k = 6, bs = "cc") + s(Anomaly, k = 6, bs = "tp"), data = RelTempDiff_RRI, family = scat, method = "fREML", nthreads = 3, discrete = TRUE)

gam.check(gamSimp)
r1 = acf(resid(gRRI1a),  plot=FALSE)$acf[2]
acf(resid(gamSimp))
pacf(resid(gamSimp))
par(mfrow = c(1,1))
plot(gamSimp, all.terms = TRUE, pages = 1)

```


Model with anomaly
```{r}
gamRRI1 <- bam(RelTempDiff~ te(julian, Hour, Anomaly,  k = c(12,6,5), bs = c("cc", "cc", "tp")), data = RelTempDiff_RRI,family = scat,method = "fREML", nthreads = 3, discrete = TRUE)

par(mfrow=c(2,2))
gam.check(gamRRI1)
par(mfrow=c(1,1))
vis.gam(x = gamRRI1,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour", type = "response")

```

Predictions
```{r}
newdataRRI <- expand.grid(#Create all combinations of predictor variables
                       julian = with(RelTempDiff_RRI, min(julian):max(julian)),
                       Anomaly = c(-3, -1.5, 0, 1.5, 3),
                       Hour = 1:24) %>%
                       # Standardize each variable based on full dataset for model
          mutate(julian_s=(julian-mean(RelTempDiff_RRI$julian, na.rm=T))/sd(RelTempDiff_RRI$julian, na.rm=T),
                 Hour_s=(Hour-mean(RelTempDiff_RRI$Hour, na.rm=T))/sd(RelTempDiff_RRI$Hour, na.rm=T),
                 Anomaly_s=(Anomaly-mean(RelTempDiff_RRI$Anomaly, na.rm=T))/sd(RelTempDiff_RRI$Anomaly, na.rm=T))

gamRRI1_pred<-predict(gamRRI1, newdata=newdataRRI, type="terms", se.fit=TRUE, discrete=T)
```

Plot predictions
```{r}
library(viridis)
library(grid)
library(gridExtra)
library(metR)

predictions <- data.frame(gamRRI1_pred$fit, gamRRI1_pred$se.fit)
colnames(predictions) <- c("fit", "se.fit")
range(gamRRI1_pred$fit)
RRIPlot <- cbind(newdataRRI, predictions) %>%
  mutate(fit = round(fit,2),
         se.fit = round(se.fit,2))


# How does Anomaly compare with original Anomaly? Pretty close to linear.
ggplot(RelTempDiff_RRI, aes(Anomaly, Anomaly2)) + geom_point() + geom_smooth(method = "lm")
# Are there only certain years that reached anomaly of -1.5? Two primary cool years - 2017, 2019
ggplot(RelTempDiff_RRI, aes(x = fWY, y = Anomaly, color = fWY)) + geom_boxplot() 
ggplot(subset(RelTempDiff_RRI, Anomaly > -3 & Anomaly < 3), aes(x = Anomaly, y = RelTempDiff, color = fWY), alpha = 0.3) + geom_jitter() + scale_color_viridis(discrete = TRUE)


# Is reltempdiff lower during lower anomalies? Yes but specifically around -1.5.
v1 <- ggplot(subset(RelTempDiff_RRI, Anomaly > -3 & Anomaly < 3), aes(x = Anomaly, y = RelTempDiff, color = julian)) + geom_jitter() + scale_color_viridis()
v2 <- ggplot(RRIPlot, aes(x = Anomaly, y = fit, color = julian)) + geom_jitter() + scale_color_viridis()
grid.arrange(v1,v2, nrow = 1)

breaks = seq(-3,1, by = 0.2)

# Plotting function
AnomalyPlot <- function(df = RRIPlot, Anomaly = 0) {
  Anomaly = enquo(Anomaly)
  
  dplyr::filter(df, Anomaly == UQ(Anomaly)) %>%
    ggplot(mapping = aes(x = julian, y = Hour, z = fit)) +
    geom_raster(mapping = aes(fill = fit)) + scale_fill_viridis() +
    geom_contour(colour = "white") +
    geom_text_contour(stroke = 0.2, breaks = breaks, check_overlap = TRUE) +
    theme_classic() +
    theme(axis.text = element_text(size = 14))+
    labs(title = Anomaly)
}

# Make Plots
pvcool <-AnomalyPlot(RRIPlot, -3)
pcool <- AnomalyPlot(Anomaly = -1.5)
pavg <- AnomalyPlot(RRIPlot, Anomaly = 0)
pwarm <- AnomalyPlot(RRIPlot, Anomaly = 1.5)
pvwarm <- AnomalyPlot(RRIPlot, Anomaly = 3)

# Plots combined
grid.arrange(pvcool, pcool, pavg, pwarm, pvwarm, nrow = 2)
```


# MRZ

Create anomaly using model of surface data. Add anomaly to data. 
Use lowest k possible - don't want it to be too fitted.
```{r}
gamAnomaly2 <- bam(Surface~te(julian,Hour, k = c(5,5), bs = c("cc", "cc")), 
                         data = RelTempDiff_MRZ,
                         family = scat, method = "fREML",
                         nthreads = 3,
                         discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gamAnomaly2)
par(mfrow = c(1,1))
plot(gamAnomaly2, all.terms = TRUE, pages = 1)

# data-fitted values is type = response
# Use residuals from surface temperature as Anomaly 

RelTempDiff_MRZ <- RelTempDiff_MRZ%>%
  mutate(Anomaly = resid(gamAnomaly2, type = "response"))

range(RelTempDiff_MRZ$Anomaly)
```

Original anomaly
```{r}
RelTempDiff_MRZ <- RelTempDiff_MRZ %>%
  group_by(julian, Hour) %>%
  mutate(meanTemp = mean(Surface),
         Anomaly2 = Surface-meanTemp) %>%
  ungroup()

str(RelTempDiff_MRZ)
hist(RelTempDiff_MRZ$RelTempDiff)
```


Model with anomaly
```{r}
gamMRZ1 <- bam(RelTempDiff~ te(julian, Hour, Anomaly,  k = c(12,6,5), bs = c("cc", "cc", "tp")), data = RelTempDiff_MRZ,family = scat,method = "fREML", nthreads = 3, discrete = TRUE)

par(mfrow=c(2,2))
gam.check(gamMRZ1)
par(mfrow=c(1,1))
vis.gam(x = gamMRZ1,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour", type = "response")

```

Predictions
```{r}
newdataMRZ <- expand.grid(#Create all combinations of predictor variables
                       julian = with(RelTempDiff_MRZ, min(julian):max(julian)),
                       Anomaly = c(-3, -1.5, 0, 1.5, 3),
                       Hour = 1:24) %>%
                       # Standardize each variable based on full dataset for model
          mutate(julian_s=(julian-mean(RelTempDiff_MRZ$julian, na.rm=T))/sd(RelTempDiff_MRZ$julian, na.rm=T),
                 Hour_s=(Hour-mean(RelTempDiff_MRZ$Hour, na.rm=T))/sd(RelTempDiff_MRZ$Hour, na.rm=T),
                 Anomaly_s=(Anomaly-mean(RelTempDiff_MRZ$Anomaly, na.rm=T))/sd(RelTempDiff_MRZ$Anomaly, na.rm=T))

gamMRZ1_pred<-predict(gamMRZ1, newdata=newdataMRZ, type="terms", se.fit=TRUE, discrete=T)
```

Plot predictions
```{r}
library(viridis)
library(grid)
library(gridExtra)
library(metR)

predictions2 <- data.frame(gamMRZ1_pred$fit, gamMRZ1_pred$se.fit)
colnames(predictions2) <- c("fit", "se.fit")
range(gamMRZ1_pred$fit)
MRZPlot <- cbind(newdataMRZ, predictions2) %>%
  mutate(fit = round(fit,2),
         se.fit = round(se.fit,2))


# How does Anomaly compare with original Anomaly? Pretty close to linear.
ggplot(RelTempDiff_MRZ, aes(Anomaly, Anomaly2)) + geom_point() + geom_smooth(method = "lm")
# Are there only certain years that reached anomaly of -1.5? 
ggplot(RelTempDiff_MRZ, aes(x = fWY, y = Anomaly, color = fWY)) + geom_boxplot() 
ggplot(subset(RelTempDiff_MRZ, Anomaly > -3 & Anomaly < 3), aes(x = Anomaly, y = RelTempDiff, color = fWY), alpha = 0.3) + geom_jitter() + scale_color_viridis(discrete = TRUE)


# Is reltempdiff lower during lower anomalies? No. much lower during high anomalies.
vis1 <- ggplot(subset(RelTempDiff_MRZ, Anomaly > -3 & Anomaly < 3), aes(x = Anomaly, y = RelTempDiff, color = julian)) + geom_jitter() + scale_color_viridis()
vis2 <- ggplot(MRZPlot, aes(x = Anomaly, y = fit, color = julian)) + geom_jitter() + scale_color_viridis()
grid.arrange(vis1,vis2, nrow = 1)

breaks = seq(-3,1, by = 0.2)

# Plotting function
AnomalyPlot <- function(df = RRIPlot, Anomaly = 0) {
  Anomaly = enquo(Anomaly)
  
  dplyr::filter(df, Anomaly == UQ(Anomaly)) %>%
    ggplot(mapping = aes(x = julian, y = Hour, z = fit)) +
    geom_raster(mapping = aes(fill = fit)) + scale_fill_viridis() +
    geom_contour(colour = "white") +
    geom_text_contour(stroke = 0.2, breaks = breaks, check_overlap = TRUE) +
    theme_classic() +
    theme(axis.text = element_text(size = 14))+
    labs(title = Anomaly)
}

# Make Plots
pvcool2 <-AnomalyPlot(MRZPlot, -3)
pcool2 <- AnomalyPlot(MRZPlot, Anomaly = -1.5)
pavg2 <- AnomalyPlot(MRZPlot, Anomaly = 0)
pwarm2 <- AnomalyPlot(MRZPlot, Anomaly = 1.5)
pvwarm2 <- AnomalyPlot(MRZPlot, Anomaly = 3)

# Plots combined
grid.arrange(pvcool2, pcool2, pavg2, pwarm2, pvwarm2, nrow = 2)
```














Do I need to standardize julian day or Hour?

```{r}
# Tell it what the starting event is
RelTempDiff_RRI = start_event(as.data.frame(RelTempDiff_RRI), column="Datetime", event=c("Station"), label.event="Event")

# Keep anomaly k value low in model
# Model without autocorrelation
gamRRI_0 <- bam(RelTempDiff~ te(julian, Hour, Anomaly,  k = c(12,6,6), bs = c("cc", "cc", "tp")), data = RelTempDiff_RRI, 
                family = scat, 
                method = "fREML", 
                nthreads = 3, 
                discrete = TRUE)
# Plot results for anomalies -1.5, 0, and 1.5



# Calculate rho
rAn = acf(resid(gamRRI_0),  plot=FALSE)$acf[2]

# Check model
par(mfrow = c(1,2))
acf(resid(gamRRI_0))
pacf(resid(gamRRI_0))
par(mfrow=c(2,2))
gam.check(gamRRI_0)


# Model using rho from above
gamRRI <- bam(RelTempDiff~ te(julian, Hour, Anomaly, k = c(12,6,16), bs = c("cc", "cc", "tp")), data = RelTempDiff_RRI, 
            family = scat, 
            method = "fREML", 
            rho = rAn, 
            AR.start = RelTempDiff_RRI$start.event, 
            nthreads = 3, 
            discrete = TRUE)

# Check model
par(mfrow = c(1,2))
acf(resid(gamRRI))
pacf(resid(gamRRI))
par(mfrow = c(2,2))
gam.check(gamRRI)
summary(gamRRI)
par(mfrow = c(1,1))
plot(gamRRI, all.terms = TRUE, pages = 1)
vis.gam(x = gamRRI,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour", type = "response")

save(gamRRI_0, gamRRI, file = "gamRRIAnomaly.RData")
load("gamRRIAnomaly.RData")
```

julian by TOD
```{r}
gamRRI <- bam(RelTempDiff~ te(julian, Hour, Anomaly, k = c(12,6,16), bs = c("cc", "cc", "tp")), data = RelTempDiff_RRI, 
            family = scat, 
            method = "fREML", 
            rho = rAn, 
            AR.start = RelTempDiff_RRI$start.event, 
            nthreads = 3, 
            discrete = TRUE)
```

julian by Anomaly 
```{r}
mRRI1 <- bam(RelTempDiff~ te(julian, Anomaly, by = TOD, k = c(12,6), bs = c("cc""tp")) + s(TOD), data = RelTempDiff_RRI, 
            family = scat, 
            method = "fREML", 
            rho = rAn, 
            AR.start = RelTempDiff_RRI$start.event, 
            nthreads = 3, 
            discrete = TRUE)
```











Differencing the data - this doesn't work
```{r}
df <- RelTempDiff_RRI %>%
  arrange(Datetime) %>%
  mutate(diff1 = c(NA,diff(RelTempDiff)))

gamRRI_diff0 <- bam(RelTempDiff~ te(julian, Hour, Anomaly,  k = c(12,6,16), bs = c("cc", "cc", "tp")), data = df, 
                family = scat, 
                method = "fREML", 
                nthreads = 3, 
                discrete = TRUE,
                na.action = na.omit)

# Calculate rho
par(mfrow = c(1,2))
acf(resid(gamRRI_diff0))
pacf(resid(gamRRI_diff0))
rAn = acf(resid(gamRRI_diff0),  plot=FALSE)$acf[2]
par(mfrow=c(2,2))
gam.check(gamRRI_diff0)
```


corARMA
```{r}
library(nlme)
gammRRI <- gamm(RelTempDiff~ te(julian, Hour, Anomaly, k = c(12,6,16), bs = c("cc", "cc", "tp")), data = RelTempDiff_RRI, 
            family = scat, 
            method = "fREML", 
            correlation = corARMA())


```



Look at the anomaly values. 2015 should have higher ones, 2017 should have lower ones.
```{r}
ggplot(RRI_pred, aes(x = factor(Month), y = Anomaly)) + geom_boxplot() + facet_wrap(~fWY)

ggplot(RRI_pred, aes(x = factor(fWY), y = Anomaly)) + geom_boxplot() 

ggplot(RRI_pred, aes(x = Datetime, y = Anomaly)) + geom_point()

RelTempDiff_RRI <- left_join(RelTempDiff_RRI, RRI_pred)
```


Playing with time series
```{r}

library(timetk)
library(feasts)
library(forecast)
dataset <- as_tsibble(RelTempDiff_RRI, index = Datetime) %>%
  filter(Year >15)
dataset %>% autoplot(RelTempDiff)
dataImpute <- ts_impute_vec(dataset$RelTempDiff)
dataset %>% timetk::plot_seasonal_diagnostics(.date_var = Datetime, .value = RelTempDiff)
dataset %>% plot_stl_diagnostics(.date_var = Datetime, .value = RelTempDiff)
tsdata <- ts(dataset$RelTempDiff, frequency = 8760, start = c(2015, 1) )
autoarima1 <- auto.arima(tsdata)
```




Alternate models

```{r}
library(itsadug)

##adjusting model
# RelTempDiff_RRI = filter(RelTempDiff_RRI, !is.na(TempDiffLag), !is.na(RelTempDiff), !is.na(TempDiffLag2))
  
# Determine rho by first running the model without the AR term
gRRI1a <- bam(RelTempDiff~ te(julian, Hour, k = c(6, 12), bs = c("cc", "cc")), data = RelTempDiff_RRI, 
            family = scat, method = "fREML", nthreads = 3, discrete = TRUE)

r1 = acf(resid(gRRI1a),  plot=FALSE)$acf[2]
acf(resid(gRRI1a))
pacf(resid(gRRI1a))

par(mfrow = c(2,2))
gam.check(gRRI1a)

gRRI1 <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")), data = RelTempDiff_RRI, 
            family = scat, method = "fREML", rho = r1, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)

par(mfrow = c(2,2))
gam.check(gRRI1)
acf(resid(gRRI1)) # This looks the same

par(mfrow = c(1,1))
plot(gRRI1, all.terms = TRUE, pages = 1)
summary(gRRI1)
vis.gam(x = gRRI1,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")




# Add year in as a linear term
gRRI2a <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 20), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, 
            family = scat, method = "fREML", nthreads = 3, discrete = TRUE)
r2 = acf(resid(gRRI2a),  plot=FALSE)$acf[2]
par(mfrow = c(2,2))
gam.check(gRRI2a)

gRRI2 <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, 
            family = scat, method = "fREML", rho = r2, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gRRI2)
par(mfrow = c(1,1))
plot(gRRI2, all.terms = TRUE, pages = 1)
summary(gRRI2)
vis.gam(x = gRRI2,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")


# Add year in as an interaction
gRRI3a <- bam(RelTempDiff ~ te(julian, Hour, by = fWY, k = c(20,12), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI,
             family = scat, method = "fREML", nthreads = 3, discrete = TRUE)
r3 = acf(resid(gRRI3a),  plot=FALSE)$acf[2]


par(mfrow = c(2,2))
gam.check(gRRI3a)


gRRI3 <- bam(RelTempDiff ~ te(julian, Hour, by = fWY, k = c(20,12), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI,
             family = scat, method = "fREML", rho = r3, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gRRI3)
par(mfrow = c(2,2))
acf(resid(gRRI3a))
pacf(resid(gRRI3a))

summary(gRRI3)
par(mfrow = c(1,1))
plot(gRRI3, all.terms = TRUE, pages = 1)
par(mfrow = c(2,2))
acf(resid(gRRI3))
pacf(resid(gRRI3))

summary(gRRI3)
par(mfrow = c(1,1))
vis.gam(x = gRRI3,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour") # Can I make plots by year?





# Add year in as a random effect

gRRI4a <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")) + s(fWY, bs = "re"), data = RelTempDiff_RRI, 
            family = scat, method = "fREML", nthreads = 3, discrete = TRUE)
r4 = acf(resid(gRRI4a),  plot=FALSE)$acf[2]
par(mfrow = c(2,2))
gam.check(gRRI4a)


gRRI4 <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, 
            family = scat, method = "fREML", rho = r4, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gRRI4)
plot(gRRI4, all.terms = TRUE, pages = 1)
summary(gRRI4)
vis.gam(x = gRRI4,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

acf(resid(gRRI4))


save(gRRI3a, gRRI3, file = "gamRRIWY.RData")


```



Plot models
#https://mfasiolo.github.io/mgcViz/articles/mgcviz.html
```{r}

```










Mixed Models
```{r}
library(lme4)
library(lmerTest)

modelmRRI1 <- lmer(RelTempDiff ~ sjulian + sHour + TempDiffLag + (1|fYear), data = RelTempDiff_RRI)

summary(modelmRRI1)

modelmRRI2 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + (1|fYear) , data = RelTempDiff_RRI)

# Validation
plot(modelmRRI1)
qqnorm(modelmRRI1)
qqline(modelmRRI1)

# https://stats.stackexchange.com/questions/76671/mixed-effect-model-validation
plot(modelmRRI1, resid(., scaled=TRUE) ~ fitted(.) | fYear, abline = 0)


```


Plot Results
https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_interactions.html
```{r}
library(sjPlot)
library(sjmisc)

# ggplot(relativetempdiff, aes(x = Hour, y = sHour)) + geom_point()
# 1 = 0, 24 midnight
# -1 = 12 noon

### JULIAN 
# ggplot(relativetempdiff, aes(x = julian, y = sjulian)) + geom_point()
## 1 = winter
## 0 = spring, fall
## -1 = summer
par(mfrow = c(2,1))
plot_model(modelRRI4, type= "int")
plot_model(modelRRI4, type= "pred", terms = c("sjulian", "fYear"))
plot_model(modelRRI4, type= "pred", terms = c("sjulian", "sHour", "fYear"))

# sequence of range of variables
# expand.grid to get every combination of different variables
# can include factors
# predict function to generate model predictions
# add confidence intervals, may need to convert se to CI
```







Take a look into models 
```{r}
par(mfrow = c(2,2))
visreg(modelANH)
visreg(modelANH,xvar = "sjulian", by = "sHour")
plot(modelANH)
### points on normal Q-Q to pull up
visreg(modelMAL)
plot(modelMAL)
acf(modelANH)

visreg(modelMRZ)
plot(modelMRZ)

visreg(modelRRI)
plot(modelRRI)
```

```{r}
### deeper look into each station with ggplot and then ggplotly

##ANH##


##looking at the interaction between sjulian and shour
ggplot(RelTempDiff_ANH, aes(x= sjulian, y = sHour))+ geom_point() ## not a great plot
## with hour as a factor
ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(Hour)))+ geom_point(size = .4)
## better but still not great
###plotly to see the data clearer
#first with Hour
plotANHhour <- ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(Hour)))+ geom_point(size = .4) 
## need to add the station as the legend for quick view#

ggplotly(plotANHhour)
# now with TOD as a factor 
plotANHTOD <- ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotANHTOD)

## TOD seems like it will be easier for us to use for our figures for the viewers, but the models will be run hourly

## RRI##
##with TOD
plotRRITOD <- ggplot(RelTempDiff_RRI, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotRRI)

## MAL##
plotMALTOD <- ggplot(RelTempDiff_MAL, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotMALTOD)

##MRZ##
plotMRZTOD <- ggplot(RelTempDiff_MRZ, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotMRZTOD)


## Suggestions for making the data easier to view and see: color code by TOD (change groups) add a loess line with gmsmooth
## now going to try to plot all the TOD temp differences in a 4 panel
figure <- ggarrange(plotANHTOD, plotMALTOD, plotMRZTOD, plotRRITOD, labels = c("Antioch", "Mallard", "Martinez", "Rough and Ready Island"), ncol = 2, nrow = 2)
## didnt work I dont know where ggarrange function is I thought from the tutorial it looks like it was from ggplot
## now lets just try using the facet wrap

plotANHTOD + facet_wrap(plotMALTOD) + facet_wrap(plotMRZTOD) + facet_wrap(plotRRITOD) 

# Nope am missing the end part of the argument?


```

*Cat's notes here:*
To use facet_wrap you need all of the data to be in one dataset. So use your original dataset.
```{r}

## change the order of the TOD
relativetempdiff$TOD <- as.factor(relativetempdiff$TOD)
relativetempdiff$TOD<-  factor(relativetempdiff$TOD, levels(relativetempdiff$TOD)[c(2,4,1,3)])
levels(relativetempdiff$TOD)

### subset data to use when making the plots before finalized
relativetempdiff_sample <- relativetempdiff %>% sample_frac(.1)

### plot with facet wrap




plotTOD <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_point(aes(color = TOD),size = .6) + facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +

  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) +
    guides(color = guide_legend(title = "Time of Day", override.aes=list(size = 4)))

plotTOD

## adding trend lines
plotTODlines <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_point(aes(color = TOD),size = 0.02, alpha = .1) +
geom_smooth(aes(color = TOD), method = "loess", se = F, fullrange = T) +
  facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(title = "Time of Day", override.aes = list(size=4)))

plotTODlines

## just the trend lines
plotlinesonly <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_smooth(aes(color = TOD), 
  method = "loess", se = T, fullrange = T) +
  facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(title = "Time of Day", override.aes = list(size=4)))

plotlinesonly
```

```{r}
plotTODLine <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_smooth(aes(color = TOD), method = "loess", se = TRUE) + facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  labs(y = "Relative Temperature Difference (C)", 
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) +
    guides(color = guide_legend(title = "Time of Day", override.aes=list(size = 4)))
plotTODLine
```


For your ggarrange, you had a typo in one of the plots and you need to call the plot. Here is your result, which doesn't look as good as the facet. 

```{r}
figure
```

I have not found the perfect solution for making multi-panel plots, but if you use facet, you can annotate each of your plots.

https://r-graphics.org/recipe-annotate-facet
```{r}
# Make a data frame for your labels
plot_labels <- data.frame(Station = c("ANH", "MAL", "MRZ", "RRI"), label = c("A", "B", "C", "D"))

# Add those labels to your plot
plotTOD + labs(x = "Julian Day", y = "Relative Temperature Diff (C)") + 
  geom_text(x = 350, y = -3.5, aes(label = label), size =6, data = plot_labels)
```
Nans and summary stats, model results table

```{r}
summary(relativetempdiff)

stargazer(modelANH, modelMAL, modelMRZ, modelRRI, type = "html", column.labels = c("ANH", "MAL", "MRZ", "RRI"), title = "Continuous Dataset Model Results", out ="allglmdpethmodeloutputs.html")

```
model results figures
```{r}
par(mfrow = c(2,2))
visreg(modelANH)
plot(modelANH)


```

