---
title: "Relative Temperature Difference"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---
#Libraries needed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
### load all libraries, added all libraries from previous depthdatavisualiztion.rmd whether we necessarily needed them or not.
library(tidyverse)
library(lubridate)
library(readr)
library(plotly)
library(tidyr)
library(visreg)
library(itsadug)
library(mgcv)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(viridis)
library(stargazer)
```

WD, Read in Data, Separate by Station
```{r}
## set wd, read in CSV relative tempdiff, bring over all data
relativetempdiff <- readRDS("DepthAnalysis/Data/RelativeTempDiff2.rds")
## relativetempdiff has all of our parameters: julian day, WY, sinejulian, sinehour etc and is the correct timeframe

relativetempdiff <- relativetempdiff %>% select(-Stress)

# Add factor variables
relativetempdiff$fWY = factor(relativetempdiff$WY)
relativetempdiff$fYear = factor(relativetempdiff$Year)

# Filter to just water years 2013-2019 
relativetempdiff <- filter(relativetempdiff, WY < 2020 & WY > 2012)

# filter to only those on the hour
relativetempdiff$minute <- minute(relativetempdiff$Datetime)
relativetempdiff <- filter(relativetempdiff, minute == "0")

#no NAs
relativetempdiff <- filter(relativetempdiff, !is.na(RelTempDiff))

info <- relativetempdiff %>%
  group_by(Station, fWY) %>%
  summarize(n =  n())

## filter the relativetempdiff for each station so I can bring in the models or try the models first
RelTempDiff_MRZ <- relativetempdiff %>% filter(Station == "MRZ")
RelTempDiff_RRI <- relativetempdiff %>% filter(Station == "RRI")
RelTempDiff_MAL <- relativetempdiff %>% filter(Station == "MAL")
RelTempDiff_ANH <- relativetempdiff %>% filter(Station == "ANH")

```




##Plots
```{r}

## max differnce per station

ggplot(RelTempDiff_MRZ, aes(x = Hour, y = RelTempDiff)) + geom_point() 

ggplot(RelTempDiff_RRI, aes(x = Hour, y = RelTempDiff)) + geom_point()

ggplot(RelTempDiff_MAL, aes(x = Hour, y = RelTempDiff)) + geom_point()

ggplot(RelTempDiff_ANH, aes(x = Hour, y = RelTempDiff)) + geom_point()

### now plot all stations together with their relative temperature difference

ggplot(relativetempdiff, aes(x = Hour, y = RelTempDiff)) + geom_point() + facet_wrap(~Station)

```

Look at year differences
```{r}
# All stations
ggplot(relativetempdiff) + geom_jitter(aes(x = julian, y = RelTempDiff, color = fWY)) + facet_wrap(~Station)

# Julian-WY
# 2017 interesting
# Note 2020 and 2012 have some missing data?
ggplot(relativetempdiff) + geom_smooth(aes(x = julian, y = RelTempDiff, color = fWY), method = "loess") + facet_wrap(~Station)+ scale_color_viridis(discrete = TRUE) + 
  theme(strip.text = element_text(size = 15),
        axis.text = element_text(size = 15))

# Hour-WY
# Not much difference. 2012 and 2020 may be off because of aformementioned missing data. 
ggplot(relativetempdiff) + geom_smooth(aes(x = Hour, y = RelTempDiff, color = fWY), method = "loess") + facet_wrap(~Station) + scale_color_viridis(discrete = TRUE) + 
  theme(strip.text = element_text(size = 15),
        axis.text = element_text(size = 15))
```


## Models
```{r}
### run models for each station use as results interpretation








## original models below
modelMAL <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_MAL)
modelMRZ <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_MRZ)
modelRRI <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag , data = RelTempDiff_RRI)
### now let's look at the model outputs (will put into a table)

summary(modelANH)
summary(modelMAL)
summary(modelMRZ)
summary(modelRRI)
```


MRZ
```{r}

##adjusting model
RelTempDiff_MRZ = filter(RelTempDiff_MRZ, !is.na(TempDiffLag), !is.na(RelTempDiff), !is.na(TempDiffLag2))


modelMRZ1 <- glm(RelTempDiff ~ sjulian + sHour + TempDiffLag + fYear , data = RelTempDiff_MRZ)

modelMRZ2 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear , data = RelTempDiff_MRZ)

modelMRZ3 <- glm(RelTempDiff ~ sjulian + sHour + + fYear:sjulian + TempDiffLag  , data = RelTempDiff_MRZ)

modelMRZ4 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear:sjulian , data = RelTempDiff_MRZ)

AIC(modelMRZ1, modelMRZ2, modelMRZ3, modelMRZ4)

summary(modelMRZ2)

# Validation
par(mfrow = c(2,2))
plot(modelMRZ2)

#R2
with(summary(modelMRZ2), 1 - deviance/null.deviance)
```



RRI
```{r}

##adjusting model
RelTempDiff_RRI = filter(RelTempDiff_RRI, !is.na(TempDiffLag), !is.na(RelTempDiff), !is.na(TempDiffLag2))


modelRRI1 <- glm(RelTempDiff ~ sjulian + sHour + TempDiffLag + fYear , data = RelTempDiff_RRI)

modelRRI2 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear , data = RelTempDiff_RRI)

modelRRI3 <- glm(RelTempDiff ~ sjulian + sHour + + fYear:sjulian + TempDiffLag  , data = RelTempDiff_RRI)

modelRRI4 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear:sjulian , data = RelTempDiff_RRI)

modelRRI5 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + fYear:sjulian , data = RelTempDiff_RRI)

AIC(modelRRI1, modelRRI2, modelRRI3, modelRRI4)

summary(modelRRI4)




# Validation
par(mfrow = c(2,2))
plot(modelRRI4)
plot(hist(resid(modelRRI4)))

#R2
with(summary(modelRRI4), 1 - deviance/null.deviance)
```

GAMs - Model RRI and MRZ only 
```{r}
library(mgcv)

# https://noamross.github.io/gams-in-r-course/
  
# autoregressive
# gamm() - incorporating random effects and autocorrelation
  # look into nlme for description of autocorrelation function
  # arma, AR1
  # look up random effect notation in nlme
  # gamm model predictions - gratia

str(RelTempDiff_RRI)

# RRI Model
# What is the relative temperature difference at RRI? 

# RelTempDiff ~ interaction(julian, Hour) + re(fWY) + autocorrelation 



# Use normal smooth and separate variables
gamRRI1 <- bam(RelTempDiff ~ s(julian, bs = "cc", k = 25) + s(Hour, bs = "cc", k = 15) + fWY, data = RelTempDiff_RRI, method = "REML")
par(mfrow = c(2,2))
gam.check(gamRRI1)

# Use tensor smooth for interactions of different scales
gamRRI2 <- bam(RelTempDiff ~ te(julian, Hour, k = c(15, 10), bs = c("cc")) + fWY, data = RelTempDiff_RRI, method = "REML")
par(mfrow = c(2,2))
gam.check(gamRRI2)
par(mfrow = c(1,1))
vis.gam(x = gamRRI2,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# Family = scat
gamRRI2b <- bam(RelTempDiff ~ te(julian, Hour, k = c(15,10), bs = "cc") + fWY, data = RelTempDiff_RRI, family = scat, method = "REML")
summary(gamRRI2b)
gam.check(gamRRI2b)
vis.gam(x = gamRRI2b,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# Include all 3
gamRRI3 <- bam(RelTempDiff ~ te(julian, Hour, fWY, d = c(2, 1), k = c(15,10), bs = c("cc", "tp")), data = RelTempDiff_RRI, family = scat, method = "REML")
gam.check(gamRRI3)


# Interaction with different levels
gamRRI4 <- bam(RelTempDiff ~ te(julian, Hour, by = fWY, k = c(12,12), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, AR.start=RelTempDiff_RRI$TempDiffLag, discrete = TRUE, family = scat, method = "REML")
par(mfrow = c(2,2))
gam.check(gamRRI4)
par(mfrow = c(1,1))
vis.gam(x = gamRRI4,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")
summary(gamRRI4)


# Random effect of year
gamRRI5 <- bam(RelTempDiff ~ te(julian, Hour, k = c(15,10), bs = "cc") + s(fWY, bs = "re"), data = RelTempDiff_RRI, family = scat, method = "REML")
summary(gamRRI5)
par(mfrow = c(2,2))
gam.check(gamRRI5)
par(mfrow = c(1,1))
vis.gam(x = gamRRI5,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")




# center and standardize TempDiffLag, easier for predictions
gamMRZ1 <-  gam(RelTempDiff ~ te(julian, Hour, bs = "cc") + TempDiffLag + fWY, family = scat)

bam(Temperature_difference ~ te(Julian_day_s, Hour, by = fWaterYear) + fWaterYear, bs=c("cc","cc"))

# bam and gam random effects
+ s(fWaterYear,bs="re")
    # tp is default
    # cc = cyclic smooth
    # by = doesn't need a smooth
    # by = will make a smoother for each WY
    # factor smooth interaction: pooling effects by WY (see paper)

# Add WY 
# Check fit
# bam and gam have their own functions for model predictions
# gam.check() for model validation 

```

Temperature Anomaly

Do I need to standardize julian day or Hour?

```{r}
# Detecting anomaly

# Predict Surface Temperature
gAnRRIa <- bam(Surface~ te(julian, Hour, k = c(20, 10), 
                           bs = c("cc", "cc")), 
               data = RelTempDiff_RRI,
               method = "fREML", 
               nthreads = 3, 
               discrete = TRUE)

rAn = acf(resid(gAnRRIa),  plot=FALSE)$acf[2]

# Do I need autocorrelation in this model? 
gAnRRI <- bam(Temp~ te(julian, Hour, k = c(20, 12), 
                       bs = c("cc", "cc")), 
              data = SurfaceTempRRI, 
              method = "fREML", 
              rho = rAn, 
              AR.start = SurfaceTempRRI$start.event, 
              nthreads = 3, 
              discrete = TRUE)

gam.check(gAnRRI)
# Doesn't look very good. Can we still use this? 

vis.gam(x = gAnRRI,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# Look at predicted (fitted) values - is this the right thing to look at? 
predRRI <- as.data.frame(fitted.values(gAnRRI))
colnames(predRRI) <- "Fitted"
RRI_pred <- cbind(RelTempDiff_RRI, predRRI) 

# Calculate Anomaly by subtracting predicted (based on hour and julian day) from the actual temperature
RRI_pred <- RRI_pred %>%
  mutate(Anomaly = Temp-Fitted)

# Look at the anomaly values. 2015 should have higher ones, 2017 should have lower ones. 
ggplot(RRI_pred, aes(x = factor(Month), y = Anomaly)) + geom_boxplot() + facet_wrap(~fWY)

ggplot(RRI_pred, aes(x = factor(fWY), y = Anomaly)) + geom_boxplot() 

ggplot(RRI_pred, aes(x = Datetime, y = Anomaly)) + geom_point()

RelTempDiff_RRI <- left_join(RelTempDiff_RRI, RRI_pred)
```



```{r}
library(itsadug)

##adjusting model
# RelTempDiff_RRI = filter(RelTempDiff_RRI, !is.na(TempDiffLag), !is.na(RelTempDiff), !is.na(TempDiffLag2))

# Tell it what the starting event is
RelTempDiff_RRI = start_event(as.data.frame(RelTempDiff_RRI), column="Datetime", event=c("Station"), label.event="Event")
  
# Determine rho by first running the model without the AR term
gRRI1a <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")), data = RelTempDiff_RRI, 
            family = scat, method = "fREML", nthreads = 3, discrete = TRUE)
r1 = acf(resid(gRRI1a),  plot=FALSE)$acf[2]
par(mfrow = c(2,2))
gam.check(gRRI1a)

gRRI1 <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")), data = RelTempDiff_RRI, 
            family = scat, method = "fREML", rho = r1, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gRRI1)
par(mfrow = c(1,1))
plot(gRRI1, all.terms = TRUE, pages = 1)
summary(gRRI1)
vis.gam(x = gRRI1,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# Incorporate anomaly
gRRIAn <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 12), bs = c("cc", "cc")) + s(Residuals, k = 20, bs = "re"), data = RelTempDiff_RRI, 
            family = scat, method = "fREML", rho = 0.83, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)

gam.check(gRRIAn)

gRRIAn2 <- bam(RelTempDiff~ te(julian, Hour, Anomaly, k = c(20, 12, 20), bs = c("cc", "cc", "tp")), 
               data = RelTempDiff_RRI, 
               family = scat, 
               method = "fREML", 
               rho = 0.83, 
               AR.start = RelTempDiff_RRI$start.event, 
               nthreads = 3, 
               discrete = TRUE)
gam.check(gRRIAn2)

#https://mfasiolo.github.io/mgcViz/articles/mgcviz.html

# Add year in as a linear term
gRRI2a <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 20), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, 
            family = scat, method = "fREML", nthreads = 3, discrete = TRUE)
r2 = acf(resid(gRRI2a),  plot=FALSE)$acf[2]
par(mfrow = c(2,2))
gam.check(gRRI2a)

gRRI2 <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, 
            family = scat, method = "fREML", rho = r2, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gRRI2)
par(mfrow = c(1,1))
plot(gRRI2, all.terms = TRUE, pages = 1)
summary(gRRI2)
vis.gam(x = gRRI2,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")


# Add year in as an interaction
gRRI3a <- bam(RelTempDiff ~ te(julian, Hour, by = fWY, k = c(20,10), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI,
             family = scat, method = "fREML", nthreads = 3, discrete = TRUE)
r3 = acf(resid(gRRI3a),  plot=FALSE)$acf[2]
par(mfrow = c(2,2))
gam.check(gRRI3a)


gRRI3 <- bam(RelTempDiff ~ te(julian, Hour, by = fWY, k = c(20,10), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI,
             family = scat, method = "fREML", rho = r3, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gRRI3)
par(mfrow = c(1,1))
plot(gRRI3, all.terms = TRUE, pages = 1)
summary(gRRI3)
par(mfrow = c(1,1))
vis.gam(x = gRRI3,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour") # Can I make plots by year?




# Add year in as a random effect

gRRI4a <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 20), bs = c("cc", "cc")) + s(fWY, bs = "re"), data = RelTempDiff_RRI, 
            family = scat, method = "fREML", nthreads = 3, discrete = TRUE)
r4 = acf(resid(gRRI4a),  plot=FALSE)$acf[2]
par(mfrow = c(2,2))
gam.check(gRRI4a)


gRRI4 <- bam(RelTempDiff~ te(julian, Hour, k = c(20, 10), bs = c("cc", "cc")) + fWY, data = RelTempDiff_RRI, 
            family = scat, method = "fREML", rho = r4, AR.start = RelTempDiff_RRI$start.event, nthreads = 3, discrete = TRUE)
par(mfrow = c(2,2))
gam.check(gRRI4)
plot(gRRI4, all.terms = TRUE, pages = 1)
summary(gRRI4)
vis.gam(x = gRRI4,
        view = c("julian", "Hour"),
        color = "heat", plot.type = "contour")

# Can't check the autocorrelation?
acf(gRRI4)





```







Mixed Models
```{r}
library(lme4)
library(lmerTest)

modelmRRI1 <- lmer(RelTempDiff ~ sjulian + sHour + TempDiffLag + (1|fYear), data = RelTempDiff_RRI)

summary(modelmRRI1)

modelmRRI2 <- glm(RelTempDiff ~ sjulian + sHour + sjulian:sHour + TempDiffLag + (1|fYear) , data = RelTempDiff_RRI)

# Validation
plot(modelmRRI1)
qqnorm(modelmRRI1)
qqline(modelmRRI1)

# https://stats.stackexchange.com/questions/76671/mixed-effect-model-validation
plot(modelmRRI1, resid(., scaled=TRUE) ~ fitted(.) | fYear, abline = 0)


```


Plot Results
https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_interactions.html
```{r}
library(sjPlot)
library(sjmisc)

# ggplot(relativetempdiff, aes(x = Hour, y = sHour)) + geom_point()
# 1 = 0, 24 midnight
# -1 = 12 noon

### JULIAN 
# ggplot(relativetempdiff, aes(x = julian, y = sjulian)) + geom_point()
## 1 = winter
## 0 = spring, fall
## -1 = summer
par(mfrow = c(2,1))
plot_model(modelRRI4, type= "int")
plot_model(modelRRI4, type= "pred", terms = c("sjulian", "fYear"))
plot_model(modelRRI4, type= "pred", terms = c("sjulian", "sHour", "fYear"))

# sequence of range of variables
# expand.grid to get every combination of different variables
# can include factors
# predict function to generate model predictions
# add confidence intervals, may need to convert se to CI
```







Take a look into models 
```{r}
par(mfrow = c(2,2))
visreg(modelANH)
visreg(modelANH,xvar = "sjulian", by = "sHour")
plot(modelANH)
### points on normal Q-Q to pull up
visreg(modelMAL)
plot(modelMAL)
acf(modelANH)

visreg(modelMRZ)
plot(modelMRZ)

visreg(modelRRI)
plot(modelRRI)
```

```{r}
### deeper look into each station with ggplot and then ggplotly

##ANH##


##looking at the interaction between sjulian and shour
ggplot(RelTempDiff_ANH, aes(x= sjulian, y = sHour))+ geom_point() ## not a great plot
## with hour as a factor
ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(Hour)))+ geom_point(size = .4)
## better but still not great
###plotly to see the data clearer
#first with Hour
plotANHhour <- ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(Hour)))+ geom_point(size = .4) 
## need to add the station as the legend for quick view#

ggplotly(plotANHhour)
# now with TOD as a factor 
plotANHTOD <- ggplot(RelTempDiff_ANH, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotANHTOD)

## TOD seems like it will be easier for us to use for our figures for the viewers, but the models will be run hourly

## RRI##
##with TOD
plotRRITOD <- ggplot(RelTempDiff_RRI, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotRRI)

## MAL##
plotMALTOD <- ggplot(RelTempDiff_MAL, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotMALTOD)

##MRZ##
plotMRZTOD <- ggplot(RelTempDiff_MRZ, aes(x= julian, y = RelTempDiff, color = factor(TOD)))+ geom_point(size = .6)
ggplotly(plotMRZTOD)


## Suggestions for making the data easier to view and see: color code by TOD (change groups) add a loess line with gmsmooth
## now going to try to plot all the TOD temp differences in a 4 panel
figure <- ggarrange(plotANHTOD, plotMALTOD, plotMRZTOD, plotRRITOD, labels = c("Antioch", "Mallard", "Martinez", "Rough and Ready Island"), ncol = 2, nrow = 2)
## didnt work I dont know where ggarrange function is I thought from the tutorial it looks like it was from ggplot
## now lets just try using the facet wrap

plotANHTOD + facet_wrap(plotMALTOD) + facet_wrap(plotMRZTOD) + facet_wrap(plotRRITOD) 

# Nope am missing the end part of the argument?


```

*Cat's notes here:*
To use facet_wrap you need all of the data to be in one dataset. So use your original dataset.
```{r}

## change the order of the TOD
relativetempdiff$TOD <- as.factor(relativetempdiff$TOD)
relativetempdiff$TOD<-  factor(relativetempdiff$TOD, levels(relativetempdiff$TOD)[c(2,4,1,3)])
levels(relativetempdiff$TOD)

### subset data to use when making the plots before finalized
relativetempdiff_sample <- relativetempdiff %>% sample_frac(.1)

### plot with facet wrap




plotTOD <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_point(aes(color = TOD),size = .6) + facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +

  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) +
    guides(color = guide_legend(title = "Time of Day", override.aes=list(size = 4)))

plotTOD

## adding trend lines
plotTODlines <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_point(aes(color = TOD),size = 0.02, alpha = .1) +
geom_smooth(aes(color = TOD), method = "loess", se = F, fullrange = T) +
  facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(title = "Time of Day", override.aes = list(size=4)))

plotTODlines

## just the trend lines
plotlinesonly <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_smooth(aes(color = TOD), 
  method = "loess", se = T, fullrange = T) +
  facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(override.aes = list(size=4)))+
  labs(y = "Relative Temperature Difference (C)",
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) + guides(colour = guide_legend(title = "Time of Day", override.aes = list(size=4)))

plotlinesonly
```

```{r}
plotTODLine <- ggplot(relativetempdiff, aes(x= julian, y = RelTempDiff))+ geom_smooth(aes(color = TOD), method = "loess", se = TRUE) + facet_wrap(~Station) + 
  theme_bw() + theme(strip.text = element_text(size = 14),
                     axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14)) +
  labs(y = "Relative Temperature Difference (C)", 
       x = "Julian Day") +
  scale_color_viridis(discrete = TRUE) +
    guides(color = guide_legend(title = "Time of Day", override.aes=list(size = 4)))
plotTODLine
```


For your ggarrange, you had a typo in one of the plots and you need to call the plot. Here is your result, which doesn't look as good as the facet. 

```{r}
figure
```

I have not found the perfect solution for making multi-panel plots, but if you use facet, you can annotate each of your plots.

https://r-graphics.org/recipe-annotate-facet
```{r}
# Make a data frame for your labels
plot_labels <- data.frame(Station = c("ANH", "MAL", "MRZ", "RRI"), label = c("A", "B", "C", "D"))

# Add those labels to your plot
plotTOD + labs(x = "Julian Day", y = "Relative Temperature Diff (C)") + 
  geom_text(x = 350, y = -3.5, aes(label = label), size =6, data = plot_labels)
```
Nans and summary stats, model results table

```{r}
summary(relativetempdiff)

stargazer(modelANH, modelMAL, modelMRZ, modelRRI, type = "html", column.labels = c("ANH", "MAL", "MRZ", "RRI"), title = "Continuous Dataset Model Results", out ="allglmdpethmodeloutputs.html")

```
model results figures
```{r}
par(mfrow = c(2,2))
visreg(modelANH)
plot(modelANH)


```

