---
title: "ThresholdExceedanceFigure"
author: "Catarina Pien"
date: "9/22/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

Modified from Brian Mahardja 
https://github.com/bmahardja/Bottom_Surface_Temp_Analysis/blob/master/R_Continuous_Data_Plots.R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages
```{r}
library(tidyverse)
library(lubridate)
library(grid)
library(gridExtra)
library(viridis)
library(ggpubr)
library(scales)


# library(broom)
# library(rgdal)
# library(mgcv)
# library(AICcmodavg)
# library(sf)

# library(gtable)
# library(plotly)
# 
# require(spacetime)
# require(sp)
# require(gstat)
# require(itsadug)
# require(patchwork)
```

## Read in data
```{r}
tempdiff <- readRDS("DepthAnalysis/Data/RelativeTempDiff2.rds")
```

## Look at summary of annual means and completeness of datasets
```{r}
annual_summary <- tempdiff %>% 
  group_by(Year,Station) %>% 
  summarise(AnnualMean=mean(Surface),
            n = n()) %>%
  filter(!(Year %in% c(2012, 2020))) %>%ungroup()
```

```{r}
ggplot(annual_summary, aes(x = Year, y = Station)) + geom_tile(aes(fill = n, color = AnnualMean)) + scale_fill_viridis()
```

## Make new dataset for 2015, calculate whether suitable and percent of each day that is suitable
```{r}
temp_2015 <- tempdiff %>%
  ungroup() %>%
  filter(Year == 2015) %>%
  filter(Station %in% c("MRZ", "RRI")) %>%
  #pivot_longer(values_to = "Temp", names_to = "Type", cols = c(4,5,9)) %>%
  mutate(Suitable_DSM_S = ifelse(Surface<25, 1, 0),
         Suitable_DSM_B = ifelse(Bottom<25, 1, 0),
         Suitable_CHN_S = ifelse(Surface<20, 1, 0),
         Suitable_CHN_B = ifelse(Bottom<20, 1, 0)) 

str(temp_2015)
```

```{r}
temp_percent <- temp_2015 %>%
  group_by(Station, Date) %>%
  summarize(Percent_DSM_S = mean(Suitable_DSM_S),
            Percent_DSM_B = mean(Suitable_DSM_B),
         Percent_CHN_S = mean(Suitable_CHN_S),
         Percent_CHN_B = mean(Suitable_CHN_B)) %>%
  mutate(Diff_DSM = Percent_DSM_B-Percent_DSM_S,
         Diff_CHN = Percent_CHN_B-Percent_CHN_S) %>%
  ungroup()

temp_percent_long <- temp_percent %>%
  pivot_longer(cols = c(3:8), names_to = "Type", values_to = "Proportion")

part1 <- temp_percent_long %>%
  filter(Type != "Diff_DSM")
part2 <- temp_percent_long %>%
  filter(Type == "Diff_DSM")
```

```{r}
theme_fig <- ggplot2::theme(plot.title=element_text(size=11), 
               axis.text.x=element_text(size=13, color="black"), 
               axis.text.y = element_text(size=13, color="black",angle=45), 
               axis.title.x = element_blank(), 
               axis.title.y = element_text(size=15, color="black"),
               strip.text = element_text(size = 13),
               legend.text=element_text(size = 13),
               strip.background = element_rect(size=0.3)) 
```

Make figure for Delta Smelt
```{r}
prop_DSM <- part1 %>%
  filter(grepl("DSM", Type)) %>%
  mutate(Type = ifelse(Type == "Percent_DSM_S", "Surface",  "Bottom")) %>%
  mutate(Type = factor(Type)) 

prop_DSM2 <- part2 %>%
  filter(grepl("DSM", Type))

prop_DSM <- temp_percent_long %>%
  filter(grepl("DSM",Type)) %>%
  mutate(Type = ifelse(Type == "Percent_DSM_S", "Surface   ", ifelse(Type == "Percent_DSM_B", "Bottom    ", "Difference"))) %>%
  mutate(Type = factor(Type)) %>%
  mutate(Type = fct_relevel(Type,  "Difference", "Bottom    ", "Surface   ")) %>%
  filter(Type != "Difference")

levels(prop_DSM$Type)


# Plot
plot_habitat_deltasmelt <-ggplot2::ggplot(prop_DSM,aes(y=Type,x=Date,fill=Proportion)) +
  
  ggplot2:: geom_tile() +
  ggplot2:: geom_hline(yintercept=1.5, linetype = "dashed", color = "maroon3") +
  #scale_fill_viridis(name="Percent Suitable",option ="magma") +
  ggplot2::theme_bw()+
  ggplot2::facet_grid(.~Station) +
  scale_fill_viridis(option = "magma") +
#  scale_fill_gradientn(colours = c("#918BC3", "#C2CD23", "#808282", "#fcfdbf", "#b73779", "#918BC3", "#918BC3"), breaks = seq(from = -0.5, to = 1.0, by = 0.25), na.value="white")+
 ggplot2::guides(fill = guide_legend(title = "Proportion of time\n temperature was\n <25°C", reverse = TRUE))+
  ggplot2::labs(y = "Delta Smelt") + 
  scale_x_date(date_breaks = "2 months", date_minor_breaks = "1 month", labels = date_format("%b")) +
  theme_fig
plot_habitat_deltasmelt

# plot_habitat_deltasmelt2 <-ggplot2::ggplot(prop_DSM2,aes(y=Type,x=Date,fill=Proportion)) +
#   ggplot2:: geom_tile() +
#   #scale_fill_viridis(name="Percent Suitable",option ="magma") +
#   ggplot2::theme_bw()+
#   ggplot2::facet_grid(Station~.) +
#   scale_fill_viridis() +
# #  scale_fill_gradientn(colours = c("#918BC3", "#C2CD23", "#808282", "#fcfdbf", "#b73779", "#918BC3", "#918BC3"), breaks = seq(from = -0.5, to = 1.0, by = 0.25), na.value="white")+
#  ggplot2::guides(fill = guide_legend(title = "Proportion of time\n temperature was\n <25°C"))+
#   ggplot2::labs(y = "Delta Smelt")+
#   ggplot2::theme(plot.title=element_text(size=11), 
#                axis.text.x=element_text(size=11, color="black"), 
#                axis.text.y = element_text(size=10, color="black",angle=45), 
#                axis.title.x = element_blank(), 
#                axis.title.y = element_text(size=14, color="black"),
#                strip.text = element_text(size = 11),
#                legend.text=element_text(size = 11),
#                strip.background = element_rect(size=0.3)) 
# plot_habitat_deltasmelt2
```

Chinook plot
```{r}
prop_CHN <- temp_percent_long %>%
  filter(grepl("CHN",Type)) %>%
  mutate(Type = ifelse(Type == "Percent_CHN_S", "Surface   ", ifelse(Type == "Percent_CHN_B", "Bottom    ", "Difference"))) %>%
  mutate(Type = factor(Type, levels = c("Difference","Bottom    ","Surface   ")))

levels(prop_CHN$Type)

CHN1 <- prop_CHN %>%
  filter(Type!="Difference")


plot_habitat_chinook <-ggplot2::ggplot(CHN1,aes(y=Type,x=Date,fill=Proportion))+
  ggplot2:: geom_tile() +scale_fill_viridis(name="Percent Suitable",option ="magma") +
  ggplot2:: geom_hline(yintercept=1.5, linetype = "dashed", color = "maroon3") +
  ggplot2::theme_bw()+
  ggplot2::facet_grid(.~Station) +
  ggplot2::guides(fill = guide_legend(title = "Proportion of time\n temperature was\n <20°C", reverse = TRUE))+
  ggplot2::labs(y = "Chinook Salmon")+
  scale_x_date(date_breaks = "2 months", date_minor_breaks = "1 month", labels = date_format("%b")) +
  theme_fig
plot_habitat_chinook
```

Difference plot (don't use this)
```{r}
Difference <- temp_percent_long %>%
  filter(grepl("Diff",Type)) %>%
  mutate(Type = ifelse(Type == "Diff_DSM", "D Smelt", "Chinook"),
         Type2 = "Difference") %>%
  mutate(Type = factor(Type, levels = c("Chinook", "D Smelt")))


plot_diff <-ggplot2::ggplot(Difference,aes(y=Type,x=Date,fill=Proportion))+
  ggplot2:: geom_tile() +
 scale_fill_gradientn(colours = c("#FFF041", "#FFEC08", "#FFF1B6", "gray95",
                                  "#ACB7BD","#0F5981","#1B2090"), 
                      breaks = round(seq(from = -0.6, to = 0.8, by = 0.2),1),
                       na.value="white") +
#scale_fill_viridis(breaks = round(seq(-0.6,0.2, 0.2),1),option ="cividis") +
  ggplot2::theme_bw()+
  ggplot2::facet_grid(Station~.) +
  ggplot2::guides(fill = guide_legend(title = "Proportion of time\nbottom is more\nsuitable than\nsurface", reverse = TRUE))+
  ggplot2::labs(y = "Difference")+
  theme_fig
plot_diff


```

Option b for difference (different faceting - use this)
```{r}
DifferenceCHN <- filter(Difference, Type == "Chinook")
DifferenceDSM <- filter(Difference, Type == "D Smelt")

# plot_diffCHN <-ggplot2::ggplot(DifferenceCHN,aes(y=Type,x=Date,fill=Proportion))+
#   ggplot2:: geom_tile() +
#  scale_fill_gradientn(colours = c("#1B2090", "#0F5981", "#ACB7BD", "gray95", "#FFF1B6", "#FFEC08", "#FFF041"),
#                       breaks = round(seq(from = -0.6, to = 0.8, by = 0.2),1),
#                        na.value="white") +
# #scale_fill_viridis(breaks = round(seq(-0.6,0.2, 0.2),1),option ="cividis") +
#   ggplot2::theme_bw()+
#   ggplot2::facet_grid(.~Station) +
#   ggplot2::guides(fill = guide_legend(title = "Proportion of time\nsurface is more\nsuitable than\nbottom", reverse = TRUE))+
#   ggplot2::labs(y = "Difference")+
#   theme_fig
# plot_diffCHN


# plot_diffDSM <-ggplot2::ggplot(DifferenceDSM,aes(y=Type,x=Date,fill=Proportion))+
#   ggplot2:: geom_tile() +
# scale_fill_gradientn(colours = c("#0F5981", "#ACB7BD","gray95"),
#                       breaks = round(seq(from = -0.6, to = 0, by = 0.2),1),
#                        na.value="white") +
# #scale_fill_viridis(breaks = round(seq(-0.6,0.2, 0.2),1),option ="cividis") +
#   ggplot2::theme_bw()+
#   ggplot2::facet_grid(.~Station) +
#   ggplot2::guides(fill = guide_legend(title = "Proportion of time\nsurface is more\nsuitable than\nbottom", reverse = TRUE))+
#   ggplot2::labs(y = "Difference")+
#   theme_fig
# plot_diffDSM

# Chinook
plot_diffCHN2 <-ggplot2::ggplot(DifferenceCHN,aes(y=Type2,x=Date,fill=Proportion))+
  ggplot2:: geom_tile() +
 scale_fill_gradientn(colours = c("#FFF041", "#FFEC08", "#FFF1B6","gray95",
                                  "#ACB7BD","#0F5981","#1B2090" ),
                      breaks = round(seq(from = -0.6, to = 0.8, by = 0.2),1),
                       na.value="white") +
#scale_fill_viridis(breaks = round(seq(-0.6,0.2, 0.2),1),option ="cividis") +
  ggplot2::theme_bw()+
  ggplot2::facet_grid(.~Station) +
  scale_x_date(date_breaks = "2 months", date_minor_breaks = "1 month", labels = date_format("%b")) +
  ggplot2::guides(fill = guide_legend(title = "Proportion of time\nbottom is more\nsuitable than\nsurface", reverse = TRUE))+
  ggplot2::labs(y = "Chinook Salmon")+
  theme_fig
plot_diffCHN2



# Delta Smelt
plot_diffDSM2 <-ggplot2::ggplot(DifferenceDSM,aes(y=Type2,x=Date,fill=Proportion))+
  ggplot2:: geom_tile() +
scale_fill_gradientn(colours = c("gray95", "#ACB7BD","#0F5981"), 
                      breaks = round(seq(from = -0.1, to = 0.5, by = 0.2),1),
                       na.value="white") +
  scale_x_date(date_breaks = "2 months", date_minor_breaks = "1 month", labels = date_format("%b")) +
  ggplot2::theme_bw()+
  ggplot2::facet_grid(.~Station) +
  ggplot2::guides(fill = guide_legend(title = "Proportion of time\nbottom is more\nsuitable than\nsurface", reverse = TRUE))+
  ggplot2::labs(y = "Delta Smelt")+
  theme_fig
plot_diffDSM2

```

This one
```{r}
#Print out smelt and salmon figure together
tiff(filename=file.path("Figures/Depth/Figure_Continuous_Data_Suitability3.tiff"), units="in",type="cairo", bg="white", height=9.5, 
     width=10, res=300, pointsize=10,compression="lzw")
ggarrange(plot_habitat_chinook, plot_diffCHN2, plot_habitat_deltasmelt, plot_diffDSM2, ncol=1, nrow=4,labels = c(" a)"," b)", " c)", " d)"),hjust=-0.1)
dev.off()
```

Interspersed figure
```{r}
#Print out smelt and salmon figure together
tiff(filename=file.path("Figures/Depth/Figure_Continuous_Data_Suitability2V.tiff"), units="in",type="cairo", bg="white", height=9, 
     width=10, res=300, pointsize=10,compression="lzw")
ggarrange(plot_habitat_chinook,  plot_diffCHN,plot_habitat_deltasmelt, plot_diffDSM, ncol=1, nrow=4,labels = c("A","B", "C", "D"), heights = c(2, 1.8, 2, 1.8),hjust=-0.1)
dev.off()
```

Difference at the bottom figure
```{r}
#Print out smelt and salmon figure together
tiff(filename=file.path("Figures/Depth/Figure_Continuous_Data_Suitability3V.tiff"), units="in",type="cairo", bg="white", height=10, 
     width=9, res=300, pointsize=10,compression="lzw")
ggarrange(plot_habitat_chinook,  plot_habitat_deltasmelt,plot_diffCHN, plot_diffDSM, ncol=1, nrow=4,labels = c("a)","b)", "c)", "d)"), heights = c(2, 2, 1.8, 1.8), hjust=-0.1)
dev.off()
```

