---
title: "TempHeatStress"
author: "Catarina Pien"
date: "2/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly) # interactive plots
library(pscl) # glm
library(visreg) # visualize model results
library(lattice)
library(lme4) # glmm
library(lmerTest) #glmm p values
```

Read in 
```{r}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")

#tempFilt <- readRDS("Data/tempFilt.rds") 
tempToUse <- readRDS("Data/temp10years_20200922.rds")
#tempAn <- readRDS("Data/tempAnnual.rds")
tempMon <- readRDS("Data/tempMonthly.rds")
tempDaily <- readRDS("Data/tempDaily.rds")
#tempHeat <- readRDS("Data/heatstressDaily.rds")
```

Code to make sure every month has data
```{r nMon}
# Filter to only data that has temps from every month so as not to skew the data that only has part of the year represented.
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

nMon$WY <- as.numeric(nMon$WY)
```

## Daily Range
```{r Models Daily Max}
tempDaily <- filter(tempDaily, WY > 2008 & WY < 2020)
tempDaily$yday = yday(tempDaily$Date)
tempDaily$Year = year(tempDaily$Date)
tempDaily$fYear = factor(tempDaily$Year)
tempDaily$fWY = factor(tempDaily$WY)
tempDaily$Month = month(tempDaily$Date)
tempDaily$fMonth = ordered(tempDaily$Month)
tempDailyM <- left_join(tempDaily, nMon) %>%
  filter(nMon == 12)

tempDaily$WYType2_Sac = as.factor(tempDaily$WYType2_Sac)
tempToUse$Hour <- hour(tempToUse$Datetime)

#try a sine-transformation on "month" so we can include it in linear models
tempDailyM$syday = sin(pi*tempDailyM$yday/365)

# Add season
tempToUse <- tempToUse %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempToUse$Season <- factor(tempToUse$Season, levels = c("Spring", "Summer", "Fall", "Winter"))


# Add season
tempDailyM <- tempDailyM %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempDailyM$Season <- factor(tempDailyM$Season, levels = c("Spring", "Summer", "Fall", "Winter"))
```

**Scientific Questions**  

1. What is the approximate daily range? 
2. How does range change on annual scale? 
3. Does the range differ by region (taking into account month)?
4. Does the range differ at particular stations in a region? 

### Trends

What does temperature look like overall by hour?
```{r }
# Overall temperature trends by Month and Region 
temp_s <- tempToUse %>% group_by(Region) %>% sample_frac(.1)
ggplot(temp_s, aes(x = factor(Hour), y = Temp)) + geom_boxplot() + facet_grid(Region~Season)+theme_bw()
```

Table of Ranges by Region, Season, Month
```{r}
summaryRange <- tempDailyM %>%
  group_by(Region, Season, fMonth) %>%
  summarize(mean.Range = mean(rangeTemp),
            median.Range = median(rangeTemp),
            n = n(),
            sd = sd(rangeTemp),
            se = sd(rangeTemp)/sqrt(n))
```
