---
title: "TempHeatStress"
author: "Catarina Pien"
date: "2/16/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly) # interactive plots
library(pscl) # glm
library(visreg) # visualize model results
library(lattice)
library(lme4) # glmm
library(lmerTest) #glmm p values
library(here)
```

```{r}
theme_wtemp <- theme_classic() + 
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 15),
        strip.text = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 15))
```

## Read in 
```{r}
#tempFilt <- readRDS("Data/tempFilt.rds") 
# tempToUse <- readRDS("Data/tempToUse_20210811.rds")
tempToUse <- readRDS(here::here("Data/temp10years_20210811.rds"))
#tempAn <- readRDS("Data/tempAnnual.rds")
#tempMon <- readRDS("Data/tempMonthly.rds")
tempDaily <- readRDS(here::here("Data/tempDaily_20210811.rds"))
```

## 1. Calculating High Stress 
### 21-25C Thresholds

Identifying Heat Stress Level (High/Med/Low) 
Identifying "StressAllDay" = when min daily temperature >25 (could change this)
```{r heatevents}
# Flagging starts on day 3 of >25C
heat <- tempDaily %>%
  dplyr::select(-meanDaily) %>%
  group_by(Region, Station, WY) %>%
  mutate(Thr25 = ifelse(maxDaily > 25, 1L, 0L),
         Thr21 = ifelse(maxDaily > 21, 1L, 0L)) %>% 
  mutate(Stress = 
           ifelse(Thr25 == lag(Thr25, 1) & Thr25 == lag(Thr25, 2) & Thr25 == 1, "High", 
                            ifelse(Thr21 == lag(Thr21, 1) & Thr21 == lag(Thr21, 2) & Thr21 == 1, "Med", 
                                   "Low"))) %>%
  ungroup() %>%
  group_by(Region, Station, WY, Date) %>%
  mutate(StressAllDay = ifelse(Stress == "High" & minDaily>25, "Y", "N")) %>%
  dplyr::select(-starts_with("Thr")) %>%
  filter(!is.na(Stress)) # Remove NAs coming from lag term
# saveRDS(heat, "Data/heatstressDaily.rds")
```


 Temp variables
```{r Models Daily Max}
tempHeat <- filter(heat, WY > 2008 & WY < 2020)
tempHeat$yday = yday(tempHeat$Date)
tempHeat$Year = year(tempHeat$Date)
tempHeat$fYear = factor(tempHeat$Year)
tempHeat$fWY = factor(tempHeat$WY)
tempHeat$Month = month(tempHeat$Date)
tempHeat$fMonth = ordered(tempHeat$Month)
tempHeat$Station = factor(tempHeat$Station)
tempHeat$WYType2_Sac = as.factor(tempHeat$WYType2_Sac)
tempToUse$Hour <- hour(tempToUse$Datetime)

#try a sine-transformation on "month" so we can include it in linear models
tempHeat$syday = sin(pi*tempHeat$yday/365)

# Add season
tempHeat <- tempHeat %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempHeat$Season <- factor(tempHeat$Season, levels = c("Spring", "Summer", "Fall", "Winter"))
```


Number of days at each stress level
```{r}
# Calculate number of samples in a year or water year
heatDaysSamp <- tempHeat %>%
  group_by(Region, Station, WY, fWY) %>%
  summarize(totalDays = n()) 

# Calculate number of days and proportion of days at each stress level
heatDays1 <- tempHeat %>%
  group_by(Region, Station, WY, fWY, Stress) %>%
  summarize(nDays = n()) %>%
    ungroup() %>%
 complete(Stress, nesting(Region, Station, WY, fWY), fill = list(nDays=0)) %>%
  left_join(heatDaysSamp) %>%
  mutate(propDays = round(nDays/totalDays,3)) %>%
  ungroup()

# Look at days where there is no recovery
heatDays2 <- tempHeat %>%
  dplyr::select(-Stress) %>%
  group_by(Region, Station, WY,fWY, StressAllDay) %>%
  summarize(nDays = n()) %>%  
  ungroup() %>%
   complete(StressAllDay, nesting(Region, Station, WY, fWY), fill = list(nDays=0)) %>%
  left_join(heatDaysSamp) %>%
  mutate(propDays = round(nDays/totalDays,3))%>%
  ungroup() %>%
  arrange(Region, Station, WY, fWY) 


# write_csv(heatDays1, "Data/heatDaysHighMedLow25_20210811.csv")
# write_csv(heatDays2, "Data/noRecovery25_20210811.csv")
```

```{r}
tempHeat%>%
  ggplot() + 
  geom_boxplot(aes(x = fMonth, y = maxDaily, fill = Stress))+ facet_wrap(~Region) + scale_fill_viridis(discrete = TRUE)
```




#### Days at high stress

Plot by region and station
```{r}

highHeat <- filter(heatDays1, Stress == "High")

# Assign axis colors by region
StationCol = highHeat %>%
  mutate(colors = ifelse(Region == "San Joaquin", "maroon4",
                                    ifelse(Region == "South", "orangered",
                                           ifelse(Region == "Suisun Bay", "blue",
                                                  ifelse(Region == "Suisun Marsh", "turquoise",
                                                         ifelse(Region == "Far North", "yellow", ifelse(Region == "North Delta", "chartreuse4",
                                                                                                        ifelse(Region == "Sac River", "ivory4", "darkslategrey")))))))) %>%
  arrange(as.numeric(Region)) %>%
  select(c(3,9)) %>%
  unique()

axisColor <- as.vector(StationCol$colors)

# By Station
ggplot(highHeat, aes(fWY, fct_reorder(Station, as.numeric(Region)), fill = nDays)) + geom_tile() +
scale_fill_viridis(option = "plasma") + theme_wtemp+ theme(axis.text.y = element_text(color = axisColor),
                                                           axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) ) 

ggplot(highHeat, aes(fWY, fct_reorder(Station, as.numeric(Region)), fill = propDays)) + geom_tile() +
scale_fill_viridis(option = "viridis") + 
  theme_wtemp+ theme(axis.text.y = element_text(color = axisColor,  size = 11),
                     axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) )



# By Region
ggplot(highHeat, aes(fWY, Region, fill = nDays)) + geom_tile() + scale_fill_viridis(option = "plasma")+ theme_wtemp +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) )

ggplot(highHeat, aes(fWY, Region, fill = propDays)) + geom_tile() + scale_fill_viridis() + theme_wtemp +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) )

```

#### No recovery
```{r}
NoRecovery <- filter(heatDays2, StressAllDay == "Y")

# By Station
ggplot(NoRecovery, aes(fWY, Station, fill = nDays)) + geom_tile() + scale_fill_viridis(option= "plasma") + theme_wtemp + theme(axis.text.y = element_text(color = axisColor),
                                                                                                axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


ggplot(NoRecovery, aes(fWY, Station, fill = propDays)) + geom_tile() + scale_fill_viridis(option= "viridis") + theme_wtemp + 
  theme(axis.text.y = element_text(color = axisColor),                                        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


# By Region
ggplot(NoRecovery, aes(fWY, Region, fill = nDays)) + geom_tile() + scale_fill_viridis(option = "plasma") + theme_wtemp + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 

ggplot(NoRecovery, aes(fWY, Region, fill = propDays)) + geom_tile() + scale_fill_viridis() + theme_wtemp + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```


### 21 Threshold
```{r}
# Flagging starts on day 3 of >21C
tempHeat2 <- tempDaily %>%
  dplyr::select(-meanDaily) %>%
  group_by(Region, Station, WY) %>%
  mutate(Thr21 = ifelse(maxDaily > 21, 1L, 0L)) %>%
  mutate(Stress = ifelse(Thr21 == lag(Thr21, 1) & Thr21 == lag(Thr21, 2) & Thr21 == 1, "High", "Low")) %>%
  ungroup() %>%
  group_by(Region, Station, WY, Date) %>%
  mutate(StressAllDay = ifelse(Stress == "High" & minDaily>21, "Y", "N")) %>%
  dplyr::select(-starts_with("Thr")) %>%
  filter(!is.na(Stress)) # Remove NAs coming from lag term

```


Temp variables
```{r Models Daily Max}
tempHeat2$yday = yday(tempHeat2$Date)
tempHeat2$Year = year(tempHeat2$Date)
tempHeat2$fYear = factor(tempHeat2$Year)
tempHeat2$fWY = factor(tempHeat2$WY)
tempHeat2$Month = month(tempHeat2$Date)
tempHeat2$fMonth = factor(tempHeat2$Month)
tempHeat2$Station = factor(tempHeat2$Station)
tempHeat2$WYType2_Sac = as.factor(tempHeat2$WYType2_Sac)

#try a sine-transformation on "month" so we can include it in linear models
tempHeat2$syday = sin(pi*tempHeat2$yday/365)

# Add season
tempHeat2 <- tempHeat2 %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempHeat2$Season <- factor(tempHeat2$Season, levels = c("Spring", "Summer", "Fall", "Winter"))
```


Number of days at each stress level
```{r}
# Calculate number of samples in a year or water year
heatDaysSamp2 <- tempHeat2 %>%
  group_by(Region, Station, WY, fWY) %>%
  summarize(totalDays = n()) %>%
  filter(totalDays > 275)

# Calculate number of days and proportion of days at each stress level
stressDays1 <- tempHeat2 %>%
  group_by(Region, Station, WY, fWY, Stress) %>%
  summarize(nDays = n()) %>%
    ungroup() %>%
 complete(Stress, nesting(Region, Station, WY, fWY), fill = list(nDays=0)) %>%
  left_join(heatDaysSamp2) %>%
  mutate(propDays = round(nDays/totalDays,3)) %>%
  ungroup() %>%
  drop_na()

# Look at days where there is no recovery
stressDays2 <- tempHeat2 %>%
  group_by(Region, Station,WY,  fWY, StressAllDay) %>%
  summarize(nDays = n()) %>%  
  ungroup() %>%
 complete(StressAllDay, nesting(Region, Station, WY, fWY), fill = list(nDays=0)) %>%
  arrange(Region, Station, WY, fWY) %>%
  left_join(heatDaysSamp2) %>%
  mutate(propDays = round(nDays/totalDays,3)) %>%
  ungroup()


# write_csv(stressDays1, "Data/heatDaysHighLow21_20210904.csv")
# write_csv(stressDays2, "Data/noRecovery21_20211118.csv")
```

#### High Stress
```{r}
highStress <- filter(stressDays1, Stress == "High")

# Assign axis colors by region
StationCols = highStress %>%
  mutate(colors = ifelse(Region == "San Joaquin", "maroon4",
                                    ifelse(Region == "South", "orangered",
                                           ifelse(Region == "Suisun Bay", "blue",
                                                  ifelse(Region == "Suisun Marsh", "turquoise", ifelse(Region == "North Delta", "chartreuse4",
                                                                                                        ifelse(Region == "Sac River", "ivory4", "darkslategrey"))))))) %>%
  arrange(as.numeric(Region)) %>%
  select(c(3,9)) %>%
  unique()

axisColors <- as.vector(StationCols$colors)

# By Station
ggplot(highStress, aes(fWY, fct_reorder(Station, as.numeric(Region)), fill = nDays)) + geom_tile() +
scale_fill_viridis(option = "plasma") + theme_wtemp+ theme(axis.text.y = element_text(color = axisColor),
                                                           axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) ) 

ggplot(highStress, aes(fWY, fct_reorder(Station, as.numeric(Region)), fill = propDays)) + geom_tile() +
scale_fill_viridis(option = "viridis") + theme_wtemp+ 
  theme(axis.text.y = element_text(color = axisColor, size = 12),
                                                            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) )



# By Region
ggplot(highStress, aes(fWY, Region, fill = nDays)) + geom_tile() + scale_fill_viridis(option = "plasma")+ theme_wtemp +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) )

ggplot(highStress, aes(fWY, Region, fill = propDays)) + geom_tile() + scale_fill_viridis() + theme_wtemp +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1) )
```

#### No Recovery
```{r}
NoRecovery2 <- filter(stressDays2, StressAllDay == "Y")

# By Station
ggplot(NoRecovery2, aes(fWY, Station, fill = nDays)) + geom_tile() + scale_fill_viridis(option= "plasma") + theme_wtemp + theme(axis.text.y = element_text(color = axisColors),
                                                                                                axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


ggplot(NoRecovery2, aes(fWY, Station, fill = propDays)) + geom_tile() + scale_fill_viridis(option= "viridis") + theme_wtemp + theme(axis.text.y = element_text(color = axisColor),
                                                                                                                                   axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


# By Region
ggplot(NoRecovery2, aes(fWY, Region, fill = nDays)) + geom_tile() + scale_fill_viridis(option = "plasma") + theme_wtemp + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 

ggplot(NoRecovery2, aes(fWY, Region, fill = propDays)) + geom_tile() + scale_fill_viridis() + theme_wtemp + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


#### Days at low stress

Plot by region and station
```{r}
lowHeat <- filter(stressDays1, Stress == "Low")

# Assign axis colors by region
StationCol2 = lowHeat %>%
  mutate(colors = ifelse(Region == "San Joaquin", "maroon4",
                                    ifelse(Region == "South", "orangered",
                                           ifelse(Region == "Suisun Bay", "blue",
                                                  ifelse(Region == "Suisun Marsh", "turquoise", ifelse(Region == "North Delta", "chartreuse4",
                                                                                                        ifelse(Region == "Sac River", "ivory4", "darkslategrey"))))))) %>%
  arrange(as.numeric(Region)) %>%
  select(c(3,9)) %>%
  unique()

axisColor2 <- as.vector(StationCol2$colors)

# By Station
ggplot(lowHeat, aes(fWY, fct_reorder(Station, as.numeric(Region)), fill = nDays)) + geom_tile() +
scale_fill_viridis(option = "plasma") + theme_wtemp+ theme(axis.text.y = element_text(color = axisColor2)) 

ggplot(lowHeat, aes(fWY, fct_reorder(Station, as.numeric(Region)), fill = propDays)) + geom_tile() +
scale_fill_viridis(option = "viridis") + theme_wtemp+ theme(axis.text.y = element_text(color = axisColor2))


# By Region
ggplot(lowHeat, aes(fWY, Region, fill = nDays)) + geom_tile() + scale_fill_viridis(option = "plasma")+ theme_wtemp + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot(lowHeat, aes(fWY, Region, fill = propDays)) + geom_tile() + scale_fill_viridis() + theme_wtemp + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```


#### Checking out the South
```{r}
Check <- tempHeat2 %>% filter(Region %in% c("South", "North Delta"),
                         WY %in% c("2016", "2017"))

ggplot(subset(Check, Check$Region == 
                "South"), aes(Date, maxDaily)) + geom_point() + facet_wrap(~Station) +
  geom_line(y = 21, color = "red")

```











## 2. Has amount of high heat stress days changed over time?

### Look at distribution of data
```{r}
ggplot(highHeat, aes(nDays)) + geom_histogram(binwidth = 2) + theme_wtemp
ggplot(highHeat, aes(propDays)) + geom_dotplot(dotsize = 0.1) + facet_wrap(~Region) + theme_wtemp

par(mfrow = c(2,3))
dotchart(highHeat$propDays[highHeat$Region == "North Delta"], xlab ="Proportion days", main = "North Delta")
dotchart(highHeat$propDays[highHeat$Region == "Sac River"], xlab = "Proportion days", main = "Sac River")
dotchart(highHeat$propDays[highHeat$Region == "San Joaquin"], xlab ="Proportion days", main = "San Joaquin")
dotchart(highHeat$propDays[highHeat$Region == "South"], xlab = "Proportion days", main = "South")
dotchart(highHeat$propDays[highHeat$Region == "Suisun Bay"], xlab = "Proportion
days", main = "Suisun Bay")
dotchart(highHeat$propDays[highHeat$Region == "Suisun Marsh"], xlab = "Proportion days", main = "Suisun Marsh")

ggplot(highHeat, aes(fWY, propDays))+ geom_boxplot() + theme_wtemp
ggplot(highHeat, aes(Region, propDays))+ geom_boxplot() + theme_wtemp
ggplot(highHeat, aes(fWY, propDays, fill = Region))+ geom_boxplot() + scale_fill_viridis(discrete = TRUE) + theme_wtemp
highHeat$WY

ggplot(highHeat, aes(WY, propDays, color = Region))+ geom_point() + geom_smooth(method = "loess") + scale_color_viridis(discrete = TRUE) + theme_wtemp

```


Looks to be zero-inflated and pretty variable by Region and Year. 

### Model
Binomial data prep
```{r}
tempHeatBi <- tempHeat %>%
  mutate(StressHigh = ifelse(Stress == "High", 1, 0),
         StressAllDay2 = ifelse(StressAllDay == "Y", 1, 0))
```

Models - binomial 
Mixed model to include Station and Month
```{r}
library(car)
Mheat1 <- glm(cbind(nDays, totalDays) ~ fWY + Region, family = binomial(link="logit"), data = highStress)
summary(Mheat1)


Mheat2 <- glm(cbind(nDays, totalDays) ~ fWY * Region, family = binomial(link = "logit"), data = highStress)
summary(Mheat2)

AIC(Mheat1, Mheat2)
par(mfrow = c(2,2))
plot(Mheat2)
```

Mixed Models
```{r}
library(lme4)

Mheat3 <- glmer(cbind(nDays, totalDays) ~ fWY + Region + (1|Station), family = binomial, data = highStress)
summary(Mheat3)
```


Trying to use a normal lmer with an offset

```{r}
hist(highStress$nDays)


# Make offset
highStress$logTotalDays <- log(highStress$totalDays)

# Model
Mheat4 <- lmer(nDays~ fWY*Region + offset(logTotalDays) + (1|Station), data = highStress)
summary(Mheat4)

# Plot residuals
par(mfrow = c(1,2))
qqnorm(resid(Mheat4))
qqline(resid(Mheat4))
plot(Mheat4)

EP1 <- resid(Mheat4, type = "pearson")
qqrplot(EP1)


visreg(Mheat4, "fWY", by = "Region")
```

