---
title: "TempTrends"
author: "Catarina Pien"
date: "8/3/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
This code explores temporal trends existing in the integrated temperature dataset.



```{r import}
library(tidyverse)
library(lubridate)
library(readr)

setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")
tempFilt <- readRDS("Data/Temp_filtered.rds")

str(tempFilt)
```

Variable editing
```{r vars}
tempFilt$Year = year(tempFilt$Date)
tempFilt$Month = month(tempFilt$Date)
tempFilt$yDay = yday(tempFilt$Date)

```

Merge station info
Merge regions
```{r regions}
library(sf)
library(sp)
subregions <- st_read("Data/EDSM_Subregions/EDSM_Subregions_03302020.shp")
staInfo <- read.csv()
left_join(tempFilt, staInfo, by = "Station")

```

## Mean, max, min temperatures 
Create dataset for mean, max, and min, var for Monthly
Filter for data that is represented for a whole year
Create dataset for mean, max, min, var for Annual
```{r meanmaxmin}
tempMon <- tempFilt %>% 
  group_by(Station, Year, Month) %>%
  summarize(maxTemp = max(Temp),
            minTemp = min(Temp),
            meanTemp = round(mean(Temp),1),
            sdTemp = round(sd(Temp),1))

# Filter to only data that has temps from every month 

nMon <- tempMon %>% group_by(Station, Year) %>%
  summarize (nMon = n())

tempAn <- left_join(tempFilt, nMon, by = c("Station", "Year")) %>%
  filter(nMon == 12) %>%
  group_by(Station, Year) %>%
  summarize(maxTempAn = max(Temp),
            minTempAn = min(Temp),
            meanTempAn = mean(Temp),
            varTempAn = sd(Temp))

```

Functions
```{r}
heatmapplot <-  function(data,fill, temp, l1, l2) {
    fill <- enquo(fill)
    temp <- enquo(temp)
  p <- data %>%
    ggplot(mapping = aes(Year, Station, fill = !! fill,
                         text = paste("Station:", Station, "\nTemp:", !! temp)
                         )) +
    geom_tile() +
      scale_fill_viridis(option = "cividis", limits = c(l1,l2)) + theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12))
  ggplotly(p, tooltip = "text") 
  
}  

```


Link Regions, Filter into smaller datasets
```{r filter}
# Split into regions? 
# Test
stations <- unique(tempFilt$Station)
staSamp1 <- stations[1:40]
staSamp2 <- stations[41:80]
staSamp3 <- stations[81:129]

```

## Heat map for maximum temps
```{r heatmapMax}
library(RColorBrewer)
library(viridis)
library(plotly)
  
maxTemps <- tempAn %>%
  filter(!is.na(maxTempAn)) %>%
  ungroup() %>%
  dplyr::select(c(Year, Station, maxTempAn)) %>%
  group_by(Station) %>%
  mutate(maxTempAn_yr = scale(maxTempAn)) %>%
  ungroup %>%
  group_by(Year) %>%
  mutate(maxTempAn_sta = scale(maxTempAn)) %>%
  ungroup()

str(maxTemps)

# Smaller datasets
maxAn1 <- filter(maxTemps, Station %in% staSamp1) 
maxAn2 <- filter(maxTemps, Station %in% staSamp2) 
maxAn3 <- filter(maxTemps, Station %in% staSamp3) 

##### Heat maps (absolute values)
maxAn1$Year <- ordered(maxAn1$Year)
maxAn2$Year <- ordered(maxAn2$Year)
maxAn3$Year <- ordered(maxAn3$Year)

heatmapplot(maxAn1, maxTempAn, maxTempAn, 20, 35)
heatmapplot(maxAn2, maxTempAn, maxTempAn, 20, 35)
heatmapplot(maxAn3, maxTempAn, maxTempAn, 20, 35)

##### Scaled heatmaps

# By station
heatmapplot(maxAn1, maxTempAn_sta, maxTempAn,  -4.1, 4.1)
heatmapplot(maxAn2, maxTempAn_sta, maxTempAn,  -4.1, 4.1)
heatmapplot(maxAn3, maxTempAn_sta, maxTempAn,  -4.1, 4.1)
heatmapplot(maxTemps, maxTempAn_sta, maxTempAn,  -4.1, 4.1)

## By year
heatmapplot(maxAn1, maxTempAn_yr, maxTempAn,  -4.1, 4.1)
heatmapplot(maxAn2, maxTempAn_yr, maxTempAn,  -4.1, 4.1)
heatmapplot(maxAn3, maxTempAn_yr, maxTempAn,  -4.1, 4.1)
heatmapplot(maxTemps, maxTempAn_yr, maxTempAn,  -4.1, 4.1)

#####################################################################

# Spread data so you have a value for each space/time combo
maxAn_w <- maxTemps %>% spread(key=Year, value=maxTempAn)

# Assign stations as row names
maxAn_w2 <- as.data.frame(maxAn_w)
row.names(maxAn_w2) <- maxAn_w$Station

# Matrix of max temp data
maxAn_w2 <- maxAn_w2[,2:32]
maxAn.m <- data.matrix(maxAn_w2)

# Subset so there aren't too many stations per map
maxAn.m1 <- maxAn.m[1:40,]
maxAn.m2 <- maxAn.m[41:80,]
maxAn.m3 <- maxAn.m[81:127,]

# Make heatmap
# Note you can either scale the heat map by column or row. 

# Row: how do years compare?
heatmap(maxAn.m1, Rowv = NA, Colv = NA, col = brewer.pal(9, "YlGnBu"), scale = "row")
heatmap(maxAn.m2, Rowv = NA, Colv = NA, col = brewer.pal(9, "YlGnBu"), scale = "row")
heatmap(maxAn.m3, Rowv = NA, Colv = NA, col = brewer.pal(9, "YlGnBu"), scale = "row")


# Column: how do stations compare to each other?
heatmap(maxAn.m1, Rowv = NA, Colv = NA, col = brewer.pal(9, "YlGnBu"), scale = "column")
heatmap(maxAn.m2, Rowv = NA, Colv = NA, col = brewer.pal(9, "YlGnBu"), scale = "column")
heatmap(maxAn.m3, Rowv = NA, Colv = NA, col = brewer.pal(9, "YlGnBu"), scale = "column")

heatmaply(maxAn1)
```

## Heat map for mean temps
```{r heatmapMean}
library(heatmaply)
library(RColorBrewer)
library(viridis)
library(plotly)

meanTemps <- tempAn %>%
  filter(!is.na(meanTempAn)) %>%
  ungroup() %>%
  dplyr::select(c(Year, Station, meanTempAn)) %>%
  group_by(Station) %>%
  mutate(meanTempAn_yr = scale(meanTempAn)) %>%
  ungroup %>%
  group_by(Year) %>%
  mutate(meanTempAn_sta = scale(meanTempAn)) %>%
  ungroup()

str(meanTemps)

# Smaller datasets
meanAn1 <- filter(meanTemps, Station %in% staSamp1) 
meanAn2 <- filter(meanTemps, Station %in% staSamp2) 
meanAn3 <- filter(meanTemps, Station %in% staSamp3) 

##### Heat maps (absolute values)
meanAn1$Year <- ordered(meanAn1$Year)
meanAn2$Year <- ordered(meanAn2$Year)
meanAn3$Year <- ordered(meanAn3$Year)

heatmapplot(meanAn1, meanTempAn, meanTempAn, 12, 20)
heatmapplot(meanAn2, meanTempAn, meanTempAn, 12, 20)
heatmapplot(meanAn3, meanTempAn, meanTempAn, 12, 20)

##### Scaled heatmaps

# By station
heatmapplot(meanAn1, meanTempAn_sta, meanTempAn, -4.5, 4.5)
heatmapplot(meanAn2, meanTempAn_sta, meanTempAn, -4.5, 4.5)
heatmapplot(meanAn3, meanTempAn_sta, meanTempAn, -4.5, 4.5)
heatmapplot(meanTemps, meanTempAn_sta, meanTempAn, -4.5, 4.5)

## By year
heatmapplot(meanAn1, meanTempAn_yr, meanTempAn, -4.5, 4.5)
heatmapplot(meanAn2, meanTempAn_yr, meanTempAn, -4.5, 4.5)
heatmapplot(meanAn3, meanTempAn_yr, meanTempAn, -4.5, 4.5)
heatmapplot(meanTemps, meanTempAn_yr, meanTempAn, -4.5, 4.5)

```

## Heat map for min temps
```{r heatmap}
library(heatmaply)
library(RColorBrewer)
library(viridis)
library(plotly)

minTemps <- tempAn %>%
  filter(!is.na(minTempAn)) %>%
  ungroup() %>%
  dplyr::select(c(Year, Station, minTempAn)) %>%
  group_by(Station) %>%
  mutate(minTempAn_yr = scale(minTempAn)) %>%
  ungroup %>%
  group_by(Year) %>%
  mutate(minTempAn_sta = scale(minTempAn)) %>%
  ungroup()

str(minTemps)

# Smaller datasets
minAn1 <- filter(minTemps, Station %in% staSamp1) 
minAn2 <- filter(minTemps, Station %in% staSamp2) 
minAn3 <- filter(minTemps, Station %in% staSamp3) 

##### Heat maps (absolute values)
minAn1$Year <- ordered(minAn1$Year)
minAn2$Year <- ordered(minAn2$Year)
minAn3$Year <- ordered(minAn3$Year)

heatmapplot(minAn1, minTempAn, minTempAn, 1.5, 10)
heatmapplot(minAn2, minTempAn, minTempAn, 1.5, 10)
heatmapplot(minAn3, minTempAn, minTempAn, 1.5, 10)

##### Scaled heatmaps

# By station
heatmapplot(minAn1, minTempAn_sta, minTempAn, -5.7, 5.7)
heatmapplot(minAn2, minTempAn_sta, minTempAn, -5.7, 5.7)
heatmapplot(minAn3, minTempAn_sta, minTempAn, -5.7, 5.7)
heatmapplot(minTemps, minTempAn_sta, minTempAn, -5.7, 5.7)

## By year
heatmapplot(minAn1, minTempAn_yr, minTempAn, -3.5, 3.5)
heatmapplot(minAn2, minTempAn_yr, minTempAn, -3.5, 3.5)
heatmapplot(minAn3, minTempAn_yr, minTempAn, -3.5, 3.5)
heatmapplot(minTemps, minTempAn_yr, minTempAn, -3.5, 3.5)

```

Heat maps for sd
```{r heatmap}
library(heatmaply)
library(RColorBrewer)
library(viridis)
library(plotly)

varTemps <- tempAn %>%
  filter(!is.na(varTempAn)) %>%
  ungroup() %>%
  dplyr::select(c(Year, Station, varTempAn)) %>%
  group_by(Station) %>%
  mutate(varTempAn_yr = scale(varTempAn)) %>%
  ungroup %>%
  group_by(Year) %>%
  mutate(varTempAn_sta = scale(varTempAn)) %>%
  ungroup()

str(varTemps)

# Smaller datasets
varAn1 <- filter(varTemps, Station %in% staSamp1) 
varAn2 <- filter(varTemps, Station %in% staSamp2) 
varAn3 <- filter(varTemps, Station %in% staSamp3) 

##### Heat maps (absolute values)
varAn1$Year <- ordered(varAn1$Year)
varAn2$Year <- ordered(varAn2$Year)
varAn3$Year <- ordered(varAn3$Year)

heatmapplot(varAn1, varTempAn, varTempAn, 2, 7)
heatmapplot(varAn2, varTempAn, varTempAn, 2, 7)
heatmapplot(varAn3, varTempAn, varTempAn, 2, 7)

##### Scaled heatmaps

# By station
heatmapplot(varAn1, varTempAn_sta, varTempAn, -4.5, 4.5)
heatmapplot(varAn2, varTempAn_sta, varTempAn, -4.5, 4.5)
heatmapplot(varAn3, varTempAn_sta, varTempAn, -4.5, 4.5)
heatmapplot(varTemps, varTempAn_sta, varTempAn, -4.5, 4.5)

## By year
heatmapplot(varAn1, varTempAn_yr, varTempAn, -3, 3)
heatmapplot(varAn2, varTempAn_yr, varTempAn, -3, 3)
heatmapplot(varAn3, varTempAn_yr, varTempAn, -3, 3)
heatmapplot(varTemps, varTempAn_yr, varTempAn, -3, 3)

```
