---
title: "Daily Models"
author: "Catarina Pien"
date: "2/2/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Daily Temperature Trend Models {.tabset}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly) # interactive plots
library(pscl) # glm
library(visreg) # visualize model results
library(lattice)
library(lme4) # glmm
library(lmerTest) #glmm p values
library(plotly)
library(ggeffects)
```

Read in data
```{r read}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")

# tempFilt <- readRDS("Data/tempFilt.rds") 
# tempToUse <- readRDS("Data/temp10years_20200922.rds")
# tempAn <- readRDS("Data/tempAnnual.rds")
tempMon <- readRDS("Data/tempMonthly.rds")
tempDaily0 <- readRDS("Data/tempDaily.rds")
# tempHeat <- readRDS("Data/heatstressDaily.rds")
```

Add Season; Filter and alter variables
```{r filterVars}
tempDaily0$Month <- month(tempDaily0$Date)
tempDaily0$Year <- year(tempDaily0$Date)
tempDaily0 <- tempDaily0 %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempDaily0$Season <- factor(tempDaily0$Season, levels = c("Spring", "Summer", "Fall", "Winter"))
tempDaily0$WY <- as.numeric(tempDaily0$WY)
tempDaily0$fWY <- factor(tempDaily0$WY)
tempDaily0$fMonth <- factor(tempDaily0$Month, levels = c("11", "12", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))
tempDaily0$fYear <- factor(tempDaily0$Year)
tempDaily0$yday <- yday(tempDaily0$Date)


# Filter only Station-WY combos with 12 months data
# Filter 2009-2019
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

tempDaily <- left_join(tempDaily0, nMon) %>%
  filter(nMon == 12)

tempDaily <- filter(tempDaily, WY > 2008 & WY < 2020)

#try a sine-transformation on "yday" and "month" so we can include it in linear models
tempDaily$sMonth = sin(pi*tempDaily$Month/12)
tempDaily$syday = sin(pi*tempDaily$yday/365)

```

How much data do we have?
```{r}
datasummary <- tempDaily%>%
  group_by(Station, fWY) %>%
  summarize(n = n())

ggplot(datasummary, aes(x = fWY, y = Station, fill = n)) + geom_tile() + scale_fill_viridis()
```






## Daily Max Temps  
**Scientific Questions:**

1. Has maximum temperature increased over time?
2. Are there regional trends in maximum temperature increase? 
3. Do trends in max temps correspond to water year type?

```{r dailyMaxPlot}
# Daily Trends
tempD_s <- tempDaily %>% group_by(Region) %>% sample_frac(.1)

max1 <- ggplot(tempD_s) + 
  geom_jitter(aes(x = WY, y = maxDaily, color = fMonth), size = .7)+
  stat_smooth(aes(x = WY, y = maxDaily, color = fMonth),method = "lm", formula = y ~ x, size = 1, se = TRUE)+ 
  labs(title = "Maximum daily temperature by month") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
ggplotly(max1)

# Regional Trends
max2 <- ggplot(tempD_s) + 
  geom_jitter(aes(x = WY, y = maxDaily, color = Region), size = .7)+
  stat_smooth(aes(x = WY, y = maxDaily, color = Region),method = "lm", formula = y ~ x, size = 1, se = FALSE)+ 
  labs(title = "Maximum daily temperature by region") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
ggplotly(max2)
```

### Look at interaction potential
* yday * WYType: yes
* yday * Region: yes
* Region * WYType: no

```{r InteractionsPlotsMax}
# WYType:yday
# WY type trend differs by yday
ggplot(tempD_s) + 
  geom_point(aes(x = yday, y = maxDaily, color = WYType2_Sac), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = yday, y = maxDaily, color = WYType2_Sac),method = "lm", formula = y ~ x + I(x^2), size = 1, se = TRUE)+ 
  labs(title = "WYType:yday") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

#see what it looks like with the sin-transformed yday
ggplot(tempD_s) + 
  geom_point(aes(x = syday, y = maxDaily, color = WYType2_Sac), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = syday, y = maxDaily, color = WYType2_Sac),method = "lm", size = 1, se = TRUE)+ 
  labs(title = "WYType:yday with sin-transformation") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:yday
# Regional trend seems to differ by yday
ggplot(tempD_s) + 
  geom_point(aes(x = yday, y = maxDaily, color = Region), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = yday, y = maxDaily, color = Region),method = "lm", formula = y ~ x + I(x^2), size = 1, se = TRUE)+ 
    labs(title = "Region:yday") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:WYType
ggplot(tempD_s) + 
  geom_boxplot(aes(x = Region, y = maxDaily, fill = WYType2_Sac)) + 
    labs(title = "Region:WYType") +
  scale_fill_viridis(option = "viridis", discrete = TRUE) + theme_bw()
```

### Models 

Add lag 
```{r}
# Account for Temporal Autocorrelation 
tempDaily <- tempDaily %>% 
    group_by(Region, Station) %>%
  mutate(maxDailylag1 = lag(maxDaily, 1),
         maxDailylag2 = lag(maxDaily, 2),
         meanDailylag1 = lag(meanDaily, 1),
         meanDailylag2 = lag(meanDaily, 2),
         minDailylag1 = lag(minDaily, 1),
         minDailylag2 = lag(minDaily, 2)) %>%
  ungroup() %>%
  mutate(yday_s = scale(yday),
         maxDailylag1_s = scale(maxDailylag1),
         maxDailylag2_s = scale(maxDailylag2),
         meanDailylag1_s = scale(meanDailylag1),
         meanDailylag2_s = scale(meanDailylag2),
         minDailylag1_s = scale(minDailylag1),
         minDailylag2_s = scale(minDailylag2))
```

Normal glm

Check for number of lags needed
```{r}
testMax <- tempDaily %>% filter(fWY %in% c(2014, 2015, 2016, 2017))
summary(M.testlag0 <- glm(maxDaily ~ Region + fWY + syday, data = testMax, na.action = na.omit))
summary(M.testlag1 <- glm(maxDaily ~ Region + fWY + maxDailylag1 + yday, data = testMax, na.action = na.omit))
summary(M.testlag2 <- glm(maxDaily ~ Region + fWY + maxDailylag1 + maxDailylag2 + yday, data = testMax, na.action = na.omit))

acf(residuals(M.testlag0))
acf(residuals(M.testlag1))
acf(residuals(M.testlag2))
```
1 lag should be fine

Test different time variables
```{r}
# Remove NAs from lag 
tempDaily2 <-na.omit(tempDaily)

# Run models
summary(M.maxDay1 <- glm(maxDaily~Region + fWY + yday + I(yday^2) + maxDailylag1, data = tempDaily2, na.action = na.omit))
summary(M.maxDay2 <- glm(maxDaily~Region + fWY + Month + I(Month^2) + maxDailylag1, data = tempDaily2, na.action = na.omit))
summary(M.maxDay3 <- glm(maxDaily~Region + fWY + syday + maxDailylag1, data = tempDaily2, na.action = na.omit))

AIC(M.maxDay1, M.maxDay2, M.maxDay3)

```
Quadratic julian day (yday) best

Interactions
```{r}
summary(M.maxDay4 <- glm(maxDaily~Region + fWY + yday + I(yday^2) + maxDailylag1 + fWY:(yday + I(yday^2)), data = tempDaily2, na.action = na.omit))

summary(M.maxDay5 <- glm(maxDaily~Region + fWY + yday + I(yday^2) + maxDailylag1 + fWY:Region, data = tempDaily2, na.action = na.omit))

summary(M.maxDay6 <- glm(maxDaily~Region + fWY + yday + I(yday^2) + maxDailylag1 + + fWY:(yday + I(yday^2)) + fWY:Region, data = tempDaily2, na.action = na.omit))

summary(M.maxDay7 <- glm(maxDaily~Region + fWY + yday + I(yday^2) + maxDailylag1 + (yday + I(yday^2)):Region, data = tempDaily2, na.action = na.omit))

AIC(M.maxDay4, M.maxDay5, M.maxDay6, M.maxDay7)
```

Chosen Model: **((M.maxDay4 <- glm(maxDaily~Region + fWY + yday + I(yday^2) + maxDailylag1 + fWY:(yday + I(yday^2))))**

Diagnostic plots
```{r}
par(mfrow = c(2,2))
res.mmax1 = resid(M.maxDay4, type = "pearson")
plot(M.maxDay4)
plot(tempDaily2$yday^2, res.mmax1)
plot(tempDaily2$Region, res.mmax1)
plot(tempDaily2$fWY, res.mmax1)

visreg(M.maxDay4, "fWY", by = "Region")
visreg(M.maxDay4, "yday", by = "Region")
visreg(M.maxDay4, "Region", by = "yday")
visreg(M.maxDay4, "fWY", by = "yday")
```

Mixed models
* Add Station as random variable
```{r}
summary(M.maxDay4a <- lmer(maxDaily~Region + fWY + yday_s + I(yday_s^2) + maxDailylag1_s + fWY:(yday_s + I(yday_s^2)) + (1|Station), data = tempDaily2, na.action = na.omit))

# Check temporal autocorrelation
# How correlated day 1 is to day 2, 3, etc. 
acf(residuals(M.maxDay4a))

# Diagnostic Plots
# https://www.ssc.wisc.edu/sscc/pubs/MM/MM_DiagInfer.html
# What is the right diagnostic plot for lmer?
par(mfrow = c(2,3))

res.mmax2 = resid(M.maxDay4a, type = "pearson")
lev1a = hatvalues(M.maxDay4a)
plot(M.maxDay4a)
qqnorm(res.mmax2)
qqline(res.mmax2)
plot(lev1a, y = res.mmax2)

plot(res.mmax2)
plot(tempDaily2$yday^2, res.mmax2)
plot(tempDaily2$Region, res.mmax2)
plot(tempDaily2$fWY, res.mmax2)
```

Best Model: **.maxDay4a <- lmer(maxDaily~Region + fWY + yday_s + I(yday_s^2) + maxDailylag1_s + fWY:(yday_s + I(yday_s^2)) + (1|Station), data = tempDaily2))**

### Conclusions

1. Has maximum temperature increased over time?
2. Are there regional trends in maximum temperature increase? 
3. Do trends in max temps correspond to water year type?









## Minimum Daily Temp

1. Has minimum temperature increased over time?
2. Are there regional trends in minimum temperature increase? 
3. Do mins correspond to water year type?

```{r dailyMinPlot}
# Daily Trends
min1 <- ggplot(tempD_s) + 
  geom_jitter(aes(x = WY, y = minDaily, color = fMonth), size = .7)+
  stat_smooth(aes(x = WY, y = minDaily, color = fMonth),method = "lm", formula = y ~ x, size = 1, se = TRUE)+ 
  labs(title = "Minimum daily temperature by month") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
ggplotly(min1)

# Regional Trends
min2 <- ggplot(tempD_s) + 
  geom_jitter(aes(x = WY, y = minDaily, color = Region), size = .7)+
  stat_smooth(aes(x = WY, y = minDaily, color = Region),method = "lm", formula = y ~ x, size = 1, se = FALSE)+ 
  labs(title = "Minimum daily temperature by region") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
ggplotly(min2)
```

### Look at interaction potential
* yday * WYType: yes
* yday * Region: yes
* Region * WYType: no

```{r InteractionsPlotsMin}
# WYType:yday
# WY type trend differs by yday
ggplot(tempD_s) + 
  geom_point(aes(x = yday, y = minDaily, color = WYType2_Sac), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = yday, y = minDaily, color = WYType2_Sac),method = "lm", formula = y ~ x + I(x^2), size = 1, se = TRUE)+ 
  labs(title = "WYType:yday") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

#see what it looks like with the sin-transformed yday
ggplot(tempD_s) + 
  geom_point(aes(x = syday, y = minDaily, color = WYType2_Sac), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = syday, y = minDaily, color = WYType2_Sac),method = "lm", size = 1, se = TRUE)+ 
  labs(title = "WYType:yday with sin-transformation") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:yday
ggplot(tempD_s) + 
  geom_point(aes(x = yday, y = minDaily, color = Region), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = yday, y = minDaily, color = Region),method = "lm", formula = y ~ x + I(x^2), size = 2, se = TRUE)+ 
    labs(title = "Region:yday") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:WYType
ggplot(tempD_s) + 
  geom_boxplot(aes(x = Region, y = minDaily, fill = WYType2_Sac)) + 
    labs(title = "Region:WYType") +
  scale_fill_viridis(option = "viridis", discrete = TRUE) + theme_bw()
```



Normal glm

Check for number of lags needed
```{r}
summary(M.testlag0 <- glm(minDaily ~ Region + fWY + syday, data = testMax, na.action = na.omit))
summary(M.testlag1 <- glm(minDaily ~ Region + fWY + minDailylag1 + yday, data = testMax, na.action = na.omit))
summary(M.testlag2 <- glm(minDaily ~ Region + fWY + minDailylag1 + minDailylag2 + yday, data = testMax, na.action = na.omit))

par(mfrow = c(2,2))
acf(residuals(M.testlag0))
acf(residuals(M.testlag1))
acf(residuals(M.testlag2))
```
2 lags needed

Test different time variables
```{r}
# Run models
summary(M.minDay1 <- glm(minDaily~Region + fWY + yday + I(yday^2) + minDailylag1 + minDailylag2, data = tempDaily2, na.action = na.omit))
summary(M.minDay2 <- glm(minDaily~Region + fWY + Month + I(Month^2) + minDailylag1 + minDailylag2, data = tempDaily2, na.action = na.omit))
summary(M.minDay3 <- glm(minDaily~Region + fWY + syday + minDailylag1 + minDailylag2, data = tempDaily2, na.action = na.omit))

AIC(M.minDay1, M.minDay2, M.minDay3)

```
Sin julian day (yday) best

Interactions
```{r}
summary(M.minDay4 <- glm(minDaily~Region + fWY + syday + minDailylag1 + minDailylag2 + fWY:(syday), data = tempDaily2, na.action = na.omit))

summary(M.minDay5 <- glm(minDaily~Region + fWY + syday + minDailylag1 + minDailylag2 +fWY:Region, data = tempDaily2, na.action = na.omit))

summary(M.minDay6 <- glm(minDaily~Region + fWY + syday + minDailylag1  + minDailylag2 +fWY:(syday) + fWY:Region, data = tempDaily2, na.action = na.omit))

summary(M.minDay7 <- glm(minDaily~Region + fWY + syday + minDailylag1 + minDailylag2 +(syday):Region, data = tempDaily2, na.action = na.omit))

AIC(M.minDay4, M.minDay5, M.minDay6, M.minDay7)
```

Chosen Model: **glm(minDaily~Region + fWY + syday + minDailylag1 + minDailylag2 +(syday):Region**

Diagnostic plots
```{r}
par(mfrow = c(2,2))
res.mmin1 = resid(M.minDay7, type = "pearson")
plot(M.minDay7)

plot(res.mmin1)
plot(tempDaily2$syday, res.mmin1)
plot(tempDaily2$Region, res.mmin1)
plot(tempDaily2$fWY, res.mmin1)

visreg(M.minDay7, "fWY", by = "Region")
visreg(M.minDay7, "syday", by = "Region")
visreg(M.minDay7, "Region", by = "syday")
visreg(M.minDay7, "fWY", by = "syday")
```

Mixed models
```{r}
summary(M.minDay7a <- lmer(minDaily~Region + fWY + syday + minDailylag1 + minDailylag2 + (syday):Region + (1|Station), data = tempDaily2, na.action = na.omit))

# Check temporal autocorrelation
# How correlated day 1 is to day 2, 3, etc. 
acf(residuals(M.minDay7a))

# Diagnostic Plots
# https://www.ssc.wisc.edu/sscc/pubs/MM/MM_DiagInfer.html
# What is the right diagnostic plot for lmer?
par(mfrow = c(2,3))

res.mmin2 = resid(M.minDay7a, type = "pearson")
lev2a = hatvalues(M.minDay7a)
plot(M.minDay7a)
qqnorm(res.mmin2)
qqline(res.mmin2)
plot(lev1a, y = res.mmin2)

plot(res.mmin2)
plot(tempDaily2$syday, res.mmin2)
plot(tempDaily2$Region, res.mmin2)
plot(tempDaily2$fWY, res.mmin2)
```

Best Model: **M.minDay7a <- lmer(minDaily~Region + fWY + syday + minDailylag1 + minDailylag2 + (syday):Region + (1|Station)**

### Conclusions

1. Has minimum temperature increased over time?
2. Are there regional trends in minimum temperature increase? 
3. Do mins correspond to water year type?









## Mean Daily Temp

1. Has mean temperature increased over time?
2. Are there regional trends in mean temperature increase? 
3. Do means correspond to water year type?

```{r dailyMeanPlot}
# Daily Trends
mean1 <- ggplot(tempD_s) + 
  geom_jitter(aes(x = WY, y = meanDaily, color = fMonth), size = .7)+
  stat_smooth(aes(x = WY, y = meanDaily, color = fMonth),method = "lm", formula = y ~ x, size = 1, se = TRUE)+ 
  labs(title = "Mean daily temperature by month") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
ggplotly(mean1)

# Regional Trends
mean2 <- ggplot(tempD_s) + 
  geom_jitter(aes(x = WY, y = meanDaily, color = Region), size = .7)+
  stat_smooth(aes(x = WY, y = meanDaily, color = Region),method = "lm", formula = y ~ x, size = 1, se = FALSE)+ 
  labs(title = "Mean daily temperature by region") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
ggplotly(mean2)
```

### Look at interaction potential
* yday * WYType: yes
* yday * Region: yes
* Region * WYType: no

```{r InteractionsPlotsMean}
# WYType:yday
# WY type trend differs by yday
ggplot(tempD_s) + 
  geom_point(aes(x = yday, y = meanDaily, color = WYType2_Sac), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = yday, y = meanDaily, color = WYType2_Sac),method = "lm", formula = y ~ x + I(x^2), size = 1, se = TRUE)+ 
  labs(title = "WYType:yday") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

#see what it looks like with the sin-transformed yday
ggplot(tempD_s) + 
  geom_point(aes(x = syday, y = meanDaily, color = WYType2_Sac), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = syday, y = meanDaily, color = WYType2_Sac),method = "lm", size = 1, se = TRUE)+ 
  labs(title = "WYType:yday with sin-transformation") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:yday
ggplot(tempD_s) + 
  geom_point(aes(x = yday, y = meanDaily, color = Region), size = 0.5, alpha = 0.5) + 
  stat_smooth(aes(x = yday, y = meanDaily, color = Region),method = "lm", formula = y ~ x + I(x^2), size = 1, se = TRUE)+ 
    labs(title = "Region:yday") +
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:WYType
ggplot(tempD_s) + 
  geom_boxplot(aes(x = Region, y = meanDaily, fill = WYType2_Sac)) + 
    labs(title = "Region:WYType") +
  scale_fill_viridis(option = "viridis", discrete = TRUE) + theme_bw()
```



Normal glm

Check for number of lags needed
```{r}
summary(M.testlag0 <- glm(meanDaily ~ Region + fWY + syday, data = testMax, na.action = na.omit))
summary(M.testlag1 <- glm(meanDaily ~ Region + fWY + meanDailylag1 + yday, data = testMax, na.action = na.omit))
summary(M.testlag2 <- glm(meanDaily ~ Region + fWY + meanDailylag1 + meanDailylag2 + yday, data = testMax, na.action = na.omit))

par(mfrow = c(2,2))
acf(residuals(M.testlag0))
acf(residuals(M.testlag1))
acf(residuals(M.testlag2))
```
2 lags needed

Test different time variables
```{r}
# Run models
summary(M.meanDay1 <- glm(meanDaily~Region + fWY + yday + I(yday^2) + meanDailylag1 + meanDailylag2, data = tempDaily2, na.action = na.omit))
summary(M.meanDay2 <- glm(meanDaily~Region + fWY + Month + I(Month^2) + meanDailylag1 + meanDailylag2, data = tempDaily2, na.action = na.omit))
summary(M.meanDay3 <- glm(meanDaily~Region + fWY + syday + meanDailylag1 + meanDailylag2, data = tempDaily2, na.action = na.omit))

AIC(M.meanDay1, M.meanDay2, M.meanDay3)

```
Sin julian day (yday) best

Interactions
```{r}
summary(M.meanDay4 <- glm(meanDaily~Region + fWY + syday + meanDailylag1 + meanDailylag2 + fWY:(syday), data = tempDaily2, na.action = na.omit))

summary(M.meanDay5 <- glm(meanDaily~Region + fWY + syday + meanDailylag1 + meanDailylag2 +fWY:Region, data = tempDaily2, na.action = na.omit))

summary(M.meanDay6 <- glm(meanDaily~Region + fWY + syday + meanDailylag1  + meanDailylag2 +fWY:(syday) + fWY:Region, data = tempDaily2, na.action = na.omit))

summary(M.meanDay7 <- glm(meanDaily~Region + fWY + syday + meanDailylag1 + meanDailylag2 +(syday):Region, data = tempDaily2, na.action = na.omit))

AIC(M.meanDay4, M.meanDay5, M.meanDay6, M.meanDay7)
```

Chosen Model: **glm(meanDaily~Region + fWY + syday + meanDailylag1 + meanDailylag2 +(syday):Region**

Diagnostic plots
```{r}
par(mfrow = c(2,2))
res.mmean1 = resid(M.meanDay7, type = "pearson")
plot(M.meanDay7)

plot(res.mmean1)
plot(tempDaily2$syday, res.mmean1)
plot(tempDaily2$Region, res.mmean1)
plot(tempDaily2$fWY, res.mmean1)

visreg(M.meanDay7, "fWY", by = "Region")
visreg(M.meanDay7, "syday", by = "Region")
visreg(M.meanDay7, "Region", by = "syday")
visreg(M.meanDay7, "fWY", by = "syday")
```

Mixed models
```{r}
summary(M.meanDay7a <- lmer(meanDaily~Region + fWY + syday + meanDailylag1 + meanDailylag2 + (syday):Region + (1|Station), data = tempDaily2, na.action = na.omit))

# Check temporal autocorrelation
# How correlated day 1 is to day 2, 3, etc. 
acf(residuals(M.meanDay7a))

# Diagnostic Plots
# https://www.ssc.wisc.edu/sscc/pubs/MM/MM_DiagInfer.html
# What is the right diagnostic plot for lmer?
par(mfrow = c(2,3))

res.mmean2 = resid(M.meanDay7a, type = "pearson")
lev3a = hatvalues(M.meanDay7a)
plot(M.meanDay7a)
qqnorm(res.mmean2)
qqline(res.mmean2)
plot(lev3a, y = res.mmean2)

plot(res.mmean2)
plot(tempDaily2$syday, res.mmean2)
plot(tempDaily2$Region, res.mmean2)
plot(tempDaily2$fWY, res.mmean2)
```

Best Model: **M.meanDay7a <- lmer(meanDaily~Region + fWY + syday + meanDailylag1 + meanDailylag2 + (syday):Region + (1|Station)**

### Conclusions

1. Has mean temperature increased over time?
2. Are there regional trends in mean temperature increase? 
3. Do means correspond to water year type?

