---
title: "TempTrendModels"
author: "Catarina Pien"
date: "9/10/2020"
output: 
  html_document:
    code_folding: hide
    editor_options: 
      chunk_output_type: console
---
# Temperature Trend Analysis {.tabset}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly)
library(pscl)
library(visreg)
library(lattice)
```

## Data Prep and Exploration
Data import
```{r import, include = FALSE, message = FALSE, warning = FALSE}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")

tempFilt0 <- readRDS("Data/Temp_filtered.rds") %>%
  select(-StationName) # temperature data 

Regions <- read.csv("Data/Stations_wRosiesReg.csv") %>%
  select(-c(Latitude, Longitude)) # Rosie's Regions

staInfo <- read.csv("Data/StationsMetadata.csv") # Get habitat type here

LatLon <- select(staInfo, c("Station", "StationName", "Latitude", "Longitude"))

WYType <- read.csv("Data/WYType.csv") %>% # Get WY, WY type, Index 
  select(-c(starts_with("Runoff"))) %>%
  rename(WY = Year) %>%
   mutate(Index_c = Index_Sac + Index_SJ) 

WYSimple <- select(WYType, c("WY", "WYType2_Sac", "Index_c"))

str(tempFilt0)
```

Add variables
```{r vars}
tempFilt0 <- tempFilt0 %>%
  mutate(Year = year(tempFilt0$Date),
         Month = month(tempFilt0$Date),
         yDay = yday(tempFilt0$Date)) %>%
  mutate(WY = ifelse(Month %in% c(10, 11, 12), Year+1, Year))
```

Merge regions, habitats, wytype
```{r regions, message = FALSE, warning = FALSE}
# subregions <- st_read("Data/EDSM_Subregions/EDSM_Subregions_03302020.shp")

tempFilt1 <- left_join(tempFilt0, Regions, by = "Station") %>%
  filter(!Station %in% c("CNT", "CPP", "DAR", "DMC", "DYR","ECD", "HBP", "ROR", "DV7"),
         !is.na(Region)) 
tempFilt2 <- left_join(tempFilt1, staInfo, by = "Station") %>%
  select(-c(StartDateDataset:County))

tempFilt <- left_join(tempFilt2, WYSimple, by = "WY") 

tempFilt$Region <- as.factor(tempFilt$Region)
tempFilt$HabitatType <- as.factor(tempFilt$HabitatType)

# saveRDS(tempFilt, "Data/tempFilt.rds")

```

* Number of years of data per station per Region
* Filter to years with >250 days of data/year

```{r Filtering down }
StationYearCombo <- tempFilt %>%
  group_by(Region, Station, WY, Date) %>%
  summarize(perDay = n()) %>%
  ungroup() %>%
  group_by(Region, Station, WY) %>%
  summarize(totalDays = n()) %>%
  ungroup()

StationNyears <- StationYearCombo %>%
  filter(totalDays>250) %>%
  group_by(Region, Station) %>%
  summarize(firstYear = first(WY),
            lastYear = last(WY),
            nYear = n()) %>%
  ungroup()
```

Some exploratory plots to look at data
```{r exploratory plots}
tilerecord <- ggplot(StationYearCombo, aes(Station, ordered(WY), fill = totalDays)) + geom_tile() + labs(title = "Period of Record - Number of days each year for each station")
ggplotly(tilerecord)

nyears <- ggplot(StationNyears, aes(x = Region, y = nYear, color = Station)) + geom_point() +
  labs(title = "Number of years of data by Region/Station, filtered for years with >200 days data")
ggplotly(nyears)

nYearBar <- ggplot(StationNyears, aes(y = ..count.., x = nYear)) + geom_bar() +
  labs(title = "Count of Stations and number of years of data available")
ggplotly(nYearBar)

```

Map showing distribution of data with number of years of data
```{r map}
library(leaflet)

MapYears <- left_join(StationNyears, LatLon)

# Palette from viridis
  staPal <- colorNumeric("viridis", domain = MapYears$nYear)
  
MapYears %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    color = ~staPal(nYear),
    stroke = FALSE,
    fillOpacity = 0.9,
    lng = ~Longitude,
    lat = ~Latitude,
    labelOptions = labelOptions(noHide = F),
    popup = ~paste(Station, ":", StationName, "<br/>", "nYears:", nYear, "<br/>",
                   "Date Range:", firstYear, "-", lastYear)) %>%
    addLegend(pal = staPal,
            values = ~nYear,
            position = "bottomright")
```

Map 10 years+ Data
```{r}
# Filter for those with 10 years + 
MapYears2 <- MapYears %>% filter(nYear > 9)

# Palette from viridis
  staPal2 <- colorNumeric("magma", domain = MapYears2$nYear)
  
MapYears2 %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    color = ~staPal2(nYear),
    stroke = FALSE,
    fillOpacity = 0.9,
    lng = ~Longitude,
    lat = ~Latitude,
    labelOptions = labelOptions(noHide = F),
    popup = ~paste(Station, ":", StationName, "<br/>", "nYears:", nYear, "<br/>",
                   "Date Range:", firstYear, "-", lastYear)) %>%
    addLegend(pal = staPal2,
            values = ~nYear,
            position = "bottomright")
```

Subset data to use to data that has at least 10 years of data, and that extends to 2019, and each year has > 250 days of data
Took out Far North Region. Should we add LIS somewhere else?
```{r subset}
DataYrSubset <- filter(StationNyears, nYear > 9 & lastYear == 2019) %>%
  left_join(StationYearCombo) 

tempToUse <- inner_join(tempFilt, DataYrSubset, by = c("Region","Station", "WY")) %>%
  filter(Region != "Far North") %>%
  filter(totalDays > 250)

tempToUse$WY = as.numeric(tempToUse$WY)
today = format(today(), "%Y%m%d")
#saveRDS(tempToUse, paste0("Data/temp10years_", today, ".rds"))
```

## Mean, Max, Min {.tabset}

#### Overall Datasets 

#### Data Wrangling 
* Create dataset for mean, max, and min, var for Monthly
* Filter for data that is represented for a whole year
* Create datasets for mean, max, min

Daily Temp
```{r dailyoverall}
tempDaily <- tempToUse %>%
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c, Date) %>%
  summarize(maxDaily = max(Temp),
            minDaily = min(Temp),
            meanDaily = round(mean(Temp),1),
            rangeTemp = maxDaily-minDaily) %>%
  ungroup()
tempDaily$WY <- as.numeric(tempDaily$WY)
#saveRDS(tempDaily, "Data/tempDaily.rds")
```

Monthly Temp
```{r monthlyoverall, message = FALSE, warning = FALSE}
tempMon <- tempToUse %>% 
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c, Month) %>%
  summarize(maxTemp = max(Temp),
            minTemp = min(Temp),
            meanTemp = round(mean(Temp),1),
            rangeTemp = maxTemp-minTemp) %>%
  ungroup()
#saveRDS(tempMon, "Data/tempMonthly.rds")
```

Annual Temp
```{r annualoverall}
tempAn <- tempToUse %>% 
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c) %>%
  summarize(maxTemp = max(Temp),
            minTemp = min(Temp),
            meanTemp = round(mean(Temp),1),
            rangeTemp = maxTemp-minTemp) %>%
  ungroup()
#saveRDS(tempAn, "Data/tempAnnual.rds")
```

Code to make sure every month has data - currently is not being used (need to join with above)
```{r nMon}
# Filter to only data that has temps from every month so as not to skew the data that only has part of the year represented.
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

nMon$WY <- as.numeric(nMon$WY)
```

### Max Temp {.tabset}

Mean Max Temp
```{r Mean Max}
tempMaxAvMon0 <- tempToUse %>%
  group_by(Region, Station, Year, WY, WYType2_Sac, Month, Date) %>%
  summarize(maxTemp = max(Temp)) %>%
  ungroup() %>%
  group_by(Region, Station, Year, WY, WYType2_Sac,Month) %>%
  summarize(maxAv = mean(maxTemp))
```

#### Models
* Region
* Habitat Type
* Water Year Type:
    + Wet = Wet
    + Mid = Above or Below Normal
    + Dry = Dry or Critical
* Index (combined SJ and Sac)
* Month
* Year (can sometimes conflict) or WY if leaving WYType in model
* Julian day (yday)

Daily Max
Best Model: summary(M.maxDay3 <- glm(maxDaily~Region*Year + Month + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

```{r Models Daily Max}
tempDaily <- filter(tempDaily, WY > 2009 & WY < 2020)
tempDaily$yday = yday(tempDaily$Date)
tempDaily$Year = ordered(year(tempDaily$Date))
tempDaily$Month = month(tempDaily$Date)
tempDailyM <- left_join(tempDaily, nMon) %>%
  filter(nMon == 12)

tempDaily$WYType2_Sac = as.factor(tempDaily$WYType2_Sac)

# Using WYType
summary(M.maxDay1 <- glm(maxDaily~Region + Year + Month + HabitatType + WYType2_Sac + yday, data = tempDaily, na.action = na.omit))

# Using Index_c
summary(M.maxDay2 <- glm(maxDaily~Region + Year + Month + HabitatType + Index_c + yday, data = tempDaily, na.action = na.omit))

# Compare
AIC(M.maxDay1, M.maxDay2) # WY Type seems more useful

# R2 
with(summary(M.maxDay1), 1 - deviance/null.deviance)

# Interactions?
summary(M.maxDay3 <- glm(maxDaily~Region*Year + Month + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

summary(M.maxDay4 <- glm(maxDaily~Region*WYType2_Sac + Year  + Month + HabitatType, data = tempDaily, na.action = na.omit))

AIC(M.maxDay1, M.maxDay3, M.maxDay4)

par(mfrow = c(2,2))
plot(M.maxDay3)
visreg(M.maxDay3, "Year", by = "Region")
visreg(M.maxDay3, "Year", by = "WYType2_Sac")

```

#### ADDED ####
```{r}

# yday as quadratic
summary(M.maxDay3A <- glm(maxDaily~I(yday^2) + Region + Month + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

visreg(M.maxDay3)
par(mfrow = c(2,2))
plot(M.maxDay3)

# not quadratic
summary(M.maxDay3B <- glm(maxDaily~yday + Region + Month + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

AIC(M.maxDay3A, M.maxDay3B) # quadratic better


library(lme4)
library(lmerTest)
summary(M.maxDay3C <- lmer(maxDaily~I(yday^2) + Region + (1|Year) + Month + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))


# Account for Temporal Autocorrelation 
tempDaily <- tempDaily %>% 
    group_by(Region, Station) %>%
  mutate(maxDailylag = lag(maxDaily, 1)) %>%
  ungroup() %>%
  mutate(yday_s = scale(yday),
         maxDailylag_s = scale(maxDailylag))

summary(M.maxDay3D <- lmer(maxDaily~I(yday_s^2) + maxDailylag_s + Region + (1|Year) + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

summary(M.maxDay3D)
summary(M.maxDay3E <- lmer(maxDaily~I(Month^2) + maxDailylag_s + Region + (1|Year) +  HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

AIC(M.maxDay3D, M.maxDay3E) # yday just barely better

visreg(M.maxDay3D)
par(mfrow = c(2,2))
plot(M.maxDay3D)
```

Interactions - If you don't see it in the main effects, try interactions

Region*Month/yday
WYType2_Sac*Month/yday
Region*WYType2_Sac
* lower max temps in Suisun Bay
```{r}

tempDaily_s <- sample(tempDaily_s, 500)
ggplot(tempDaily, aes(x = yday, y = maxDaily, color = WYType2_Sac)) + geom_point()

```





Monthly Max
Best Model: maxTemp ~ Region * WY + Region * Month + Habitat Type
```{r Models Max Monthly Temp}
tempMon$WY <- as.numeric(tempMon$WY)
tempMon <- filter(tempMon, WY > 2000 & WY < 2020)
tempMonM <- left_join(tempMon, nMon) %>%
  filter(nMon == 12)

tempMonM$WY <- ordered(tempMonM$WY)

summary(M.max1 <- glm(maxTemp~Region + Month + WYType2_Sac + HabitatType, data = tempMonM))
summary(M.max2 <- glm(maxTemp~Region + WY + Month + HabitatType, data = tempMonM))
summary(M.max3 <- glm(maxTemp~Region*Month + WY + HabitatType, data = tempMonM))
summary(M.max4 <- glm(maxTemp~Region*WY + Month + HabitatType, data = tempMonM))
summary(M.max5 <- glm(maxTemp~Region*WYType2_Sac + Region*Month + HabitatType, data = tempMonM))
summary(M.max6 <- glm(maxTemp~Region*WYType2_Sac + Region*Month + HabitatType, data = tempMonM))
summary(M.max7 <- glm(maxTemp~Region*WY + Region*Month + HabitatType, data = tempMonM, na.action =na.omit))
summary(M.max8 <- glm(maxTemp~Region*WY + Region*Month, data = tempMonM))

AIC(M.max1, M.max2, M.max3, M.max4, M.max5, M.max6, M.max7, M.max8)

par(mfrow = c( 2,2))
plot(M.max7)

visreg(M.max7, "WY", by = "Region")
visreg(M.max7, "Month", by = "Region")
visreg(M.max7, "Region", by = "WY")
visreg(M.max7, "WY", by = "HabitatType")

```

Monthly Mean Max
```{r}


```

Annual Max
Best model: summary(M.maxAn3 <- glm(maxTemp~Region * WYType2_Sac + WY+ HabitatType, data = tempAn))
```{r Models Max Annual Temp}
tempAn$WY <- ordered(tempAn$WY)

summary(M.maxAn1 <- glm(maxTemp~Region + WY + WYType2_Sac + HabitatType, data = tempAn))
summary(M.maxAn2 <- glm(maxTemp~Region + WY + WYType2_Sac, data = tempAn))
summary(M.maxAn3 <- glm(maxTemp~Region * WYType2_Sac + WY+ HabitatType, data = tempAn))
summary(M.maxAn4 <- glm(maxTemp~Region * WY + HabitatType + WYType2_Sac, data = tempAn))
summary(M.maxAn5 <- glm(maxTemp~Region * WYType2_Sac +  Region * WY + HabitatType , data = tempAn))

AIC(M.maxAn1, M.maxAn2, M.maxAn3, M.maxAn4, M.maxAn5)

par(mfrow = c( 2,2))
plot(M.maxAn3)

visreg(M.maxAn3, "WY", by  = "Region")
visreg(M.maxAn3, "WYType2_Sac", by = "Region")
visreg(M.maxAn3, "Region", by = "WYType2_Sac")
```


### Mean Temp{.tabset}
#### Data Wrangling

#### Models 

Mean Daily 
Best Model: summary(M.meanDay3 <- glm(meanDaily~Region * Year + Month + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

Need to check for autocorrelation
```{r MeanDaily Model, warning = FALSE, message = FALSE}
# Using WYType
summary(M.meanDay1 <- glm(meanDaily~Region + Year + Month + HabitatType + WYType2_Sac + yday, data = tempDaily, na.action = na.omit))

summary(M.meanDay2 <- glm(meanDaily~Region + Year + Month + HabitatType + Index_c + yday, data = tempDaily, na.action = na.omit))

AIC(M.meanDay1, M.meanDay2) # Choose WYType

#Remove yday
summary(M.meanDay3 <- glm(meanDaily~Region * Year + Month + HabitatType + WYType2_Sac, data = tempDaily, na.action = na.omit))

summary(M.meanDay4 <- glm(meanDaily~Region * WYType2_Sac + Year + Month + HabitatType, data = tempDaily, na.action = na.omit))

AIC(M.meanDay1, M.meanDay3, M.meanDay4)

par(mfrow = c(2,2))

plot(M.meanDay3)
visreg(M.meanDay3, "Year", by = "Region")
visreg(M.meanDay3, "Region", by = "WYType2_Sac")
visreg(M.meanDay3, "Year", by = "HabitatType")

```

Mean Monthly
Best Model: summary(M.meanMon7 <- glm(meanTemp~Region * WY + Region * Month + HabitatType, data = tempMon))
```{r MonthlyMeanModels}
summary(M.meanMon1 <- glm(meanTemp~Region + Month + WYType2_Sac + HabitatType, data = tempMon))
summary(M.meanMon2 <- glm(meanTemp~Region + WY + Month + HabitatType, data = tempMon))
AIC(M.meanMon1, M.meanMon2)

summary(M.meanMon3 <- glm(meanTemp~Region*Month + WY + HabitatType, data = tempMon))
summary(M.meanMon4 <- glm(meanTemp~Region*WY + Month + HabitatType, data = tempMon))
summary(M.meanMon5 <- glm(meanTemp~Region*WYType2_Sac + Month + HabitatType, data = tempMon))
summary(M.meanMon6 <- glm(meanTemp~Region*WYType2_Sac + Region*Month + HabitatType, data = tempMon))
summary(M.meanMon7 <- glm(meanTemp~Region*WY + Region*Month + HabitatType, data = tempMon))
summary(M.meanMon8 <- glm(meanTemp~Region*WY + Region*Month, data = tempMon))
summary(M.meanMon9 <- glm(meanTemp~Region*WY + Region*Month + Region * WYType2_Sac + HabitatType, data = tempMon))

AIC(M.meanMon1, M.meanMon2, M.meanMon3, M.meanMon4, M.meanMon5, M.meanMon6, M.meanMon7, M.meanMon8, M.meanMon9)

par(mfrow = c( 2,2))
plot(M.meanMon7)

visreg(M.meanMon7)
visreg(M.meanMon7, "WY", by = "Region")
visreg(M.meanMon7, "Month", by = "Region")
visreg(M.meanMon7, "Region", by = "WY")

```

Mean Annual 
```{r Models Mean Annual Temp}

summary(M.meanAn1 <- glm(meanTemp~Region + WY + WYType2_Sac + HabitatType, data = tempAn))
summary(M.meanAn2 <- glm(meanTemp~Region + WY + WYType2_Sac, data = tempAn))
summary(M.meanAn3 <- glm(meanTemp~Region * WYType2_Sac + WY+ HabitatType, data = tempAn))
summary(M.meanAn4 <- glm(meanTemp~Region * WY + HabitatType + WYType2_Sac, data = tempAn))
summary(M.meanAn5 <- glm(meanTemp~Region * WYType2_Sac +  Region * WY + HabitatType , data = tempAn))

AIC(M.meanAn1, M.meanAn2, M.meanAn3, M.meanAn4, M.meanAn5)

par(mfrow = c( 2,2))
plot(M.meanAn3)

visreg(M.meanAn3, "WY", by  = "Region")
visreg(M.meanAn3, "WYType2_Sac", by = "Region")
visreg(M.meanAn3, "Region", by = "WYType2_Sac")
```


### Min Temp{.tabset}
#### Data Wrangling 
#### Models 

Min Monthly
```{r}
summary(M.minMon1 <- glm(minTemp~Region + Month + WYType2_Sac + HabitatType, data = tempMon))
summary(M.minMon2 <- glm(minTemp~Region + WY + Month + HabitatType, data = tempMon))
AIC(M.minMon1, M.minMon2)

summary(M.minMon3 <- glm(minTemp~Region*Month + WY + HabitatType, data = tempMon))
summary(M.minMon4 <- glm(minTemp~Region*WY + Month + HabitatType, data = tempMon))
summary(M.minMon5 <- glm(minTemp~Region*WYType2_Sac + Month + HabitatType, data = tempMon))
summary(M.minMon6 <- glm(minTemp~Region*WYType2_Sac + Region*Month + HabitatType, data = tempMon))
summary(M.minMon7 <- glm(minTemp~Region*WY + Region*Month + HabitatType, data = tempMon))
summary(M.minMon8 <- glm(minTemp~Region*WY + Region*Month, data = tempMon))
summary(M.minMon9 <- glm(minTemp~Region*WY + Region*Month + Region * WYType2_Sac + HabitatType, data = tempMon))

AIC(M.minMon1, M.minMon2, M.minMon3, M.minMon4, M.minMon5, M.minMon6, M.minMon7, M.minMon8, M.minMon9)

par(mfrow = c( 2,2))
plot(M.minMon7)

visreg(M.minMon7)
visreg(M.minMon7, "WY", by = "Region")
visreg(M.minMon7, "Month", by = "Region")
visreg(M.minMon7, "Region", by = "WY")
```


Min Annual
```{r}
summary(M.minAn1 <- glm(minTemp~Region + WY + WYType2_Sac + HabitatType, data = tempAn))
summary(M.minAn2 <- glm(minTemp~Region + WY + WYType2_Sac, data = tempAn))
summary(M.minAn3 <- glm(minTemp~Region * WYType2_Sac + WY+ HabitatType, data = tempAn))
summary(M.minAn4 <- glm(minTemp~Region * WY + HabitatType + WYType2_Sac, data = tempAn))
summary(M.minAn5 <- glm(minTemp~Region * WYType2_Sac +  Region * WY + HabitatType , data = tempAn))

AIC(M.minAn1, M.minAn2, M.minAn3, M.minAn4, M.minAn5)

par(mfrow = c( 2,2))
plot(M.minAn3)

visreg(M.minAn3, "WY", by  = "Region")
visreg(M.minAn3, "WYType2_Sac", by = "Region")
visreg(M.minAn3, "Region", by = "WYType2_Sac")
```


## Variance/Range {.tabset}
### Data Wrangling
### Models
Monthly Range
```{r RangeModel}
summary(M.range1 <- glm(rangeTemp~Region + Month + WYType2_Sac + HabitatType, data = tempMonM))
summary(M.range2 <- glm(rangeTemp~Region + WY + Month + HabitatType, data = tempMonM))
summary(M.range3 <- glm(rangeTemp~Region*Month + WY + HabitatType, data = tempMonM))
summary(M.range4 <- glm(rangeTemp~Region*WY + Month + HabitatType, data = tempMonM))
summary(M.range5 <- glm(rangeTemp~Region*WYType2_Sac + Region*Month + HabitatType, data = tempMonM))
summary(M.range6 <- glm(rangeTemp~Region*WYType2_Sac + Region*Month + HabitatType, data = tempMonM))
summary(M.range7 <- glm(rangeTemp~Region*WY + Region*Month + HabitatType, data = tempMonM, na.action =na.omit))
summary(M.range8 <- glm(rangeTemp~Region*WY + Region*Month, data = tempMonM))

AIC(M.range1, M.range2, M.range3, M.range4, M.range5, M.range6, M.range7, M.range8)

par(mfrow = c( 2,2))
plot(M.range7)

visreg(M.range7, "WY", by = "Region")
visreg(M.range7, "Month", by = "Region")
visreg(M.range7, "Region", by = "WY")
visreg(M.range7, "WY", by = "HabitatType")
```

Annual Range
```{r}
summary(M.rangeAn1 <- glm(rangeTemp~Region + WY + WYType2_Sac + HabitatType, data = tempAn))
summary(M.rangeAn2 <- glm(rangeTemp~Region + WY + WYType2_Sac, data = tempAn))
summary(M.rangeAn3 <- glm(rangeTemp~Region * WYType2_Sac + WY+ HabitatType, data = tempAn))
summary(M.rangeAn4 <- glm(rangeTemp~Region * WY + HabitatType + WYType2_Sac, data = tempAn))
summary(M.rangeAn5 <- glm(rangeTemp~Region * WYType2_Sac +  Region * WY + HabitatType , data = tempAn))

AIC(M.rangeAn1, M.rangeAn2, M.rangeAn3, M.rangeAn4, M.rangeAn5)

par(mfrow = c( 2,2))
plot(M.rangeAn3)

visreg(M.rangeAn3, "WY", by  = "Region")
visreg(M.rangeAn3, "WYType2_Sac", by = "Region")
visreg(M.rangeAn3, "Region", by = "WYType2_Sac")
```


## Diel Variation {.tabset}
### Data Wrangling 
### Models 

## Stress Levels {.tabset}
### High Stress Days {.tabset}
#### Data Wrangling 

Identifying Heat Stress Level (High/Med/Low) 
Identifying "StressAllDay" = when min daily temperature >25 (could change this)
```{r heatevents}
# Flagging starts on day 3 of >25C
heat <- tempDaily %>%
  select(-meanDaily) %>%
  group_by(Region, Station, HabitatType, WY) %>%
  mutate(Thr25 = ifelse(maxDaily > 25, 1L, 0L),
         Thr21 = ifelse(maxDaily > 21, 1L, 0L)) %>%
  mutate(Stress = ifelse(Thr25 == lag(Thr25, 1) & Thr25 == lag(Thr25, 2) & Thr25 == 1L, "High", 
                            ifelse(Thr21 == lag(Thr21, 1) & Thr21 == lag(Thr21, 2) & Thr21 == 1, "Med", 
                                   "Low"))) %>%
  ungroup() %>%
  group_by(Region, Station, HabitatType, WY, Date) %>%
  mutate(StressAllDay = ifelse(Stress == "High" & minDaily>25, "Y", "N")) %>%
  select(-starts_with("Thr"))

# saveRDS(heat, "Data/heatstressDaily.rds")
```

Number of days at each stress level
```{r}
# Calculate number of samples in a year or water year
heatDaysSamp <- heat %>%
  group_by(Region, Station, HabitatType, WY) %>%
  summarize(totalDays = n()) %>%
  filter(totalDays > 250)

# Calculate number of days and proportion of days at each stress level
heatDays <- heat %>%
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Stress) %>%
  summarize(nDays = n()) %>%
  left_join(heatDaysSamp) %>%
  mutate(propDays = round(nDays/totalDays,3)) %>%
  ungroup()

```


High heat stress
Remove Far North and WY < 2000
```{r}
# Count number of days at high heat
HighHeat <- heatDays %>%
  mutate(DaysNotHigh = totalDays-nDays) %>%
           filter(Stress == "High",
         Region != "Far North",
         WY > 2009 & WY < 2020)

HighHeat$WY <- ordered(HighHeat$WY)
#  complete(WY, nesting(Station, Region, HabitatType), fill = list(nDays = 0))

summary(HighHeat)
```

#### Models {.tabset}
Best model: heat2 <- glm(propDays ~ Region + WYType2_Sac, family = "binomial", data = HighHeat)) BUT nothing is significant! 
Questions:
* Why does binomial result in no significance? 
* nDays vs propDays

```{r heatmodels}
library(nlme)
HighHeat$WY <- ordered(HighHeat$WY)
HighHeat$Region <- factor(HighHeat$Region)
HighHeat$WYType2_Sac <- factor(HighHeat$WYType2_Sac)
HighHeat$HabitatType <- factor(HighHeat$HabitatType)

# Model
# Model 1
heat1 <- glm(nDays ~ HabitatType + Region * WYType2_Sac,  data = HighHeat)
summary(heat1)

par(mfrow = c(2,2))
plot(heat1)
E = resid(heat1)
plot(HighHeat$Region, E)
plot(HighHeat$WYType2_Sac, E)
plot(HighHeat$HabitatType, E)

visreg(heat1, "WYType2_Sac", by = "Region")

summary(heat1 <- glm(propDays ~ Region + WYType2_Sac + HabitatType, family = "binomial", data = HighHeat))

summary(heat2 <- glm(propDays ~ Region + WYType2_Sac, family = "binomial", data = HighHeat))

summary(heat3 <- glm(propDays ~ Region * WYType2_Sac, family = "binomial", data = HighHeat))

(heat4 <- glm(propDays ~ Region + WY + HabitatType, family = "binomial", data = HighHeat))

(heat5 <- glm(propDays ~ Region + WY, family = "binomial", data = HighHeat))

(heat6 <- glm(propDays ~ Region * WY, family = "binomial", data = HighHeat))

AIC(heat1, heat2, heat3, heat4, heat5, heat6)

par(mfrow = c(2,2))
plot(heat2)
visreg(heat2)
visreg(heat2, "Region", by = "WYType2_Sac")
visreg(heat2, "WYType2_Sac", by = "Region")
```

### High stress days no recovery {.tabset}
#### Heatmap
```{r no recovery}
heatNoRecovery <-  heat  %>%
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c, StressAllDay) %>%
  summarize(NoRecovery = n())

heatNoRecoverySum <- filter(heatNoRecovery,
                 StressAllDay == "Y") 
hotSta <- unique(heatNoRecoverySum$Station)
hmapNoRecov <- ggplot(heatNoRecoverySum, aes(x = WY, y = Station, fill = NoRecovery )) + geom_tile() +
  scale_fill_viridis(option = "cividis") + labs(title = "Number of unrecovered high stress days per year")
ggplotly(hmapNoRecov)

```

#### Models
Stress All Day
Best Model: summary(heatA <- glm(NoRecovery ~ Region + WYType2_Sac + HabitatType, data = heatNoRecoverySum))
To Solve: 
* Residuals look unhappy - change variance structure?
* Use nDays vs propDays
* Add 0s in to years with 0 days? --> different distribution? 

```{r stressAllDay Models}
summary(heatA <- glm(NoRecovery ~ Region + WYType2_Sac + HabitatType, data = heatNoRecoverySum))

summary(heatB <- glm(NoRecovery ~ Region + WY + HabitatType, data = heatNoRecoverySum))

summary(heatC <- glm(NoRecovery ~ Region * WYType2_Sac + HabitatType, data = heatNoRecoverySum))

AIC(heatA, heatB, heatC)
par(mfrow = c(2,2))
plot(heatA)
visreg(heatA, "WYType2_Sac", by = "Region")
visreg(heatA, "HabitatType", by = "Region")
```
