---
title: "TempTrendGAM"
author: "Catarina Pien"
date: "9/22/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Temperature Trend Analysis {.tabset}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly)
library(pscl)
library(visreg)
library(lattice)
library(mgcv)
```

## Data Prep and Exploration
Data import
```{r import, include = FALSE, message = FALSE, warning = FALSE}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")

tempFilt <- readRDS("Data/tempFilt.rds") 
tempToUse <- readRDS("Data/temp10years_20200922.rds")
tempAn <- readRDS("Data/tempAnnual.rds")
tempMon <- readRDS("Data/tempMonthly.rds")
tempDaily <- readRDS("Data/tempDaily.rds")
tempHeat <- readRDS("Data/heatstressDaily.rds")

```

Code to make sure every month has data - currently is not being used (need to join with above)
```{r nMon}
# Filter to only data that has temps from every month so as not to skew the data that only has part of the year represented.
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

nMon$WY <- as.numeric(nMon$WY)
```

GAM for Daily Max
bs = "cc" for month and yday (cyclic cubic regression splines)
https://stat.ethz.ch/R-manual/R-patched/library/mgcv/html/smooth.terms.html
```{r Models Daily Max}
tempDaily <- filter(tempDaily, WY > 2009 & WY < 2020)
tempDaily$yday = yday(tempDaily$Date)
tempDaily$Year = ordered(year(tempDaily$Date))
tempDaily$Month = month(tempDaily$Date)
tempDaily$MonthF = ordered(tempDaily$Month)
tempDailyM <- left_join(tempDaily, nMon) %>%
  filter(nMon == 12)

tempDaily$WYType2_Sac = as.factor(tempDaily$WYType2_Sac)

#basic model of max temp based on day and location

gdmax1 =  bam(maxDaily ~ s(yday, bs = "cc") +  
          MonthF + Region + WYType2_Sac, 
          data =tempDaily, method = "REML")
summary(gdmax1)

r1 = acf(resid(gdmax1),  plot=FALSE)$acf[2]
plot(gdmax1, pages = 1, all.terms = TRUE, se = TRUE)

gdmax2 =  bam(maxDaily~ s(yday, bs = "cc") +  
          s(Month, bs = "cc") + Region + WYType2_Sac,
          data =tempDaily, method = "REML")
summary(gdmax2)
plot(gdmax2, pages = 1, all.terms = TRUE, se = TRUE)

gdmax3 =  bam(maxDaily~ s(yday, bs = "cc") +  
          s(Month, bs = "cc") + Region + WYType2_Sac + HabitatType + Year,
          data =tempDaily, method = "REML")
summary(gdmax3)
plot(gdmax3, pages = 1, all.terms = TRUE, se = TRUE)

par(mfrow = c(2,2))
gam.check(gdmax3)

gdmax4 =  bam(maxDaily~ s(yday, bs = "cc") +  
          s(Month, bs = "cc", by = WYType2_Sac) + Region + HabitatType + Year,
          data =tempDaily, method = "REML")
summary(gdmax4)
plot(gdmax4, pages = 1, all.terms = TRUE, se = TRUE)

par(mfrow = c(2,2))
gam.check(gdmax4)

```

GAM for monthly max
Best Model: maxTemp ~ Region * WY + Region * Month + Habitat Type
```{r Models Max Monthly Temp}
tempMon$WY <- as.numeric(tempMon$WY)
tempMon <- filter(tempMon, WY > 2000 & WY < 2020)
tempMonM <- left_join(tempMon, nMon) %>%
  filter(nMon == 12)

tempMonM$WY <- ordered(tempMonM$WY)

gmmax4 =  bam(maxTemp~s(Month, bs = "cc") + Region + HabitatType + WY,
          data =tempMonM, method = "REML")
summary(gmmax4)
plot(gmmax4, pages = 1, all.terms = TRUE, se = TRUE)

par(mfrow = c(2,2))
gam.check(gmmax4)
```

GAM for monthly mean
Best Model: maxTemp ~ Region * WY + Region * Month + Habitat Type
```{r Models Max Monthly Temp}
gmmean4 =  bam(meanTemp~s(Month, bs = "cc") + Region + HabitatType + WY,
          data =tempMonM, method = "REML")
summary(gmmean4)
plot(gmmean4, pages = 1, all.terms = TRUE, se = TRUE)

par(mfrow = c(2,2))
gam.check(gmmean4)
```

Number of days at each stress level
```{r}
# Calculate number of samples in a year or water year
heatDaysSamp <- heat %>%
  group_by(Region, Station, HabitatType, WY) %>%
  summarize(totalDays = n()) %>%
  filter(totalDays > 250)

# Calculate number of days and proportion of days at each stress level
heatDays <- heat %>%
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Stress) %>%
  summarize(nDays = n()) %>%
  left_join(heatDaysSamp) %>%
  mutate(propDays = round(nDays/totalDays,3)) %>%
  ungroup()

```


High heat stress
Remove Far North and WY < 2000
```{r}
# Count number of days at high heat
HighHeat <- heatDays %>%
  filter(Stress == "High",
         Region != "Far North",
         WY > 2009 & WY < 2020)

HighHeat$WY <- ordered(HighHeat$WY)
#  complete(WY, nesting(Station, Region, HabitatType), fill = list(nDays = 0))

summary(HighHeat)
```

#### Models {.tabset}
Best model: heat2 <- glm(propDays ~ Region + WYType2_Sac, family = "binomial", data = HighHeat)) BUT nothing is significant! 
Questions:
* Why does binomial result in no significance? 
* nDays vs propDays

```{r heatmodels}
library(nlme)
HighHeat$WY <- ordered(HighHeat$WY)
HighHeat$Region <- factor(HighHeat$Region)
HighHeat$WYType2_Sac <- factor(HighHeat$WYType2_Sac)
HighHeat$HabitatType <- factor(HighHeat$HabitatType)

# Model
# Model 1
heat1 <- glm(nDays ~ HabitatType + Region * WYType2_Sac,  data = HighHeat)
summary(heat1)

par(mfrow = c(2,2))
plot(heat1)
E = resid(heat1)
plot(HighHeat$Region, E)
plot(HighHeat$WYType2_Sac, E)
plot(HighHeat$HabitatType, E)

visreg(heat1, "WYType2_Sac", by = "Region")

summary(heat1 <- glm(propDays ~ Region + WYType2_Sac + HabitatType, family = "binomial", data = HighHeat))

summary(heat2 <- glm(propDays ~ Region + WYType2_Sac, family = "binomial", data = HighHeat))

summary(heat3 <- glm(propDays ~ Region * WYType2_Sac, family = "binomial", data = HighHeat))

(heat4 <- glm(propDays ~ Region + WY + HabitatType, family = "binomial", data = HighHeat))

(heat5 <- glm(propDays ~ Region + WY, family = "binomial", data = HighHeat))

(heat6 <- glm(propDays ~ Region * WY, family = "binomial", data = HighHeat))

AIC(heat1, heat2, heat3, heat4, heat5, heat6)

par(mfrow = c(2,2))
plot(heat2)
visreg(heat2)
visreg(heat2, "Region", by = "WYType2_Sac")
visreg(heat2, "WYType2_Sac", by = "Region")
```

### High stress days no recovery {.tabset}
#### Heatmap
```{r no recovery}
heatNoRecovery <-  heat  %>%
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c, StressAllDay) %>%
  summarize(NoRecovery = n())

heatNoRecoverySum <- filter(heatNoRecovery,
                 StressAllDay == "Y") 
hotSta <- unique(heatNoRecoverySum$Station)
hmapNoRecov <- ggplot(heatNoRecoverySum, aes(x = WY, y = Station, fill = NoRecovery )) + geom_tile() +
  scale_fill_viridis(option = "cividis") + labs(title = "Number of unrecovered high stress days per year")
ggplotly(hmapNoRecov)

```

