---
title: "Diel Trends"
author: "Catarina Pien"
date: "10/23/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly) # interactive plots
library(pscl) # glm
library(visreg) # visualize model results
library(lattice)
library(lme4) # glmm
library(lmerTest) #glmm p values
```

Read in 
```{r}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")

#tempFilt <- readRDS("Data/tempFilt.rds") 
tempToUse <- readRDS("Data/temp10years_20200922.rds")
#tempAn <- readRDS("Data/tempAnnual.rds")
tempMon <- readRDS("Data/tempMonthly.rds")
tempDaily <- readRDS("Data/tempDaily.rds")
#tempHeat <- readRDS("Data/heatstressDaily.rds")
```

Code to make sure every month has data
```{r nMon}
# Filter to only data that has temps from every month so as not to skew the data that only has part of the year represented.
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

nMon$WY <- as.numeric(nMon$WY)
```

## Daily Range
```{r Models Daily Max}
tempDaily <- filter(tempDaily, WY > 2008 & WY < 2020)
tempDaily$yday = yday(tempDaily$Date)
tempDaily$Year = year(tempDaily$Date)
tempDaily$fYear = factor(tempDaily$Year)
tempDaily$fWY = factor(tempDaily$WY)
tempDaily$Month = month(tempDaily$Date)
tempDaily$fMonth = ordered(tempDaily$Month)
tempDailyM <- left_join(tempDaily, nMon) %>%
  filter(nMon == 12)

tempDaily$WYType2_Sac = as.factor(tempDaily$WYType2_Sac)
tempToUse$Hour <- hour(tempToUse$Datetime)

#try a sine-transformation on "month" so we can include it in linear models
tempDailyM$syday = sin(pi*tempDailyM$yday/365)

# Add season
tempToUse <- tempToUse %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempToUse$Season <- factor(tempToUse$Season, levels = c("Spring", "Summer", "Fall", "Winter"))


# Add season
tempDailyM <- tempDailyM %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempDailyM$Season <- factor(tempDailyM$Season, levels = c("Spring", "Summer", "Fall", "Winter"))
```

**Scientific Questions**  

1. What is the approximate daily range? 
2. How does range change on annual scale? 
3. Does the range differ by region (taking into account month)?
4. Does the range differ at particular stations in a region? 

### Trends

What does temperature look like overall by hour?
```{r }
# Overall temperature trends by Month and Region 
temp_s <- tempToUse %>% group_by(Region) %>% sample_frac(.1)
ggplot(temp_s, aes(x = factor(Hour), y = Temp)) + geom_boxplot() + facet_grid(Region~Season)+theme_bw()
```

Table of Ranges by Region, Season, Month
```{r}
summaryRange <- tempDailyM %>%
  group_by(Region, Season, fMonth) %>%
  summarize(mean.Range = mean(rangeTemp),
            median.Range = median(rangeTemp),
            n = n(),
            sd = sd(rangeTemp),
            se = sd(rangeTemp)/sqrt(n))
```

**Greatest range in the summer (June-July) in South and Suisun Marsh**

```{r}
# Range by season (mean + se)
ggplot(summaryRange) + geom_col(aes(Region, mean.Range, fill = Season), size = 3, position= position_dodge()) + scale_fill_viridis(discrete = TRUE) +  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14),
axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

#####THIS ONE#####
# Range by month (mean + se)
ggplot(data = summaryRange, aes(x = fMonth, y = mean.Range, group = Region, color = Region)) + 
  geom_point(size = 3) +
  geom_line()+
  geom_errorbar(aes(ymin = mean.Range-se, ymax = mean.Range+se), width = 0.5, position = position_dodge(0.05))+ 
  scale_color_viridis(discrete = TRUE) +   theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))


# Region by Season boxplot
ggplot(tempDailyM_2, aes(x = Region, y = meanRange, fill = Season)) +   geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

Monthly Median of Daily Range
```{r}
tempDailyM_2 <- tempDailyM %>%
  group_by(Region, Station, Season, WYType2_Sac ,fWY, WY, fMonth) %>%
  summarize(medianRange = median(rangeTemp),
            meanRange = mean(rangeTemp)) %>%
  ungroup()
```

By Water Year Type

**Highest ranges during dry years in the summer**
```{r include = FALSE}
ggplot(tempDailyM_2, aes(x = fMonth, y = medianRange, fill = WYType2_Sac)) +   geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))

ggplot(tempDailyM_2, aes(x = fMonth, y = medianRange, color = WYType2_Sac)) +   geom_jitter() +
   scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

Monthly Patterns
**Summer>Spring>Fall>Winter**
**Suisun Marsh > South > San Joaquin**
```{r include=FALSE}
ggplot(tempDailyM_2, aes(x = Region, y = meanRange, fill = Season)) +   geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))

ggplot(tempDailyM_2, aes(x = fMonth, y = meanRange, fill = Region)) +   geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

**Median Range: Approximately 0.25 - 1.5C**  
**Larger range values and variability in the South**

## 2. How does range change on annual scale?

**Overall little change**

### Plots by Date
```{r}
tempDailyM_s <- tempDailyM %>% group_by(Region) %>% sample_frac(.2)

# Fraction of data by year
ggplot(tempDailyM_s, aes(x = Date, y = rangeTemp)) + geom_jitter(alpha = 0.2) + geom_smooth(se = TRUE) + theme_bw()

# By WY Type
ggplot(tempDailyM_s, aes(x = Date, y = rangeTemp, color = WYType2_Sac)) + geom_jitter() + theme_bw()

tempDailyM_3 <- tempDailyM %>%
  group_by(Region, fWY) %>%
  summarize(meanRange = mean(rangeTemp),
            medianRange = median(rangeTemp))

tempDailyM_4 <- tempDailyM %>%
  group_by(Region, fWY, Season) %>%
  summarize(meanRange = mean(rangeTemp),
            medianRange = median(rangeTemp))

tempDailyM_5 <- tempDailyM %>%
  group_by(Region, fWY, fMonth) %>%
  summarize(meanRange = mean(rangeTemp),
            medianRange = median(rangeTemp)) %>%
  filter(fMonth %in% c(5,6,7,8,9))
```

### Mean range by year and region
```{r}
#####THIS ONE#####
ggplot(tempDailyM_3, aes(x = fWY, y = meanRange, group = Region, color = Region)) + geom_point(size = 3) + geom_line() + scale_color_viridis(discrete = TRUE, option = "viridis")  +   theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14),
axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

* Very erratic in the South
* Relatively stable in Sac River, Suisun Bay, San Joaquin
* Possible slight increase in summer in San Joaquin
```{r}
ggplot(tempDailyM_4, aes(x = fWY, y = meanRange, group = Season, color = Season)) + facet_wrap(~Region) + geom_point(size = 3) + geom_line() + scale_color_viridis(discrete = TRUE, option = "viridis") +theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

* Some more evidence for change by year in the summer in San Joaquin
```{r}
ggplot(tempDailyM_5, aes(x = fWY, y = meanRange, group = fMonth, color = fMonth)) + facet_wrap(~Region) + geom_point(size = 3) + geom_line() + scale_color_viridis(discrete = TRUE, option = "viridis") +theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## 3. Does the range differ by region?

* Greatest ranges: Suisun Marsh spring, South Summer
* Region: High ranges and variability of range in Suisun Marsh, South
* Season: Range generally greater in the late spring, summer
* WY Type: Range generally slightly smaller in wet years

```{r}
ggplot(tempDailyM_s, aes(x = Region, y = rangeTemp, fill = Region)) + geom_violin() + theme_bw()

ggplot(tempDailyM_2, aes(x = fWY, y = meanRange, fill = Region)) + geom_boxplot() + scale_fill_viridis(discrete=TRUE) + theme_classic()

ggplot(tempDailyM_2, aes(x = fMonth, y = medianRange, fill = WYType2_Sac)) + facet_wrap(~Region, scales = "free_y") +  geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

By Region
```{r include = FALSE}
ggplot(tempDailyM_2, aes(x = fMonth, y = medianRange, fill = Region)) +   geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))

ggplot(tempDailyM_2, aes(x = fMonth, y = medianRange, color = Region)) +   geom_jitter() +
   scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))

ggplot(tempDailyM_2, aes(x = Season, y = medianRange, color = Region)) +   geom_jitter() +
   scale_color_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

## 4. Does the range differ at particular stations in a region?

Curious about those with large median ranges
```{r}
#####THIS ONE#####
highRange <- filter(tempDailyM_2, medianRange > 3)
ggplot(highRange, aes(x = fWY, y = medianRange, color = Station, shape = Region)) + geom_jitter(size = 4)+scale_color_viridis(option = "viridis", discrete = TRUE) +
  facet_wrap(~Season) +
  theme_bw() + 
  theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14),
        strip.text = element_text(size = 14))
```
    
    Large ranges in particular in the South, mostly in Spring and especially summer. Stations VER, SJR, RPN have very high ranges. 
    
**Suisun**
High range and range variability in BLL and SNC
```{r}
tempSuisun <- tempDailyM %>% filter(Region == "Suisun Marsh")

ggplot(tempSuisun, aes(x= fMonth, y = rangeTemp, fill = Station)) + geom_boxplot() +
  labs(title = "Suisun Marsh") + 
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

**South**

High range and range variability in UNI and VER 
```{r}
tempSouth <- tempDailyM %>% filter(Region == "South")

ggplot(tempSouth, aes(x= fMonth, y = rangeTemp, fill = Station)) + geom_boxplot() +
  labs(title = "South") +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

**San Joaquin**

* Not as much variation
* Summer CLC?
```{r}
tempSJ <- tempDailyM %>% filter(Region == "San Joaquin")

ggplot(tempSJ, aes(x= fMonth, y = rangeTemp, fill = Station)) + geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  labs(title = "San Joaquin") +
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```


## Modeling

* Main variables: WY, Region, yday, lag
* Random variables: Station, possibly WY
* Possible: WY Type

Interactions

* Region*yday: possible
```{r}
tempDaily_s <-sample_n(tempDailyM, 50000)
ggplot(tempDaily_s, aes(x = fWY, y = rangeTemp, color = Region)) + geom_point() +
  scale_color_viridis(discrete =TRUE)
  
ggplot(tempDaily_s, aes(x = fWY, y = rangeTemp, color = yday)) + geom_jitter() + scale_color_viridis()

# WYType:yday
# no trend
ggplot(tempDaily_s) + 
  geom_point(aes(x = yday, y = rangeTemp, color = WYType2_Sac), alpha = 0.5) + 
  stat_smooth(aes(x = yday, y = rangeTemp, color = WYType2_Sac),method = "lm", formula = y ~ x + I(x^2), size = 2, se = TRUE)+ 
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:yday
# Difference by Region (more differences in summer)
ggplot(tempDaily_s) + 
  geom_point(aes(x = yday, y = rangeTemp, color = Region), alpha = 0.2) + 
  stat_smooth(aes(x = yday, y = rangeTemp, color = Region),method = "lm", formula = y ~ x + I(x^2), size = 2, se = TRUE)+ 
  scale_color_viridis(option = "magma", discrete = TRUE) + theme_bw()

# Region:WY Type -not much difference
ggplot(tempDaily_s) + 
  geom_boxplot(aes(x = Region, y = rangeTemp, fill = WYType2_Sac)) + 
  scale_fill_viridis(option = "viridis", discrete = TRUE)

```

Models
Model temp autocorrelation

```{r}
# Account for Temporal Autocorrelation 
tempDailyM <- tempDailyM %>% 
    group_by(Region, Station) %>%
  mutate(rangeDailylag1 = lag(rangeTemp, 1),
         rangeDailylag2 = lag(rangeTemp, 2))%>%
  ungroup() %>%
  mutate(rangeDailylag1_s = scale(rangeDailylag1),
         rangeDailylag2_s = scale(rangeDailylag2),
         yday_s = scale(yday))

# Remove NAs from lag 
tempDaily2 <-na.omit(tempDailyM)

# Model no lag, lag(1)
summary(M.range1 <- lmer(rangeTemp~yday + I(yday_s^2) + Region + fWY + (1|Station), data = tempDaily2, na.action = na.omit))

M.range2 <- lmer(rangeTemp~ yday + I(yday_s^2) + Region + fWY + rangeDailylag1_s + (1|Station), data = tempDaily2, na.action = na.omit)

M.range3 <- lmer(rangeTemp~ yday_s + I(yday_s^2) + Region + fWY + rangeDailylag1_s + rangeDailylag2_s + (1|Station), data = tempDaily2, na.action = na.omit)

# Check temporal autocorrelation
# How correlated day 1 is to day 2, 3, etc. 
acf(residuals(M.range1))
acf(residuals(M.range2))
acf(residuals(M.range3))


```

**Chosen but not best model: M.range2 <- lmer(rangeTemp~yday + I(yday_s^2) + Region + fWY + rangeDailylag1_s + (1|Station)**
Year as random variable is slightly better but we care about year for now

Other models:
```{r}
# no WY Type
summary(M.range4 <- lmer(rangeTemp~Season + Region + fWY + rangeDailylag1_s + (1|Station), data = tempDaily2, na.action = na.omit))

summary(M.range5 <- lmer(rangeTemp~syday + Region + fWY + rangeDailylag1_s + (1|Station), data = tempDaily2, na.action = na.omit))

AIC(M.range3, M.range4, M.range5)
```

Best model still Model 3. 

# Add Interactions into model 3.
```{r}
summary(M.range6 <- lmer(rangeTemp~ yday_s + I(yday_s^2) + Region + fWY + rangeDailylag1_s + rangeDailylag2_s + yday_s:Region + (1|Station), data = tempDailyM, na.action = na.omit))

summary(M.range7 <- lmer(rangeTemp~ yday_s + I(yday_s^2) + Region + fWY + rangeDailylag1_s + rangeDailylag2_s + fWY:Region + (1|Station), data = tempDailyM, na.action = na.omit))

summary(M.range8 <- lmer(rangeTemp~ yday_s + I(yday_s^2) + Region + fWY + rangeDailylag1_s + rangeDailylag2_s + fWY:yday_s + (1|Station), data = tempDailyM, na.action = na.omit))

AIC(M.range3, M.range6, M.range7, M.range8)
```

**Best modeL : M.range7 <- lmer(rangeTemp~ yday_s + I(yday_s^2) + Region + fWY + rangeDailylag1_s + rangeDailylag2_s + fWY:Region + (1|Station)**

fWY:Region interaction helps

Diagnostic Plots

```{r}
# Diagnostic Plots
# https://www.ssc.wisc.edu/sscc/pubs/MM/MM_DiagInfer.html
# What is the right diagnostic plot for lmer?
par(mfrow = c(2,3))

res.range = resid(M.range7, type = "pearson")
lev1a = hatvalues(M.range7)
plot(M.range7)
qqnorm(res.range)
qqline(res.range)
plot(lev1a, y = res.range)

plot(res.range)
plot(tempDaily2$yday^2, res.range)
plot(tempDaily2$Region, res.range)
plot(tempDaily2$fWY, res.range)

visreg(M.range7, "fWY", by = "Region")
visreg(M.range7, "Region", by = "yday")
```


### Conclusions
* Summer higher ranges
* South, Suisun Marsh higher ranges
* South: 2011, 2015, 2017 higher ranges
* Sac River: 2017, 2019 higher
* No years alone are significant but 2013-2015 higher, rest lower





## What are the hourly patterns? 
# Hourly information
* Max temp ~ 16:00
* Min temp ~ 7:00
* Diel: 14-18 vs 5-9

```{r}
tempToUse$Hour <- hour(tempToUse$Datetime)
tempToUse$Month <- month(tempToUse$Datetime)
tempInfo <- left_join(tempToUse, tempDaily) 
tempMax <- tempInfo %>%
  filter(Temp == maxDaily)
tempMin <- tempInfo %>%
  filter(Temp == minDaily)

# When do min and max temps occur for each Region?
tempMaxInfo <- tempMax %>%
  group_by(Region, Month) %>%
  summarize(HourMax = median(Hour))
tempMinInfo <- tempMin %>%
  group_by(Region, Month) %>%
  summarize(HourMin = median(Hour))

# Plots
tempMax_s <- tempMax %>% group_by(Region) %>% sample_frac(.5) %>% ungroup()
ggplot(tempMax_s, aes(x = fMonth, y = Hour)) + geom_boxplot() + facet_wrap(~Region) + scale_fill_viridis() + theme_bw()

tempMin_s <- tempMin %>% group_by(Region) %>% sample_frac(.5)
ggplot(tempMin_s, aes(x = factor(Month), y = Hour)) + geom_boxplot() + facet_wrap(~Region) + theme_bw()
```

* Filter for just those hours. 
* Add variable TOD = Max vs Min

```{r}
tempHours <- tempInfo %>%
  filter(Hour %in% c(14,15,16,17,5,6,7,8)) %>%
  mutate(TOD = ifelse(Hour %in% c(14,15,16,17), "Max", "Min"))
```

```{r}
tempHours_sub <- filter(tempHours, fWY == "2012")
ydayseason <- tempHours %>%
  select(Season, yDay) %>%
  group_by(Season) %>%
  summarize(max = max(yDay),
            min = min(yDay))

# Testing the plot
ggplot(tempHours_sub, aes(Date, Temp, color = TOD)) + geom_point() + facet_wrap(~Region) + scale_color_viridis(discrete=TRUE) + theme_bw()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Making rectangles for seasons
rects <- data.frame(xstart = c(0, 60,152, 244, 335), xend = c(60,152,244, 335, 366), col = c("Winter", "Spring", "Summer", "Fall","Winter"))
```

North Delta
```{r}

tempHours_ND <- filter(tempHours, Region == "North Delta")
tempHours_ND_sum <- tempHours_ND %>%
  group_by(Region, Station, fWY, Season, Date, TOD) %>%
  summarize(meanTemp = mean(Temp))
tempHours_BKS <- tempHours_ND %>% filter(Station == "BKS")
tempHours_ND_sum2 <- tempHours_ND %>%
  group_by(Region, Station, WYType2_Sac,yDay, TOD) %>%
  summarize(meanTemp = mean(Temp))


# North Delta Max and min
ggplot(tempHours_ND_sum, aes(x = fWY, y = meanTemp, fill = TOD)) + geom_boxplot(position = position_dodge()) + facet_wrap(~Season) +
  scale_fill_viridis(discrete=TRUE) + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# North Delta yday by WY Type (Temp max and min averaged per day)
ggplot() + 
  geom_rect(data = rects, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf, fill = col), alpha = 0.3) + 
  geom_point(data =tempHours_ND, aes(yday, Temp, color = TOD)) + facet_wrap(~WYType2_Sac) + scale_color_viridis(discrete=TRUE) +
  geom_hline(yintercept = 22, color = "black") +  
  geom_hline(yintercept = 25, color = "red") +
theme_bw()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# North Delta yday by WYType (Temp averaged over WYType)
ggplot(tempHours_ND_sum2, aes(x = yDay, y = meanTemp, color = TOD, shape = Station)) + geom_point() + facet_grid(WYType2_Sac~.) + scale_color_viridis(discrete=TRUE) +
    geom_line(y = 22, color = "black") +  
  geom_line(y = 25, color = "red") +theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# BKS
ggplot(tempHours_BKS, aes(Date, Temp, color = TOD)) + geom_point() +  scale_color_viridis(discrete=TRUE) + 
    geom_line(y = 22, color = "black") +  
  geom_line(y = 25, color = "red") +theme_bw()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Sac River
```{r}
tempHours_Sac <- filter(tempHours, Region == "Sac River")
tempHours_Sac_sum <- tempHours_Sac %>%
  group_by(Region, Station, fWY, Season, Date, TOD) %>%
  summarize(meanTemp = mean(Temp))
tempHours_Sac_sum2 <- tempHours_Sac %>%
  group_by(Region, Station, WYType2_Sac,yday, TOD) %>%
  summarize(meanTemp = mean(Temp))

# Sac River Max min
ggplot(tempHours_Sac_sum, aes(x = fWY, y = meanTemp, fill = TOD)) + geom_boxplot(position = position_dodge()) + facet_wrap(~Season) +
  scale_fill_viridis(discrete=TRUE) + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Sac River yday by WY Type (Temp for each day)
ggplot(tempHours_Sac, aes(yday, Temp, color = TOD)) + geom_point() + facet_wrap(~WYType2_Sac) + scale_color_viridis(discrete=TRUE) +
  geom_line(y = 22, color = "black") +  
  geom_line(y = 25, color = "red") +
theme_bw()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Sac River yday by WYType (temp averaged by WYType)
ggplot(tempHours_Sac_sum2, aes(x = yday, y = meanTemp, color = TOD, shape = Station)) + geom_point() + facet_grid(WYType2_Sac~.) + scale_color_viridis(discrete=TRUE) +
    geom_line(y = 22, color = "black") +  
  geom_line(y = 25, color = "red") +theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```









# Calculate 10 year average of max temp by by season and station
# Calculate 10 year average of min monthly by season and station
# Number of hours >= max
# Number of hours <= min


nHours 