---
title: "Diel Trends"
author: "Catarina Pien"
date: "10/23/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly) # interactive plots
library(pscl) # glm
library(visreg) # visualize model results
library(lattice)
library(lme4) # glmm
library(lmerTest) #glmm p values
```

Read in 
```{r}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")

#tempFilt <- readRDS("Data/tempFilt.rds") 
tempToUse <- readRDS("Data/temp10years_20200922.rds")
#tempAn <- readRDS("Data/tempAnnual.rds")
tempMon <- readRDS("Data/tempMonthly.rds")
tempDaily <- readRDS("Data/tempDaily.rds")
#tempHeat <- readRDS("Data/heatstressDaily.rds")
```

Code to make sure every month has data
```{r nMon}
# Filter to only data that has temps from every month so as not to skew the data that only has part of the year represented.
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

nMon$WY <- as.numeric(nMon$WY)
```

## Daily Range
```{r Models Daily Max}
tempDaily <- filter(tempDaily, WY > 2008 & WY < 2020)
tempDaily$yday = yday(tempDaily$Date)
tempDaily$Year = year(tempDaily$Date)
tempDaily$fYear = ordered(tempDaily$Year)
tempDaily$fWY = ordered(tempDaily$WY)
tempDaily$Month = month(tempDaily$Date)
tempDaily$fMonth = ordered(tempDaily$Month)
tempDailyM <- left_join(tempDaily, nMon) %>%
  filter(nMon == 12)

tempDaily$WYType2_Sac = as.factor(tempDaily$WYType2_Sac)
tempToUse$Hour <- hour(tempToUse$Datetime)
# Add season
tempToUse <- tempToUse %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempToUse$Season <- factor(tempToUse$Season, levels = c("Spring", "Summer", "Fall", "Winter"))


# Add season
tempDailyM <- tempDailyM %>%
  mutate(Season = ifelse(Month %in% c(12, 1, 2), "Winter", 
                         ifelse(Month %in% c(3,4,5), "Spring", 
                                ifelse(Month %in% c(6,7,8), "Summer",
                                       "Fall"))))
tempDailyM$Season <- factor(tempDailyM$Season, levels = c("Spring", "Summer", "Fall", "Winter"))
```

**Scientific Questions**  

1. What is the approximate daily range? 
2. How does range change on annual scale? 
3. Does the range differ by region?
4. Does the range differ at particular stations in a region? 

```{r }
# Overall trends by Month and Region 
temp_s <- tempToUse %>% group_by(Region) %>% sample_frac(.1)
ggplot(temp_s, aes(x = factor(Hour), y = Temp)) + geom_boxplot() + facet_grid(Region~Season)+theme_bw()
```

Median Daily Range
```{r}
tempDailyM_2 <- tempDailyM %>%
  group_by(Region, Station, Season, WYType2_Sac ,fWY, WY, fMonth) %>%
  summarize(medianRange = median(rangeTemp),
            meanRange = mean(rangeTemp)) %>%
  ungroup()

ggplot(tempDailyM_2, aes(x = fMonth, y = medianRange, fill = WYType2_Sac)) +   geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

**Median Range: Approximately 0.25 - 1.5C**

Curious about those with large median ranges
```{r}
highRange <- filter(tempDailyM_2, medianRange > 3)
ggplot(highRange, aes(x = fWY, y = medianRange, color = Station, shape = Region)) + geom_jitter(size = 4)+scale_color_viridis(option = "viridis", discrete = TRUE) +
  facet_wrap(~Season) +
  theme_bw() + 
  theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14),
        strip.text = element_text(size = 14))
```
    
    Large ranges in San Joaquin, South, Suisun Marsh mostly in Spring and especially summer.
    

## 2. How does range change on annual scale?

* Doesn't really appear to change over time, or at least not in a consistent way
```{r}
tempDailyM_s <- tempDailyM %>% group_by(Region) %>% sample_frac(.5)

ggplot(tempDailyM_s, aes(x = Date, y = rangeTemp)) + geom_jitter() + geom_smooth(se = TRUE)

```

## 3. Does the range differ by region?

* Greater in Suisun Marsh spring, South
* High variability in Suisun Marsh
* Range generally greater in the late spring, summer
* Range generally slightly smaller in wet years
```{r}
ggplot(tempDailyM_s, aes(x = Date, y = rangeTemp, color = Region)) + geom_smooth()

ggplot(tempDailyM_2, aes(x = fWY, y = meanRange, fill = Region)) + geom_boxplot()

ggplot(tempDailyM_2, aes(x = fMonth, y = medianRange, fill = WYType2_Sac)) + facet_wrap(~Region, scales = "free_y") +  geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

## 4. Does the range differ at particular stations in a region?

**Suisun**
High range and range variability in BLL and SNC
```{r}
tempSuisun <- tempDailyM %>% filter(Region == "Suisun Marsh")

ggplot(tempSuisun, aes(x= fMonth, y = rangeTemp, fill = Station)) + geom_boxplot() +
  labs(title = "Suisun Marsh") + 
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

**South**

High range and range variability in UNI and Vernalis 
```{r}
tempSouth <- tempDailyM %>% filter(Region == "South")

ggplot(tempSouth, aes(x= fMonth, y = rangeTemp, fill = Station)) + geom_boxplot() +
  labs(title = "South") +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```

**San Joaquin**

* Not much variation
```{r}
tempSJ <- tempDailyM %>% filter(Region == "San Joaquin")

ggplot(tempSJ, aes(x= fMonth, y = rangeTemp, fill = Station)) + geom_boxplot() +
   scale_fill_viridis(option = "viridis", discrete = TRUE) + 
  labs(title = "San Joaquin") +
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
```


## Modeling

* Main variables: WY, Region, yday, lag
* Random variables: Station, possibly WY
* Possible: WY Type

```{r}
library(lme4)
library(lmerTest)

# Account for Temporal Autocorrelation 
tempDailyM <- tempDailyM %>% 
    group_by(Region, Station) %>%
  mutate(rangeDailylag1 = lag(rangeTemp, 1),
         rangeDailylag2 = lag(rangeTemp, 2))%>%
  ungroup() %>%
  mutate(rangeDailylag1_s = scale(rangeDailylag1),
         yday_s = scale(yday))

# Model no lag, lag(1)
summary(M.range1 <- lmer(rangeTemp~I(yday_s^2) + Region + Year + WYType2_Sac + (1|Station), data = tempDailyM, na.action = na.omit))

M.range2 <- lmer(rangeTemp~I(yday_s^2) + Region + Year + WYType2_Sac + rangeDailylag1_s + (1|Station), data = tempDailyM, na.action = na.omit)

# Check temporal autocorrelation
# How correlated day 1 is to day 2, 3, etc. 
acf(residuals(M.range1))
acf(residuals(M.range2))


```


**Chosen but not best model: M.range2 <- lmer(rangeTemp~I(yday_s^2) + Region + Year + WYType2_Sac + rangeDailylag1_s + (1|Station)**
Year as random variable is slightly better but we care about year for now
```{r}
summary(M.range2 <- lmer(rangeTemp~I(yday_s^2) + Region + Year + WYType2_Sac + rangeDailylag1_s + (1|Station), data = tempDailyM, na.action = na.omit))
```

Other models:
```{r}
# no WY Type
summary(M.range3 <- lmer(rangeTemp~I(yday_s^2) + Region + Year + rangeDailylag1_s + (1|Station), data = tempDailyM, na.action = na.omit))

# Year as random variable
summary(M.range4 <- lmer(rangeTemp~I(yday_s^2) + rangeDailylag1_s + Region + WYType2_Sac + (1|Year) + (1|Station), data = tempDailyM, na.action = na.omit))

# Year as factor
summary(M.range5 <- lmer(rangeTemp~I(yday_s^2) + rangeDailylag1_s + Region + fYear + WYType2_Sac + (1|Station), data = tempDailyM, na.action = na.omit))

AIC(M.range2, M.range3, M.range4, M.range5)

# Diagnostic Plots
# https://www.ssc.wisc.edu/sscc/pubs/MM/MM_DiagInfer.html
# What is the right diagnostic plot for lmer?
par(mfrow = c(2,2))
visreg(M.range2)

# Residuals vs fitted
plot(M.range2)
# Normality of residuals
qqnorm(resid(M.range2))
# significant but small diff ~0.03 degC

### Basic plot mean, max, min temp by region, WY
```

Interactions

* Region*yday
* WYType2_Sac*Month/yday
* Region*WYType2_Sac

* lower max temps in Suisun Bay
```{r}
tempDaily_s <-sample_n(tempDailyM, 50000)
ggplot(tempDaily_s, aes(x = yday, y = rangeTemp, color = WYType2_Sac)) + geom_point() + scale_color_viridis(discrete = TRUE)

# WYType:yday
# no trend
ggplot(tempDaily_s) + 
  geom_point(aes(x = yday, y = rangeTemp, color = WYType2_Sac), alpha = 0.2) + 
  stat_smooth(aes(x = yday, y = rangeTemp, color = WYType2_Sac),method = "lm", formula = y ~ x + I(x^2), size = 2, se = TRUE)+ 
  scale_color_viridis(option = "viridis", discrete = TRUE) + theme_bw()

# Region:yday
# Difference by Region (more differences in summer)
ggplot(tempDaily_s) + 
  geom_point(aes(x = yday, y = rangeTemp, color = Region), alpha = 0.2) + 
  stat_smooth(aes(x = yday, y = rangeTemp, color = Region),method = "lm", formula = y ~ x + I(x^2), size = 2, se = TRUE)+ 
  scale_color_viridis(option = "magma", discrete = TRUE) + theme_bw()

# Region:WY Type -not much difference
ggplot(tempDaily_s) + 
  geom_boxplot(aes(x = Region, y = rangeTemp, fill = WYType2_Sac)) + 
  scale_fill_viridis(option = "viridis", discrete = TRUE)

```

# Add Interactions into model
```{r}
summary(M.range6 <- lmer(maxDaily~I(yday_s^2) + rangeDailylag1_s + Region + Year + (1|Station) + WYType2_Sac + yday:Region, data = tempDailyM, na.action = na.omit))

# Diagnostics
# How should I plot this?
# Next time - work on this interpretation
visreg(M.range6, "yday", by = "Region")
visreg(M.range6, "yday", by = "WYType2_Sac")
par(mfrow = c(2,2))
plot(M.range6)
qqnorm(resid(M.range6)) # This looks weird
```








## What are the hourly patterns? 
# Hourly information
* Max temp ~ 16:00
* Min temp ~ 7:00
* Diel: 14-18 vs 5-9


```{r}
tempToUse$Hour <- hour(tempToUse$Datetime)
tempToUse$Month <- month(tempToUse$Datetime)
tempInfo <- left_join(tempToUse, tempDaily) 
tempMax <- tempInfo %>%
  filter(Temp == maxDaily)
tempMin <- tempInfo %>%
  filter(Temp == minDaily)

# When do min and max temps occur for each Region?
tempMaxInfo <- tempMax %>%
  group_by(Region, Month) %>%
  summarize(HourMax = median(Hour))
tempMinInfo <- tempMin %>%
  group_by(Region, Month) %>%
  summarize(HourMin = median(Hour))

# Plots
tempMax_s <- tempMax %>% group_by(Region) %>% sample_frac(.5)
ggplot(tempMax_s, aes(x = factor(Month), y = Hour)) + geom_boxplot() + facet_wrap(~Region)

tempMin_s <- tempMin %>% group_by(Region) %>% sample_frac(.5)
ggplot(tempMin_s, aes(x = factor(Month), y = Hour)) + geom_boxplot() + facet_wrap(~Region)


# 
# Summer_hour <- temp_s %>% filter(Month %in% c(5,6,7,8,9)) 
# Winter_hour <- temp_s %>% filter(Month %in% c(10,11,12,1,2,3,4))

```

* Filter for just those hours. 
* Add variable TOD = Early vs Late
* Run model with TOD as variable 