---
title: "DaysExceedance"
author: "Catarina Pien"
date: "9/8/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Days Exceedance
Last updated 6/19/2023 by C. Pien

Calculate days exceedance for temperature suitability based on tolerance and optimum temperatures in species table

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(ggpubr)
library(grid)
library(gridExtra)
library(readxl)
library(viridis)
library(here)
```

## Import data
- These datasets were created in TempHeatStress.Rmd based off tempDaily.rds
```{r}
tempToUse <- readRDS(here::here("manuscript_code", "Data", "temp10years_20230613.rds"))
tempDaily <- readRDS(here::here("manuscript_code","Data", "tempDaily.rds"))
thresholds <- readxl::read_excel(here::here("manuscript_code", "Data","SpeciesThresholds.xlsx")) %>%
  mutate(across(c(Suboptimum:Max_Field_Temp), na_if, "NA"))
 
species0b <- readr::read_csv(here::here("manuscript_code","Data", "fish", "exportfishabsence_presence.csv")) 
species0 <- readr::read_csv(here::here("manuscript_code","Data","fish", "absence_presence_temp.csv")) %>%
  filter(Species %in% c("Giant Reed EAV", "Brazilian Waterweed", "Water Hyacinth FAV", "Microcystis", "Asian Clam", "Overbite Clam"))
species <- rbind(species0, species0b)
```

## Manipulate data
```{r}
tempRegions <- tempDaily %>%
  mutate(Region = case_when(Region == "San Joaquin"~ "Central",
                            Region == "Sac River"~ "Confluence",
                            TRUE~ Region))
```

Calculate the number of stations within each region
```{r}
nStations <- tempRegions %>%
  dplyr::select(Region,Station) %>%
  unique() %>%
  group_by(Region) %>%
  summarize(nStation = n())

tempRegions2 <- left_join(tempRegions, nStations) %>%
  mutate(Month = month(Date),
         Season = case_when(Month %in% c(1,2,3) ~ "Winter",
                            Month %in% c(4,5,6) ~ "Spring",
                            Month %in% c(7,8,9) ~ "Summer",
                            Month %in% c(10,11,12) ~ "Fall",
                            TRUE~as.character(NA)),
         SeasonRegion = paste0(Season, Region))
```

Reformat Species Table
```{r}
species1 <- species %>%
  mutate(Presence = "Yes") 

speciesComp <- complete(species1, nesting(Species, LifeStage), Region, Season, fill = list(Presence = "No")) %>%
  mutate(SeasonRegion = paste0(Season,Region))%>%
  mutate(LifeStage = ifelse(is.na(LifeStage), "Undifferentiated", LifeStage)) %>%
  left_join(thresholds, by = c("Species", "LifeStage")) 
```

Remove any group with no thresholds listed
```{r}
none <- speciesComp %>%
  dplyr::select(Species, LifeStage, Suboptimum, Tolerance) %>%
  distinct() %>%
  filter(is.na(Suboptimum) & is.na(Tolerance))

speciesComp <- filter(speciesComp, !(is.na(Suboptimum) & is.na(Tolerance)))
```

Add species_lifestage variable for easier filtering
```{r}
speciesComp$SpeciesLS = paste0(speciesComp$Species, "_", speciesComp$LifeStage)
SpeciesLS <- unique(speciesComp$SpeciesLS)
```

Define order of species ls
```{r}
level_order = c("Green Sturgeon", "White Sturgeon","Delta Smelt", "Longfin Smelt", "Wakasagi","Chinook Salmon", "Steelhead/Rainbow Trout","Sacramento Splittail", "Sacramento Pikeminnow", "Sacramento Sucker", "Sacramento Blackfish", "Hitch", "Tule Perch", "Threespine Stickleback", "Prickly Sculpin", "Mississippi Silverside", "Striped Bass", "Largemouth Bass", "Giant Reed EAV", "Brazilian Waterweed", "Water Hyacinth FAV", "Microcystis", "Asian Clam", "Overbite Clam")
```

## Boxplot Function for calculating days exceedance, no means or sums for boxplot
* Filter to regions selected
* For each station-day, compare max daily temp to inputted tolerance and optimum. If in exceedance, assign 1. If not, assign 0.
* For each date, calculate the average number of stations that exceeded tolerance. 
* If more than 30% of stations on a particular day exceeded tolerance or optimum, assign 1. 
* For each WY, sum up the number of days exceeding tolerance
# Add species name
```{r}
funDaysExceedBox <- function(specieslsinput) {
filternewdf <- speciesComp %>%
  filter(SpeciesLS == specieslsinput,
         Presence == "Yes") 

daysExceedance3 <- tempRegions2 %>%
  filter(SeasonRegion %in% filternewdf$SeasonRegion) %>%
  mutate(ExceedTol = ifelse(maxDaily > filternewdf$Tolerance[1], 1L, 0L),
         ExceedOpt = ifelse(maxDaily > filternewdf$Suboptimum[1], 1L, 0L)) %>%
  group_by(WY, Date, SeasonRegion) %>%
  summarize(maxDaily = maxDaily,
            propTol = mean(ExceedTol, na.rm = TRUE),
            propOpt = mean(ExceedOpt, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(WY, Date) %>%
  summarize(maxPropTol = max(propTol, na.rm = TRUE),
            maxPropOpt = max(propOpt, na.rm = TRUE),
            ExceedTol = ifelse(maxPropTol > 0.3, 1L, 0L),
            ExceedOpt = ifelse(maxPropOpt > 0.3, 1L, 0L)) %>%
  ungroup() %>%
  group_by(WY) %>%
  summarize(daysExceedanceTol = sum(ExceedTol, na.rm = TRUE),
              daysExceedanceOpt = sum(ExceedOpt, na.rm = TRUE)) %>%
  ungroup() %>%
    mutate(SpeciesLS = specieslsinput) %>%
  left_join(filternewdf) %>%
  dplyr::select(WY, Species, LifeStage, Tolerance,  daysExceedanceTol, daysExceedanceOpt, Suboptimum)%>%
  distinct() 
}
```
Run function - Takes a minute
```{r}
DaysExceedanceBox <- lapply(SpeciesLS, funDaysExceedBox)
```

Bind data together
```{r}
DaysExceedanceData0 <- bind_rows(DaysExceedanceBox) 

DaysExceedanceData <- DaysExceedanceData0 %>%
  dplyr::mutate(daysExceedanceOpt = replace(daysExceedanceOpt, is.na(Suboptimum), NA),
         daysExceedanceTol = replace(daysExceedanceTol, is.na(Tolerance), NA)) %>%
  dplyr::mutate(Species = factor(Species, levels = level_order))

# write_csv(DaysExceedanceData, "manuscript_code/Data/daysExceedanceDataForPlotting.csv")
```


## Plot Data

### Theme
```{r}
theme_plots <-
  theme_bw() +
   theme(axis.text.x = element_text(size = 11, angle = 70, vjust = 1, hjust = 1),
         axis.text.y = element_text(size = 11),
         axis.title.y = element_text(size = 11.5),
         legend.text = element_text(size = 11),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = "top",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

### Plot function
```{r}
f_threshold_plot <- function(df, var, max_y) {
  ggplot(df) + 
    geom_rect(xmin = 0, xmax = 1.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
    geom_rect(xmin = 2.5, xmax = 3.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
    geom_rect(xmin = 4.5, xmax = 5.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
    geom_rect(xmin = 6.5, xmax = 7.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
    geom_rect(xmin = 8.5, xmax = 9.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
    geom_rect(xmin = 10.5, xmax = 11.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
   geom_rect(xmin = 12.5, xmax = 13.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
   geom_rect(xmin = 14.5, xmax = 15.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
      geom_rect(xmin = 16.5, xmax = 17.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
      geom_rect(xmin = 18.5, xmax = 19.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
      geom_rect(xmin = 20.5, xmax = 21.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
      geom_rect(xmin = 22.5, xmax = 23.5, ymin = -Inf, ymax = Inf, fill = "gray85") +
   geom_vline(aes(xintercept = stage(Species, after_scale = 18.5)), linetype = "dashed", linewidth = 0.5, color = "orangered2") +
    geom_boxplot(aes_string(x = "Species",  y = var, fill = "LifeStage"), position = position_dodge(preserve = "single"), color = "gray50", size = 0.3) +
   annotate(geom = "text", x = 10, y = max_y, label = "Fish", vjust = 1, hjust = 0.5, size = 4) +
   annotate(geom = "text", x = 21.5, y = max_y, label = "Vegetation & Clams", vjust = 1, size = 4) +
    viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") + 
   scale_y_continuous(limits = c(0,max_y), breaks = seq(from = 0, to = max_y, by = 25)) +
   theme_plots
}
```

### Make plots for Lower Thresholds (this is what is used in the manuscript)
```{r}
DaysExceedanceData <- read_csv("manuscript_code/Data/daysExceedanceDataForPlotting.csv") %>%
  dplyr::mutate(Species = factor(Species, levels = level_order))

maxTol = max(DaysExceedanceData$daysExceedanceTol, na.rm = TRUE) +10
maxOpt = max(DaysExceedanceData$daysExceedanceOpt, na.rm = TRUE) +10
(FishTol1 <- f_threshold_plot(DaysExceedanceData, var = "daysExceedanceTol", max_y = maxTol) +
    labs( y = "Annual Days \nExceeding Tolerance") )
(FishOpt1 <- f_threshold_plot(DaysExceedanceData, var = "daysExceedanceOpt", max_y = maxOpt) +
    labs( y = "Annual Days \nExceeding Optimum") )
    
```

### Combined (Final Plot)
```{r}
# save legend separately for final figure
get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}
legend <- get_legend(FishTol1)
(FishOpt1_noleg <- FishOpt1 + theme(legend.position = "none",
                                    axis.text.x = element_blank()))
(FishTol1_noleg<- FishTol1 + theme(legend.position = "none") )

png(filename=file.path("manuscript_code/Figures/Figure_Opt_Tol.png"), units="in",type="cairo", bg="white", height=7.5, 
     width=8, res=300, pointsize=12)
ggarrange(legend, FishOpt1_noleg, FishTol1_noleg, ncol=1, nrow=3,
             heights = c(0.75,2.5,4), labels = c("", "A","B"))
dev.off()
```

Different scale bars
```{r}
legend2 <- get_legend(FishTol1b)
(FishOpt2_noleg <- FishOpt2 + theme(legend.position = "none") )
(FishTol1b_noleg<- FishTol1b + theme(legend.position = "none") )

png(filename=file.path("manuscript_code/Figures/Figure_Opt_Tol_scalesdiff.tiff"), units="in",type="cairo", bg="white", height=5.5, 
     width=6, res=300, pointsize=12,compression="lzw")
ggarrange(legend, FishOpt2_noleg, FishTol1b_noleg, ncol=1, nrow=3,
             heights = c(0.75,3,3.3), labels = c("", "A","B"))
dev.off()
```

## Upper values (this is what is in the supplemental)
```{r}
funDaysExceedBoxUpper <- function(specieslsinput) {
filternewdf <- speciesComp %>%
  filter(SpeciesLS == specieslsinput,
         Presence == "Yes") 

daysExceedance3 <- tempRegions2 %>%
  filter(SeasonRegion %in% filternewdf$SeasonRegion) %>%
  mutate(ExceedTol = ifelse(maxDaily > filternewdf$Tolerance_Upper[1], 1L, 0L),
         ExceedOpt = ifelse(maxDaily > filternewdf$Suboptimum_Upper[1], 1L, 0L)) %>%
  group_by(WY, Date, SeasonRegion) %>%
  summarize(maxDaily = maxDaily,
            propTol = mean(ExceedTol, na.rm = TRUE),
            propOpt = mean(ExceedOpt, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(WY, Date) %>%
  summarize(maxPropTol = max(propTol, na.rm = TRUE),
            maxPropOpt = max(propOpt, na.rm = TRUE),
            ExceedTol = ifelse(maxPropTol > 0.3, 1L, 0L),
            ExceedOpt = ifelse(maxPropOpt > 0.3, 1L, 0L)) %>%
  ungroup() %>%
  group_by(WY) %>%
  summarize(daysExceedanceTol = sum(ExceedTol, na.rm = TRUE),
              daysExceedanceOpt = sum(ExceedOpt, na.rm = TRUE)) %>%
  ungroup() %>%
    mutate(SpeciesLS = specieslsinput) %>%
  left_join(filternewdf) %>%
  dplyr::select(WY, Species, LifeStage, Tolerance_Upper,  daysExceedanceTol, daysExceedanceOpt, Suboptimum_Upper)%>%
  distinct() 
}
```

### Run code
```{r}
DaysExceedanceBoxUpper <- lapply(SpeciesLS, funDaysExceedBoxUpper)

DaysExceedanceDataUpper0 <- bind_rows(DaysExceedanceBoxUpper) %>% distinct() # Not sure why it's creating so many extra rows. For now just apply distinct. 

DaysExceedanceDataUpper <- DaysExceedanceDataUpper0 %>%
  dplyr::mutate(daysExceedanceOpt = replace(daysExceedanceOpt, is.na(Suboptimum_Upper), NA),
         daysExceedanceTol = replace(daysExceedanceTol, is.na(Tolerance_Upper), NA)) %>%
  dplyr::mutate(Species = factor(Species, levels = level_order))
```

### Start from here if just editing plot
```{r}
# write_csv(DaysExceedanceDataUpper, "manuscript_code/Data/daysExceedanceUpperDataForPlotting.csv")
DaysExceedanceDataUpper <- read_csv("manuscript_code/Data/daysExceedanceUpperDataForPlotting.csv")
fieldtemps <- read_csv("manuscript_code/Data/fish/surveymaxtemps.csv") %>%
  dplyr::select(Taxon = Taxa,
         LifeStage,
         q3, maxTemp)
lengths <- read_csv("publish_thresholds/thresholds_edi/data_objects/Lifestage_length_designations.csv") %>%
  rename(Species = Common_name,
         LifeStage = Assigned_life_stage) %>%
  dplyr::select(Species, LifeStage, Length_mm, Length_type)
```

### Table
```{r}
daysExceedanceSummary0 <- DaysExceedanceData %>%
  group_by(Species, LifeStage) %>%
  reframe(meanTolerance = ifelse(is.na(Tolerance), NA, round(mean(daysExceedanceTol, na.rm = TRUE),0)),
            minTolerance= ifelse(is.na(Tolerance), NA, min(daysExceedanceTol, na.rm = TRUE)),
            maxTolerance =  ifelse(is.na(Tolerance), NA, max(daysExceedanceTol, na.rm = TRUE)),
            meanSuboptimum = ifelse(is.na(Suboptimum), NA, round(mean(daysExceedanceOpt, na.rm = TRUE),0)),
            minSuboptimum= ifelse(is.na(Suboptimum), NA, min(daysExceedanceOpt, na.rm = TRUE)),
            maxSuboptimum =  ifelse(is.na(Suboptimum), NA, max(daysExceedanceOpt, na.rm = TRUE))) %>%
  mutate(outputTolerance = ifelse(is.na(meanTolerance), NA, paste0(meanTolerance, " (", minTolerance, "-", maxTolerance, ")")),
         outputSuboptimum = ifelse(is.na(meanSuboptimum), NA, paste0(meanSuboptimum, " (", minSuboptimum, "-", maxSuboptimum, ")"))) %>%
  distinct() %>%
  left_join(thresholds %>% dplyr::select(Species, LifeStage, Taxon, Suboptimum, Tolerance))

summary_all0 <- left_join(daysExceedanceSummary0, fieldtemps, by = c("Taxon", "LifeStage")) %>%
  left_join(lengths) %>%
 dplyr::select(Species, LifeStage,    
               `Lower Suboptimum Temperature Threshold (°C)` = Suboptimum, 
               `Lower Tolerance Temperature Threshold (°C)` = Tolerance, 
               outputSuboptimum, outputTolerance) %>%
  arrange(Species, LifeStage) 
```

```{r}
daysExceedanceSummary <- DaysExceedanceDataUpper %>%
  group_by(Species, LifeStage) %>%
  reframe(meanTolerance = ifelse(is.na(Tolerance_Upper), NA, round(mean(daysExceedanceTol, na.rm = TRUE),0)),
            minTolerance= ifelse(is.na(Tolerance_Upper), NA, min(daysExceedanceTol, na.rm = TRUE)),
            maxTolerance =  ifelse(is.na(Tolerance_Upper), NA, max(daysExceedanceTol, na.rm = TRUE)),
            meanSuboptimum = ifelse(is.na(Suboptimum_Upper), NA, round(mean(daysExceedanceOpt, na.rm = TRUE),0)),
            minSuboptimum= ifelse(is.na(Suboptimum_Upper), NA, min(daysExceedanceOpt, na.rm = TRUE)),
            maxSuboptimum =  ifelse(is.na(Suboptimum_Upper), NA, max(daysExceedanceOpt, na.rm = TRUE))) %>%
  mutate(outputTolerance = ifelse(is.na(meanTolerance), NA, paste0(meanTolerance, " (", minTolerance, "-", maxTolerance, ")")),
         outputSuboptimum = ifelse(is.na(meanSuboptimum), NA, paste0(meanSuboptimum, " (", minSuboptimum, "-", maxSuboptimum, ")"))) %>%
  distinct() %>%
  left_join(thresholds %>% dplyr::select(Species, LifeStage, Taxon, Suboptimum_Upper, Tolerance_Upper))

summary_all <- left_join(daysExceedanceSummary, fieldtemps, by = c("Taxon", "LifeStage")) %>%
  left_join(lengths) %>%
 dplyr::select(Species, Taxon, LifeStage, Length_mm, Length_type,
               `Maximum Field Detection Temperature (°C)` = maxTemp, 
               `Upper Suboptimum Temperature Threshold (°C)` = Suboptimum_Upper, 
               `Upper Tolerance Temperature Threshold (°C)` = Tolerance_Upper, 
               outputSuboptimumUpper = outputSuboptimum, outputToleranceUpper = outputTolerance) %>%
  arrange(Species, LifeStage)

summary_comb <- left_join(summary_all, summary_all0) %>%
  left_join(lengths) %>%
  mutate(Suboptimum = ifelse(!is.na(`Lower Suboptimum Temperature Threshold (°C)`), paste0(`Lower Suboptimum Temperature Threshold (°C)`, "-", `Upper Suboptimum Temperature Threshold (°C)`), NA),
         Tolerance = ifelse(!is.na(`Lower Tolerance Temperature Threshold (°C)`), paste0(`Lower Tolerance Temperature Threshold (°C)`, "-", `Upper Tolerance Temperature Threshold (°C)`), NA)) %>%
 dplyr::select(Species, Taxon, LifeStage, Length_mm, Length_type,
               `Maximum Field Detection Temperature (°C)`,
              `Suboptimum Threshold Range (°C)` = Suboptimum, 
              `Tolerance Threshold Range (°C)` = Tolerance,
               outputSuboptimum, outputSuboptimumUpper, outputTolerance, outputToleranceUpper) %>%
  arrange(Taxon, LifeStage)

write_csv(summary_all, here::here("manuscript_code","Data", "tables", "Table_AppendixB_Upper.csv"))
write_csv(daysExceedanceSummary, here::here("manuscript_code","Data", "tables", "Table_numDaysExceedance_v3.csv"))    
write_csv(summary_comb, here::here("manuscript_code","Data", "tables", "Table_AppendixB.csv"))

daysExceedanceSummary %>%
  ungroup() %>%
  filter(!(Species %in% c("Giant Reed EAV", "Brazilian Waterweed", "Water Hyacinth FAV", "Microcystis", "Asian Clam", "Overbite Clam"))) %>%
  summarize(meanTol = mean(meanTolerance, na.rm = TRUE),
            meanOpt = mean(meanSuboptimum, na.rm = TRUE))
```


### Make plot
```{r}
maxTol = max(DaysExceedanceDataUpper$daysExceedanceTol, na.rm = TRUE) +10
maxOpt = max(DaysExceedanceDataUpper$daysExceedanceOpt, na.rm = TRUE) +10
(FishTolU <- f_threshold_plot(DaysExceedanceDataUpper, var = "daysExceedanceTol", max_y = maxTol) +
    labs( y = "Annual Days \nExceeding Tolerance") ) 
(FishOptU <- f_threshold_plot(DaysExceedanceDataUpper, var = "daysExceedanceOpt", max_y = maxOpt) +
    labs( y = "Annual Days \nExceeding Optimum") )
```
### Combined
```{r}
# save legend separately for final figure
get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}
legend <- get_legend(FishTolU)
(FishOptU_noleg <- FishOptU + theme(legend.position = "none",
                                    axis.text.x = element_blank()))
(FishTolU_noleg<- FishTolU + theme(legend.position = "none") )

png(filename=file.path("manuscript_code/Figures/Figure_Opt_Tol_Upper.tiff"), units="in",type="cairo", bg="white", height=7.5, 
     width=8, res=300, pointsize=12)
ggarrange(legend, FishOptU_noleg, FishTolU_noleg, ncol=1, nrow=3,
             heights = c(0.75,2.35,4), labels = c("", "A","B"))
dev.off()
```



