---
title: "TempTrendModels"
author: "Catarina Pien"
date: "9/10/2020"
output: 
  html_document:
    code_folding: hide
    editor_options: 
      chunk_output_type: console
---
# Create Datasets

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(viridis) # color palette
library(plotly)
library(pscl)
library(visreg)
library(lattice)
library(here)
```

## Data import
```{r import, include = FALSE, message = FALSE, warning = FALSE}
tempFilt0 <- readRDS(here("Data", "Temp_filtered.rds")) %>%
  dplyr::select(-StationName) # temperature data 

# Regions <- read.csv(here("Data", "Stations_wRosiesReg2.csv")) %>%
#   select(-c(Latitude, Longitude)) %>%
#   mutate(Region = ifelse(Station == "LIS", "North Delta", Region))# Rosie's Regions
Regions <- read_csv(here::here("Data", "stations_w_regions_20230601.csv"))  %>%
  dplyr::select(Station, Regions) %>%
  rename(Region = Regions)

staInfo <- read.csv(here("Data", "StationsMetadata.csv")) # Get habitat type here

LatLon <- dplyr::select(staInfo, c("Station", "StationName", "Latitude", "Longitude"))

WYType <- read.csv(here("Data", "WYType.csv")) %>% # Get WY, WY type, Index 
  dplyr::select(-c(starts_with("Runoff"))) %>%
   mutate(Index_c = Index_Sac + Index_SJ) 

WYSimple <- dplyr::select(WYType, c("WY", "WYType2_Sac", "Index_c"))

str(tempFilt0)
```

Add variables
```{r vars}
tempFilt0 <- tempFilt0 %>%
  mutate(Year = year(tempFilt0$Date),
         Month = month(tempFilt0$Date),
         yDay = yday(tempFilt0$Date)) %>%
  mutate(WY = ifelse(Month %in% c(10, 11, 12), Year+1, Year))
```

## Filter out stations, merge regions and wytype
```{r regions, message = FALSE, warning = FALSE}
tempFilt1 <- left_join(tempFilt0, Regions, by = "Station") %>%
  filter(!Station %in% c("CNT", "CPP", "DAR", "DMC", "DYR","ECD", "HBP", "ROR", "DV7", "FLT", "RCS", "FPT"),
         !Station %in% c("RPN", "RIP", "VER"), 
         !is.na(Region)) 
tempFilt2 <- left_join(tempFilt1, staInfo, by = "Station") %>%
  dplyr::select(-c(StartDateDataset:County))

tempFilt <- left_join(tempFilt2, WYSimple, by = "WY") 

tempFilt$Region <- as.factor(tempFilt$Region)
tempFilt$HabitatType <- as.factor(tempFilt$HabitatType)

# saveRDS(tempFilt, "Data/tempFilt.rds")

```

* Informational (don't need to run for filtering but useful info)
These are slow
```{r Filtering down }
StationYearCombo <- tempFilt %>%
  group_by(Region, Station, WY, Date) %>%
  summarize(perDay = n()) %>%
  ungroup() %>%
  group_by(Region, Station, WY) %>%
  summarize(totalDays = n()) %>%
  ungroup()

StationNyears <- StationYearCombo %>%
  filter(totalDays>275) %>%
  group_by(Region, Station) %>%
  summarize(firstYear = first(WY),
            lastYear = last(WY),
            nYear = n()) %>%
  ungroup()

StationDayFilterN <- tempFilt %>%
  left_join(StationYearCombo) %>%
  filter(totalDays>275) %>%
  select(-Date) %>%
  unique() %>%
  group_by(Region, Station, WY) %>%
  mutate(nMonth = n()) %>%
  ungroup()

StationMonthFilterN <- StationDayFilterN %>%
  filter(nMonth >10) %>%
  select(-Month) %>%
  unique() %>%
  group_by(Region, Station) %>%
  mutate(nYear = n())



```

## Filter by days then months then years
10 years of data
```{r}
StationYearCombo <- tempFilt %>%
  filter(WY>2009) %>%
  dplyr::select(c(Region,Station,WY,Month, Date)) %>%
  unique() %>%
  group_by(Region, Station, WY) %>%
  mutate(totalDays = n()) %>%
  ungroup()

StationNyears <- StationYearCombo %>%
  filter(totalDays>275) %>%
  group_by(Region, Station) %>%
  summarize(firstYear = first(WY),
            lastYear = last(WY),
            nYear = n()) %>%
  ungroup()
  
StationDayFilter <- StationYearCombo %>%
  filter(totalDays>275) %>%
  dplyr::select(-Date) %>%
  unique() %>%
  group_by(Region, Station, WY) %>%
  mutate(nMonth = n()) %>%
  ungroup()

StationMonthFilter <- StationDayFilter %>%
  filter(nMonth >10) %>%
  dplyr::select(-Month) %>%
  unique() %>%
  group_by(Region, Station) %>%
  mutate(nYear = n())

StationYearFilter <- StationMonthFilter %>%
  filter(nYear>7) 

ListOfSta <- StationYearFilter %>%
  dplyr::select(-c(WY, totalDays, nMonth))%>%
  unique() 

# write.csv(StationYearFilter, "StationYearFilter.csv")
```

Subset data to use to data that has at least 10 years of data, and that extends to 2019, and each year has > 275 days of data
Took out Far North Region. Add LIS to North Delta.
```{r subset}
tempToUse <- inner_join(tempFilt, StationYearFilter, by = c("Region","Station", "WY")) 
tempMonth <- inner_join(tempFilt, StationMonthFilter) 
#tempToUse$WY = as.numeric(tempToUse$WY)
today = format(today(), "%Y%m%d")
saveRDS(tempToUse, paste0("Data/temp10years_", today, ".rds"))
saveRDS(tempToUse, here::here("Data/temp10years_20210811.rds"))
```


# Calendar Year 

Edit dataset for Peggy (Calendar Year)
```{r}
StationYearComboCY <- tempFilt1 %>%
  filter(Year>2009) %>%
  dplyr::select(c(Region,Station,Year,Month, Date)) %>%
  unique() %>%
  group_by(Region, Station, Year) %>%
  mutate(totalDays = n()) %>%
  ungroup() 
  
StationDayFilterCY <- StationYearComboCY %>%
  filter(totalDays>275) %>%
  dplyr::select(-Date) %>%
  unique() %>%
  group_by(Region, Station, Year) %>%
  mutate(nMonth = n()) %>%
  ungroup()

StationMonthFilterCY <- StationDayFilterCY %>%
  filter(nMonth >10) %>%
  dplyr::select(-Month) %>%
  unique() %>%
  group_by(Region, Station) %>%
  mutate(nYear = n()) %>%ungroup()

StationYearFilterCY <- StationMonthFilterCY %>%
  filter(nYear>7) %>%
  filter(Station!="FLT")

ListOfStaCY <- StationYearFilterCY %>%
  dplyr::select(-c(Year, totalDays, nMonth))%>%
  unique() 

# Write data -------------------------
tempToUseCY <- inner_join(tempFilt, StationYearFilterCY, by = c("Region","Station", "Year")) %>%
  dplyr::select(-nMonth, -nYear, -totalDays)
#tempToUse$WY = as.numeric(tempToUse$WY)
today = format(today(), "%Y%m%d")
saveRDS(tempToUseCY, paste0("../manuscript_code/Data/temp10yearsCalYr_", today, ".rds"))

```

# Create additional datasets
* Create dataset for mean, max, and min, var for Monthly
* Filter for data that is represented for a whole year
* Create datasets for mean, max, min

Daily Temp
```{r dailyoverall}
tempDaily <- tempToUse %>%
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c, Date) %>%
  summarize(maxDaily = max(Temp),
            minDaily = min(Temp),
            meanDaily = round(mean(Temp),1),
            rangeTemp = maxDaily-minDaily) %>%
  ungroup()
tempDaily$WY <- as.numeric(tempDaily$WY)
saveRDS(tempDaily, here::here("manuscript_code/Data/tempDaily.rds"))
```

Monthly Temp
```{r monthlyoverall, message = FALSE, warning = FALSE}
tempMon0 <- tempToUse %>% 
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c, Month) %>%
  summarize(maxTemp = max(Temp),
            minTemp = min(Temp),
            meanTemp = round(mean(Temp),1),
            rangeTemp = maxTemp-minTemp) %>%
  ungroup()
#saveRDS(tempMon0, "tempMonthly.rds")
```

Annual Temp
```{r annualoverall}
tempAn <- tempToUse %>% 
  group_by(Region, Station, HabitatType, WY, WYType2_Sac, Index_c) %>%
  summarize(maxTemp = max(Temp),
            minTemp = min(Temp),
            meanTemp = round(mean(Temp),1),
            rangeTemp = maxTemp-minTemp) %>%
  ungroup()
# saveRDS(tempAn, here::here("Data/tempAnnual.rds"))
```

Code to make sure every month has data - currently is not being used (need to join with above)
```{r nMon}
# Filter to only data that has temps from every month so as not to skew the data that only has part of the year represented.
nMon <- tempMon %>% group_by(Station, WY) %>%
  summarize(nMon = n())

nMon$WY <- as.numeric(nMon$WY)
```

Mean Max and Min Temp
```{r Mean Max}
tempAvMon0 <- tempToUse %>%
  group_by(Region, Station, Year, WY, WYType2_Sac, Month, Date) %>%
  summarize(maxTemp = max(Temp),
            minTemp = min(Temp)) %>%
  ungroup() %>%
  group_by(Region, Station, Year, WY, WYType2_Sac,Month) %>%
  summarize(maxAvTemp = round(mean(maxTemp),1),
            minAvTemp = round(mean(minTemp),1))

tempMon <- left_join(tempMon0, tempAvMon0) %>%
  dplyr::select(Region, Station, HabitatType,Year,  WY, WYType2_Sac, Index_c, Month, maxTemp, maxAvTemp, minAvTemp, everything())


saveRDS(tempMon, here::here("manuscript_code", "Data","tempMonthly.rds"))
```

########### Written files from above ###############
Read in 
```{r}
setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/TempSynthesis/")

tempFilt <- readRDS("Data/tempFilt.rds") 
tempToUse <- readRDS(here::here("Data/temp10years_20210811.rds"))
tempAn <- readRDS("Data/tempAnnual.rds")
tempMon <- readRDS("Data/tempMonthly.rds")
tempDaily <- readRDS("Data/tempDaily.rds")
```




# Some exploratory plots to look at data
```{r exploratory plots}
tilerecord <- ggplot(StationYearFilter, aes(Station, ordered(WY), fill = totalDays)) + geom_tile() + labs(title = "Period of Record - Number of days each water year for each station") +
  theme_bw() + theme(axis.text.y = element_text(size = 12),
                     axis.text.x = element_text(size = 10, angle = 90, vjust = 0.5),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14))
ggplotly(tilerecord)
tilerecord

nyears <- ggplot(StationNyears, aes(x = Region, y = nYear, color = Station)) + geom_point() +
  labs(title = "Number of years of data by Region/Station, filtered for years with >200 days data")
ggplotly(nyears)

nYearBar <- ggplot(StationNyears, aes(y = ..count.., x = nYear)) + geom_bar() +
  labs(title = "Count of Stations and number of years of data available") +
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14))
ggplotly(nYearBar)
nYearBar
```

Map showing distribution of data with number of years of data
```{r map}
library(leaflet)

MapYears <- left_join(StationNyears, LatLon)

# Palette from viridis
  staPal <- colorNumeric("viridis", domain = MapYears$nYear)
  
MapYears %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    color = ~staPal(nYear),
    stroke = FALSE,
    fillOpacity = 0.9,
    lng = ~Longitude,
    lat = ~Latitude,
    labelOptions = labelOptions(noHide = F),
    popup = ~paste(Station, ":", StationName, "<br/>", "nYears:", nYear, "<br/>",
                   "Date Range:", firstYear, "-", lastYear)) %>%
    addLegend(pal = staPal,
            values = ~nYear,
            position = "bottomright")
```

Map 10 years+ Data
```{r}
# Filter for those with 10 years + 
MapYears2 <- MapYears %>% filter(nYear > 9)

# Palette from viridis
  staPal2 <- colorNumeric("magma", domain = MapYears2$nYear)
  
MapYears2 %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    color = ~staPal2(nYear),
    stroke = FALSE,
    fillOpacity = 0.9,
    lng = ~Longitude,
    lat = ~Latitude,
    labelOptions = labelOptions(noHide = F),
    popup = ~paste(Station, ":", StationName, "<br/>", "nYears:", nYear, "<br/>",
                   "Date Range:", firstYear, "-", lastYear)) %>%
    addLegend(pal = staPal2,
            values = ~nYear,
            position = "bottomright")
```

